---
title: "CASE Full FINAL"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = TRUE)
```
# Setup
```{r include=TRUE}
library(ggplot2)
library(tidyr)
library(plyr)
library(dplyr)
library(qvalue)
library(stringr)
library(pcadapt)
library(poolSeq)
library(ACER)
library(ggman)
library(VennDiagram)
library(scales)
library(data.table)
library(patchwork)


# Custom theme for black background figures
theme_black = function(base_size = 16, base_family = "") {
  
  theme_grey(base_size = base_size, base_family = base_family) %+replace%
    
    theme(
      # Specify axis options
      axis.line = element_line(colour = "white", size = 1.5),
      axis.text.x = element_text(size = base_size*0.8, color = "white", lineheight = 0.9),  
      axis.text.y = element_text(size = base_size*0.8, color = "white", lineheight = 0.9),  
      axis.ticks = element_line(color = "white", size  =  0.2),  
      axis.title.x = element_text(size = base_size, color = "white", margin = margin(0, 10, 0, 0)),  
      axis.title.y = element_text(size = base_size, color = "white", angle = 90, margin = margin(0, 10, 0, 0)),  
      axis.ticks.length = unit(0.3, "lines"),   
      # Specify legend options
      legend.background = element_rect(color = NA, fill = "transparent"),  
      legend.key = element_rect(color = NA,  fill = "transparent"),  
      legend.key.size = unit(1.2, "lines"),  
      legend.key.height = NULL,  
      legend.key.width = NULL,      
      legend.text = element_text(size = base_size*0.8, color = "white"),  
      legend.title = element_text(size = base_size*0.8, face = "bold", hjust = 0, color = "white"),  
      legend.position = "right",  
      legend.text.align = NULL,  
      legend.title.align = NULL,  
      legend.direction = "vertical",  
      legend.box = NULL, 
      # Specify panel options
      panel.background = element_rect(fill = "transparent", color  =  NA),  
      panel.border = element_blank(),  
      panel.grid.major = element_line(color = "transparent"),  
      panel.grid.minor = element_line(color = "transparent"),  
      #panel.margin = unit(0.5, "lines"),   
      panel.spacing= unit(0.5, "lines"),
      # Specify facetting options
      strip.background = element_rect(fill = "transparent", color = "transparent"),  
      strip.text.x = element_text(size = base_size*0.8, color = "white"),  
      strip.text.y = element_text(size = base_size*0.8, color = "white",angle = -90),  
      # Specify plot options
      plot.background = element_rect(color = "transparent", fill = "transparent"),  
      plot.title = element_text(size = base_size*1.2, color = "white", hjust = 1),  
      plot.margin = unit(rep(1, 4), "lines")
      
    )
  
}

# Function to convert p-values to q-values
Qvalue_convert <- function(table) {


table <- spread(table,GROUP,PVAL)  
  
table$CHR <- table$CHROM

table %>% 
  mutate(CHR = str_replace(CHR, "NC_035780.1", "1")) %>% 
  mutate(CHR = str_replace(CHR, "NC_035781.1", "2")) %>% 
  mutate(CHR = str_replace(CHR, "NC_035782.1", "3")) %>% 
  mutate(CHR = str_replace(CHR, "NC_035783.1", "4")) %>% 
  mutate(CHR = str_replace(CHR, "NC_035784.1", "5")) %>% 
  mutate(CHR = str_replace(CHR, "NC_035785.1", "6")) %>% 
  mutate(CHR = str_replace(CHR, "NC_035786.1", "7")) %>% 
  mutate(CHR = str_replace(CHR, "NC_035787.1", "8")) %>%
  mutate(CHR = str_replace(CHR, "NC_035788.1", "9")) %>% 
  mutate(CHR = str_replace(CHR, "NC_035789.1", "10"))  -> pp1

pp1 <- unite(pp1, "SNP", c("CHROM","BP"),remove = FALSE)

pp1$CHR <- as.numeric(pp1$CHR)  

# Set pi0=1 to equal Benjamini Hochberg
pp1$QCA <- qvalue(pp1$PCA, pi0 = 1)$qvalues
pp1$QCON <- qvalue(pp1$PCON, pi0 = 1)$qvalues
pp1$QSE <- qvalue(pp1$PSE, pi0 = 1)$qvalues
pp1$QCASE <- qvalue(pp1$PCASE, pi0 = 1)$qvalues

#pp1$QCA <- qvalue(pp1$PCA)$qvalues
#pp1$QCON <- qvalue(pp1$PCON)$qvalues
#pp1$QSE <- qvalue(pp1$PSE)$qvalues
#pp1$QCASE <- qvalue(pp1$PCASE)$qvalues

return(pp1)
}

# Function to determine significant loci in various outpus
Significat_subset <- function(pv, alpha, alpha2) {
  # Add new logical columns based on conditions
  pv$Sig.CASE <- pv$QCASE < alpha
  pv$Sig.CA <- pv$QCA < alpha
  pv$Sig.SE <- pv$QSE < alpha
  
  # Subset the dataframe
  ppsig <- subset(pv, QCA < alpha | QCASE < alpha | QSE < alpha)
  ppsig <- subset(ppsig, QCON > alpha2)
  
  # Print diagnostics
  print(nrow(pv))
  print(nrow(ppsig))
  print(nrow(ppsig) / nrow(pv))
  
  # Return the modified dataframe
  return(ppsig)
}

group_and_average <- function(df) {
  df %>%
    dplyr::group_by(SNP) %>%
    dplyr::summarize(across(c(PCA, PCASE, PCON, PSE, CHR, QCA, QCON, QSE, QCASE), 
                            ~ if (all(is.na(.))) NA else min(., na.rm = TRUE)),
                     Sig.CASE = any(Sig.CASE, na.rm = TRUE),
                     Sig.CA = any(Sig.CA, na.rm = TRUE),Sig.SE = any(Sig.SE, na.rm = TRUE),
                     CHROM = first(CHROM), BP = first(BP), .groups = "drop") }


cbPaletteSmall <- c("#E69F00", "#009E73", "#999999","sky blue","#0072B2")
cbPaletteSmall4 <- c("#999999","#E69F00", "#0072B2", "#009E73")
cbPaletteSmall3 <- c("#E69F00", "#0072B2","#009E73")
```

```{r}
sessionInfo()
```

## Download Popoolation2 scripts
```{bash, eval = FALSE}
cd ../scripts
git clone https://github.com/ToBoDev/assessPool.git
```

## Create conda (mamba) environment
```{bash, eval=FALSE}
mamba env create --file ../CASE_environment.yaml
mamba env create --file ../random_draw_environment.yaml
```
# Filtering
```{bash, eval=FALSE}
source activate CASE
cd ../raw.vcf
bash ../scripts/CASE_PVCF_filter2.sh CASE 64 20
```


```{bash, eval=FALSE}
source activate CASE
cd ../raw.vcf 
bcftools index CASE.TRSdp.20.g5.nDNA.FIL.vcf.gz
bcftools query -l CASE.TRSdp.20.g5.nDNA.FIL.vcf.gz > samples
```
## Create Unified Sync file
Each sequencing run had some extra samples that need to be removed before starting the analysis
Each block was filtered for missing data less than 10% and MAF of > 0.015 based on read counts using VCF file first.



```{bash, eval=FALSE}
source activate CASE

cd ../raw.vcf
bcftools view -S <(grep B11 samples | grep -v 1.G) CASE.TRSdp.20.g5.nDNA.FIL.vcf.gz | bcftools view -i 'F_MISSING<0.1'  | bcftools view -M 4 -m 2 | bcftools +fill-tags -- -t 'AAF:1=sum(FORMAT/AO)/sum(FORMAT/DP)' | bcftools +fill-tags -- -t  FORMAT/VAF | bcftools view --threads 40 -i 'AAF > 0.015 && AAF < 0.985' | bcftools query -f '%CHROM\t%POS\n' > B11.pos

bcftools view -S <(grep B10 samples | grep -v J17 | grep -v J05) CASE.TRSdp.20.g5.nDNA.FIL.vcf.gz | bcftools view -i 'F_MISSING<0.1' | bcftools view -M 4 -m 2 | bcftools +fill-tags -- -t 'AAF:1=sum(FORMAT/AO)/sum(FORMAT/DP)' | bcftools +fill-tags -- -t  FORMAT/VAF | bcftools view --threads 40 -i 'AAF > 0.015 && AAF < 0.985' | bcftools query -f '%CHROM\t%POS\n' > B10.pos

bcftools view -S <(grep B12 samples) CASE.TRSdp.20.g5.nDNA.FIL.vcf.gz | bcftools view -i 'F_MISSING<0.1' | bcftools view -M 4 -m 2 | bcftools +fill-tags -- -t 'AAF:1=sum(FORMAT/AO)/sum(FORMAT/DP)' | bcftools +fill-tags -- -t  FORMAT/VAF | bcftools view --threads 40 -i 'AAF > 0.015 && AAF < 0.985' | bcftools query -f '%CHROM\t%POS\n'  > B12.pos

cat B*.pos | sort | uniq > fil.pos

bcftools view -R fil.pos -S <(grep -v 1.GB11 samples | grep -v J17B10| grep -v J05B10) --threads 40 -m2 -M 4 CASE.TRSdp.20.g5.nDNA.FIL.vcf.gz -O z -o SNP.CASE.TRSdp.20.B90.2a.perp.vcf.gz

#bcftools view --threads 40 SNP.CASE.TRSdp.20.B90.2a.perp.vcf.gz | mawk '!/#/' | cut -f 1,2 | mawk '{print $1"\t"$2-1"\t"$2}' > total.snp.bed

#bedtools intersect -wb -a total.snp.bed -b ~/CASE/analysis/sorted.ref3.0.gene.bed | grep -oh "gene=LOC.*;g" | sed 's/gene=//g' | sed 's/;g//g' | sort | uniq > CASE.study.background.LOC

```

### Create Sync files
```{bash, eval=FALSE}
source activate CASE

bcftools view --threads 40 ../raw.vcf/SNP.CASE.TRSdp.20.B90.2a.perp.vcf.gz  | mawk -F'\t' -v OFS='\t' '{ for(i=1;i<=NF;i++) if($i==".:.:.:.:.:.:.:.") $i="."; print }' > temp.vcf
python2 ../scripts/VCFtoPopPool.py temp.vcf CASE.All.Blocks.sync 
rm temp.vcf
```

### This sort is to maintain reproducibility across older analysis
```{bash}
mawk 'BEGIN {OFS="\t"
    order["CHROM"] = 0
    order["NC_035789.1"] = 1
    order["NC_035780.1"] = 2
    order["NC_035781.1"] = 3
    order["NC_035782.1"] = 4
    order["NC_035783.1"] = 5
    order["NC_035784.1"] = 6
    order["NC_035785.1"] = 7
    order["NC_035786.1"] = 8
    order["NC_035787.1"] = 9
    order["NC_035788.1"] = 10
}
{ print order[$1], $2, NR, $0 }' CASE.All.Blocks.sync | sort -k1,1n -k2,2n -k3,3n | cut -f4- > test.sync

mv test.sync CASE.All.Blocks.sync
```


```{bash}
cat <(echo -e "CHROM\tPOS") ../raw.vcf/B10.pos > B10.pos
cat <(echo -e "CHROM\tPOS") ../raw.vcf/B11.pos > B11.pos
cat <(echo -e "CHROM\tPOS") ../raw.vcf/B12.pos > B12.pos

mawk 'NR==FNR{a[$1,$2]; next} ($1,$2) in a' B10.pos CASE.All.Blocks.sync | mawk 'NR==1{for(i=1;i<=NF;i++)if(i<=3||$i~/B10$/)k[i]}{o="";for(i=1;i<=NF;i++)if(i in k)o=o?o OFS $i:$i;print o}' OFS='\t' | mawk '!/\t\.\t/' > CASE.Block10.sync
mawk 'NR==FNR{a[$1,$2]; next} ($1,$2) in a' B11.pos CASE.All.Blocks.sync | mawk 'NR==1{for(i=1;i<=NF;i++)if(i<=3||$i~/B11$/)k[i]}{o="";for(i=1;i<=NF;i++)if(i in k)o=o?o OFS $i:$i;print o}' OFS='\t' | mawk '!/\t\.\t/' > CASE.Block11.sync
mawk 'NR==FNR{a[$1,$2]; next} ($1,$2) in a' B12.pos CASE.All.Blocks.sync | mawk 'NR==1{for(i=1;i<=NF;i++)if(i<=3||$i~/B12$/)k[i]}{o="";for(i=1;i<=NF;i++)if(i in k)o=o?o OFS $i:$i;print o}' OFS='\t' | mawk '!/\t\.\t/' > CASE.Block12.sync
```

## Add coverage stats to sync file and filter by minimum coverage

```{bash, eval=FALSE}
source activate CASE
mawk -f ../scripts/add_cov_sync CASE.Block10.sync | mawk '$20 > 9 && $22 > 24' > CASE.dp20.Block10.cov.sync &
mawk -f ../scripts/add_cov_sync CASE.Block11.sync | mawk '$24 > 9 && $26 > 24' > CASE.dp20.Block11.cov.sync &
mawk -f ../scripts/add_cov_sync CASE.Block12.sync | mawk '$24 > 9 && $26 > 24' > CASE.dp20.Block12.cov.sync &
#mawk -f ../scripts/add_cov_sync CASE.All.Blocks.sync | mawk '$66 > 9 && $68 > 24' > CASE.All.Blocks.cov.sync
mawk -f ../scripts/add_cov_sync CASE.All.Blocks.sync | mawk '$60 > 9 && $62 > 24' | mawk '!/\t\.\t/'  > CASE.All.Blocks.cov.sync

cut -f1,2 CASE.dp20.Block1*.cov.sync | sort | uniq -c | mawk '$1 > 2' | mawk '{print $2 "\t" $3}' > filtered.loci.allthreeblocks
```

# Visualize across 10,000 random loci

## All
```{bash, eval = FALSE}
source activate CASE

mawk '!/CHR/' filtered.loci.allthreeblocks | shuf -n 50000  | shuf -n 10000 > rand.loci

mawk 'NR==FNR{a[$1,$2]; next} ($1,$2) in a' rand.loci CASE.All.Blocks.cov.sync | cut --complement -f60- > input.all.rand.sync

```

```{r}
input.all.rand <- read.sync(file="input.all.rand.sync", gen=seq(1,56), repl=seq(1,56), polarization="rising")


input.all.rand.af <- af(input.all.rand,gen=seq(1,56), repl=seq(1,56))
treatment.labels <- c(rep("CA", 11),rep("CASE", 11),rep("CON", 11),rep("IS", 12),rep("SE", 11))
spawn.names <- c("B12","B11","B12","B10","B11","B10","B11","B12","B10","B12","B11","B10","B11","B12","B12","B10","B12","B11","B10","B11","B11","B12","B10","B11","B12","B11","B10","B12","B10","B11","B12","B11","B12","B10","B11","B10","B11","B10","B11","B10","B11","B12","B12","B12","B12","B11","B12","B10","B10","B11","B11","B10","B12","B12","B11","B12")

colnames(input.all.rand.af) <- paste(treatment.labels,spawn.names,sep="_")


# Perform PCA
af_t <- t(input.all.rand.af)

pca_res <- prcomp(af_t, center = TRUE, scale. = TRUE)

# Get scores for plotting
pca_df <- as.data.frame(pca_res$x)
#pca_df$locus <- rownames(input.all.rand.af)  # keep locus IDs if you have them

var_explained <- pca_res$sdev^2 / sum(pca_res$sdev^2) * 100

# Example: if you have a vector "pop_group" the same length as rows

treatment.labels <- c(rep("CA", 11),rep("CASE", 11),rep("CON", 11),rep("IS", 12),rep("SE", 11))
spawn.names <- c("B12","B11","B12","B10","B11","B10","B11","B12","B10","B12","B11","B10","B11","B12","B12","B10","B12","B11","B10","B11","B11","B12","B10","B11","B12","B11","B10","B12","B10","B11","B12","B11","B12","B10","B11","B10","B11","B10","B11","B10","B11","B12","B12","B12","B12","B11","B12","B10","B10","B11","B11","B10","B12","B12","B11","B12")

pca_df$Population <- spawn.names
pca_df$Treatments <- treatment.labels

ggplot(pca_df, aes(x = PC1, y = PC2, color = Population, fill=Population)) +
  geom_point(aes(alpha=0.2), size =10,shape=21, col="black")+  scale_fill_manual(values=cbPaletteSmall,name="Treatment")+ 
guides(alpha=FALSE) +theme(axis.title.x = element_text(size = 24),axis.title.y = element_text(size = 24)) +
  theme_minimal() +
  labs(
    x = paste0("PC1 (", round(var_explained[1], 1), "%)"),
    y = paste0("PC2 (", round(var_explained[2], 1), "%)"),
    title = "PCA of Allele Frequencies"
  )

```
```{r}
png(filename="PC_all_rand1.png", type="cairo",units="px", width=5400, height=3000, res=300, bg="transparent")
ggplot(pca_df, aes(x=PC1, y= PC2, color = Treatments, fill=Treatments)) + geom_point(aes(alpha=0.2), size =10,shape=21, col="black")+ theme_classic() + scale_fill_manual(values=cbPaletteSmall,name="Treatment")+ 
guides(alpha=FALSE) +theme(axis.title.x = element_text(size = 24),axis.title.y = element_text(size = 24))+
  labs(
    x = paste0("PC1 (", round(var_explained[1], 1), "%)"),
    y = paste0("PC2 (", round(var_explained[2], 1), "%)"),
    title = "PCA of Allele Frequencies"
  )
dev.off()
png(filename="PC_all_rand1S.png", type="cairo",units="px", width=5400, height=3000, res=300, bg="transparent")
ggplot(pca_df, aes(x=PC1, y= PC2, color = Population, fill=Population)) + geom_point(aes(alpha=0.2), size =10,shape=21, col="black")+ theme_classic() + scale_fill_manual(values=cbPaletteSmall,name="Spawn")+ 
guides(alpha=FALSE) +theme(axis.title.x = element_text(size = 24),axis.title.y = element_text(size = 24))+
  labs(
    x = paste0("PC1 (", round(var_explained[1], 1), "%)"),
    y = paste0("PC2 (", round(var_explained[2], 1), "%)"),
    title = "PCA of Allele Frequencies"
  )
dev.off()
```

## All Initial Samples

```{r}
input.IS.rand <- input.all.rand.af[,34:45]
afi_t <- t(input.IS.rand)

pca_i_res <- prcomp(afi_t, center = TRUE, scale. = TRUE)

# Get scores for plotting
pca_i_df <- as.data.frame(pca_i_res$x)

var_explained <- pca_i_res$sdev^2 / sum(pca_i_res$sdev^2) * 100

pca_i_df$Population <- spawn.names[34:45]
pca_i_df$Treatments <- c(rep("IS", 12))

ggplot(pca_i_df, aes(x = PC1, y = PC2, color = Population, fill=Population)) +
  geom_point(aes(alpha=0.2), size =10,shape=21, col="black")+  scale_fill_manual(values=cbPaletteSmall,name="Treatment")+ 
guides(alpha=FALSE) +theme(axis.title.x = element_text(size = 24),axis.title.y = element_text(size = 24)) +
  theme_classic() +
  labs(
    x = paste0("PC1 (", round(var_explained[1], 1), "%)"),
    y = paste0("PC2 (", round(var_explained[2], 1), "%)"),
    title = "PCA of Allele Frequencies"
  )

```



```{r}
png(filename="PC_all_IS_rand1.png", type="cairo",units="px", width=5400, height=3000, res=300, bg="transparent")

ggplot(pca_i_df, aes(x = PC1, y = PC2, color = Population, fill=Population)) +
  geom_point(aes(alpha=0.2), size =10,shape=21, col="black")+  scale_fill_manual(values=cbPaletteSmall,name="Spawn")+ 
guides(alpha=FALSE) +theme(axis.title.x = element_text(size = 24),axis.title.y = element_text(size = 24)) +
  theme_classic() +
  labs(
    x = paste0("PC1 (", round(var_explained[1], 1), "%)"),
    y = paste0("PC2 (", round(var_explained[2], 1), "%)"),
    title = "PCA of Allele Frequencies"
  )
```

## Random loci for each individual blocks
```{r}

# Optional: clean whitespace from column names (safe-guard)
colnames(input.all.rand.af) <- trimws(colnames(input.all.rand.af))

stages <- c("B10","B11","B12")

for(stage in stages){
  # match columns that end with "_B10" / "_B11" / "_B12"
  cols_idx <- grep(paste0("_", stage, "$"), colnames(input.all.rand.af))
  cat(sprintf("\n== Stage %s: found %d sample columns ==\n", stage, length(cols_idx)))
  if(length(cols_idx) < 2){
    warning(sprintf("Stage %s: less than 2 samples found - skipping PCA.", stage)); next
  }

  sub_mat <- input.all.rand.af[, cols_idx, drop = FALSE]
  cat("  dim(sub_mat) (loci x samples):", dim(sub_mat), "\n")

  # transpose so rows = samples, cols = loci (variables)
  mat_t <- t(sub_mat)

  # remove loci (columns) with zero variance across the samples in this stage
  var_cols <- apply(mat_t, 2, var, na.rm = TRUE)
  keep <- which(var_cols > 0)
  removed_n <- sum(var_cols == 0)
  cat("  loci removed (zero variance):", removed_n, "\n")

  if(length(keep) < 2){
    warning(sprintf("Stage %s: fewer than 2 variable loci after filtering - skipping PCA.", stage)); next
  }
  mat_t2 <- mat_t[, keep, drop = FALSE]
  cat("  dim(mat_t2) (samples x retained loci):", dim(mat_t2), "\n")

  # run PCA (now safe to scale)
  pca_res <- prcomp(mat_t2, center = TRUE, scale. = TRUE)

  # PCA dataframe
  pca_df <- as.data.frame(pca_res$x)

  # extract Treatments and Spawn from sample names (rownames of mat_t2)
  sample_names <- rownames(mat_t2)
  pca_df$Treatment <- sub("_.*", "", sample_names)   # text before first "_"
  pca_df$Spawn     <- sub(".*_", "", sample_names)   # text after last "_"

  # variance explained
  var_explained <- (pca_res$sdev^2) / sum(pca_res$sdev^2) * 100

  # choose palette fallback if cbPaletteSmall not defined
  if(exists("cbPaletteSmall")){
    fill_scale <- scale_fill_manual(values = cbPaletteSmall, name = "Treatment")
  } else {
    fill_scale <- scale_fill_brewer(palette = "Set1", name = "Treatment")
  }

  # plot
  p <- ggplot(pca_df, aes(x = PC1, y = PC2, fill = Treatment)) +
    geom_point(aes(alpha = 0.2), size = 6, shape = 21, color = "black") +
    fill_scale +
    guides(alpha = FALSE) +
    theme_classic() +
    theme(axis.title.x = element_text(size = 14),
          axis.title.y = element_text(size = 14),
          plot.title = element_text(hjust = 0.5)) +
    labs(
      title = paste0("PCA - ", stage),
      x = paste0("PC1 (", round(var_explained[1], 1), "%)"),
      y = paste0("PC2 (", round(var_explained[2], 1), "%)")
    )

  # save (adjust size/resolution or use png(...) if you prefer)
  outfile <- paste0("PCA_all_rand_", stage, ".png")
  ggsave(outfile, plot = p, width = 12, height = 7, dpi = 300)
  cat("  saved:", outfile, "\n")
}
```

### Venn Diagram for called loci
```{bash}
cut -f1,2 CASE.dp20.Block10.cov.sync > Block10.pos
cut -f1,2 CASE.dp20.Block11.cov.sync > Block11.pos
cut -f1,2 CASE.dp20.Block12.cov.sync > Block12.pos

cat <(echo "SNP") <(cat Block1*.pos | cut -f1,2 | sort | uniq -c | mawk '$1 <2' | mawk '{print $2"_"$3}') > singleton.loci
```

```{r}
# Read and preprocess data
B10.loci <- read.table("Block10.pos", header = TRUE)
colnames(B10.loci) <- c("CHROM", "BP")
B10.loci <- B10.loci %>% mutate(BLOCK_10 = TRUE)

B11.loci <- read.table("Block11.pos", header = TRUE)
colnames(B11.loci) <- c("CHROM", "BP")
B11.loci <- B11.loci %>% mutate(BLOCK_11 = TRUE)

B12.loci <- read.table("Block12.pos", header = TRUE)
colnames(B12.loci) <- c("CHROM", "BP")
B12.loci <- B12.loci %>% mutate(BLOCK_12 = TRUE)

# Full join all data frames to preserve all CHROM and BP combinations
pos_df <- B10.loci %>%
  full_join(B11.loci %>% dplyr::select(CHROM, BP, BLOCK_11), by = c("CHROM", "BP")) %>%
  full_join(B12.loci %>% dplyr::select(CHROM, BP, BLOCK_12), by = c("CHROM", "BP"))

# Replace NA values in the BLOCK_* columns with FALSE
pos_df <- pos_df %>%
  mutate(
    BLOCK_10 = ifelse(is.na(BLOCK_10), FALSE, BLOCK_10),
    BLOCK_11 = ifelse(is.na(BLOCK_11), FALSE, BLOCK_11),
    BLOCK_12 = ifelse(is.na(BLOCK_12), FALSE, BLOCK_12)
  )


loci.b10 <- nrow(subset(pos_df,BLOCK_10 == TRUE))
loci.b11 <- nrow(subset(pos_df,BLOCK_11 == TRUE))
loci.b12 <- nrow(subset(pos_df,BLOCK_12 == TRUE))

loci.b10.b11 <- nrow(subset(pos_df,BLOCK_10 == TRUE & BLOCK_11 ==TRUE))
loci.b10.b12 <- nrow(subset(pos_df,BLOCK_10 == TRUE & BLOCK_12 ==TRUE))
loci.b11.b12 <- nrow(subset(pos_df,BLOCK_11 == TRUE & BLOCK_12 ==TRUE))
loci.b10.b11.b12 <- nrow(subset(pos_df,BLOCK_10 == TRUE & BLOCK_11 ==TRUE & BLOCK_12 ==TRUE))

png(filename="VenSNPs.png", type="cairo",units="px", width=4000, height=4000, res=500, bg="transparent")

venn.plot <- draw.triple.venn(
  area1=loci.b10, area2=loci.b11, area3=loci.b12, 
  n12= loci.b10.b11, n13=loci.b10.b12, 
  n23=loci.b11.b12,scaled=TRUE,
  n123=loci.b10.b11.b12, cex=rep(2, 7),
  category = c("Block 10", "Block 11", "Block 12"),
  fill = cbPaletteSmall3,cat.cex = rep(2, 3),
  cat.col = cbPaletteSmall3, label.col = rep("white", 7))
dev.off()
```

## Differentiate Singleton Loci
```{bash}
source activate CASE

tail -n +2 singleton.loci | awk '{
  match($1, /_[0-9]+$/)
  print substr($1, 1, RSTART-1) "\t" substr($1, RSTART+1)
}' > sing.pos.txt

mawk 'BEGIN {
  FS = "\t"
  maf_min   = 0.015
  depth_min = 20
  while ((getline line < "sing.pos.txt") > 0) {
    split(line, p, "\t")
    sing[p[1] FS p[2]] = 1
  }
  close("sing.pos.txt")
  print "SNP\tdepth_b10\tmaf_b10\tdepth_b11\tmaf_b11\tdepth_b12\tmaf_b12\tdropout_type"
}
NR == 1 {
  nb10 = nb11 = nb12 = 0
  for (i = 1; i <= NF; i++) {
    if ($i ~ /B10/) c10[++nb10] = i
    if ($i ~ /B11/) c11[++nb11] = i
    if ($i ~ /B12/) c12[++nb12] = i
  }
  next
}
!(($1 FS $2) in sing) { next }
function block_maf(cols, ncols,    i, ct, d, d_total, minor_total, max_ct) {
  d_total = 0; minor_total = 0
  for (i = 1; i <= ncols; i++) {
    split($(cols[i]), ct, ":")
    d = ct[1]+ct[2]+ct[3]+ct[4]
    d_total += d
    if (d > 0) {
      max_ct = ct[1]
      if (ct[2] > max_ct) max_ct = ct[2]
      if (ct[3] > max_ct) max_ct = ct[3]
      if (ct[4] > max_ct) max_ct = ct[4]
      minor_total += d - max_ct
    }
  }
  bd_out   = d_total
  bmaf_out = (d_total > 0) ? minor_total / d_total : -1
}
{
  block_maf(c10, nb10); d10=bd_out; m10=bmaf_out
  block_maf(c11, nb11); d11=bd_out; m11=bmaf_out
  block_maf(c12, nb12); d12=bd_out; m12=bmaf_out
  snp = $1"_"$2

  # Near-fixed in an absent block = adequate depth but MAF below threshold
  lv10 = (d10>=depth_min && m10>=0 && m10<maf_min) ? 1 : 0
  lv11 = (d11>=depth_min && m11>=0 && m11<maf_min) ? 1 : 0
  lv12 = (d12>=depth_min && m12>=0 && m12<maf_min) ? 1 : 0

  type = (lv10||lv11||lv12) ? "low_variation" : "low_coverage"
  printf "%s\t%d\t%.4f\t%d\t%.4f\t%d\t%.4f\t%s\n", \
    snp, d10, m10, d11, m11, d12, m12, type
}' CASE.All.Blocks.sync > singleton.loci.classified.txt

echo "Breakdown by dropout type:"
cut -f8 singleton.loci.classified.txt | sort | uniq -c

awk 'NR==1 || $8=="low_variation" {print $1}' singleton.loci.classified.txt > singleton.loci.lowvar
awk 'NR==1 || $8=="low_coverage"  {print $1}' singleton.loci.classified.txt > singleton.loci.lowcov
```
# Individual Blocks for outlier testing
#### B10
```{bash, eval=FALSE}
source activate CASE

bash ../scripts/sum.sh <(cut -f1,2,3,13-16 CASE.dp20.Block10.cov.sync) > CASE.B10.IS.sync
paste CASE.B10.IS.sync <(cut -f4 CASE.B10.IS.sync) <(cut -f4 CASE.B10.IS.sync)  > CASE.B10.ISsum3.sync

AV_COV=$(mawk -f ../scripts/add_cov_sync <(cut -f13-16 --complement CASE.dp20.Block10.cov.sync) | mawk '{sum=sum+$21} END {print sum/NR}')

echo $AV_COV

mawk -f ../scripts/add_cov_sync CASE.B10.ISsum3.sync | mawk -v x=$AV_COV '$7 >= x' | mawk '!/CHR/' | cut -f1-6 > CASE.B10.ISsum3nh.sync

mawk -f ../scripts/add_cov_sync_IS CASE.B10.ISsum3.sync | mawk -v x=$AV_COV '$7 >= x'> CASE.B10.ISsum3nh.cov.sync


paste CASE.dp20.Block10.cov.sync <(mawk -f ../scripts/add_cov_sync CASE.B10.ISsum3.sync ) | mawk -v x=$AV_COV '$29 >= x' | cut -f1-22 > temp.sync

mv temp.sync CASE.dp20.Block10.COV.sync
#cp CASE.dp20.Block10.cov.sync CASE.dp20.Block10.COV.sync
mawk -f ../scripts/add_cov_sync <(cut -f13-16,20- --complement CASE.dp20.Block10.COV.sync) > temp.cov


paste temp.cov <(cut -f7 CASE.B10.ISsum3nh.cov.sync) | mawk -v OFS='\t' '{if ($18 > $19) {$18=$19; print $0} else {print $0}}' | cut -f1-18> CASE.dp20.Block10.COV
```

```{bash, eval=FALSE}
source activate random_draw

#python ../scripts/sub_sample.py CASE.dp20.Block10.COV CASE.B10.ISsum3nh.sync CASE.B10.ISs.sync
python ../scripts/sub_sample.py CASE.B10.ISsum3nh.cov.sync CASE.B10.ISsum3nh.sync CASE.B10.ISs.sync

cat <(echo -e "CHROM\tPOS\tREF\tIS_RS1\tIS_RS2\tIS_RS3") CASE.B10.ISs.sync > CASE.B10.ISsum.sync

paste <(cut -f1,2,3,4 CASE.B10.ISsum.sync) <(cut -f4 CASE.dp20.Block10.COV.sync) <(cut -f5 CASE.B10.ISsum.sync) <(cut -f5 CASE.dp20.Block10.COV.sync) <(cut -f6 CASE.B10.ISsum.sync) <(cut -f6 CASE.dp20.Block10.COV.sync)> CA.B10.sync

head -1 CA.B10.sync

mawk '!/CHR/' CA.B10.sync > CA.B10.input

paste <(cut -f1,2,3,4 CASE.B10.ISsum.sync)  <(cut -f7 CASE.dp20.Block10.COV.sync) <(cut -f5 CASE.B10.ISsum.sync) <(cut -f8 CASE.dp20.Block10.COV.sync) <(cut -f6 CASE.B10.ISsum.sync) <(cut -f9 CASE.dp20.Block10.COV.sync)> CASE.B10.sync

head -1 CASE.B10.sync
tail -n +2 CASE.B10.sync > CASE.B10.input


paste <(cut -f1,2,3,4 CASE.B10.ISsum.sync) <(cut -f17 CASE.dp20.Block10.COV.sync) <(cut -f5 CASE.B10.ISsum.sync) <(cut -f19 CASE.dp20.Block10.COV.sync) <(cut -f6 CASE.B10.ISsum.sync) <(cut -f18 CASE.dp20.Block10.COV.sync) > SE.B10.sync

head -1 SE.B10.sync
tail -n +2 SE.B10.sync > SE.B10.input


paste <(cut -f1,2,3,4 CASE.B10.ISsum.sync) <(cut -f10 CASE.dp20.Block10.COV.sync) <(cut -f5 CASE.B10.ISsum.sync) <(cut -f11 CASE.dp20.Block10.COV.sync) <(cut -f6 CASE.B10.ISsum.sync) <(cut -f12 CASE.dp20.Block10.COV.sync)> CON.B10.sync

head -1 CON.B10.sync
tail -n +2 CON.B10.sync | mawk '!/0:0:0:0:0:0/' > CON.B10.input
```

#### B11
```{bash, eval=FALSE}
AV_COV=$(mawk -f ../scripts/add_cov_sync <(cut -f16-19 --complement CASE.dp20.Block11.cov.sync) | mawk '{sum=sum+$22} END {print sum/NR}')

echo $AV_COV

bash ../scripts/sum.sh <(cut -f1,2,3,16-19 CASE.dp20.Block11.cov.sync) > CASE.B11.IS.sync
paste CASE.B11.IS.sync <(cut -f4 CASE.B11.IS.sync) <(cut -f4 CASE.B11.IS.sync) <(cut -f4 CASE.B11.IS.sync) > CASE.B11.ISsum4.sync

mawk -f ../scripts/add_cov_sync CASE.B11.ISsum4.sync | mawk -v x=$AV_COV '$8 >= x' | mawk '!/CHR/' | cut -f1-7 > CASE.B11.ISsum4nh.sync

paste CASE.dp20.Block11.cov.sync <(mawk -f ../scripts/add_cov_sync CASE.B11.ISsum4.sync ) | mawk -v x=$AV_COV '$34 >= x' | cut -f1-23 > temp.sync

mv temp.sync CASE.dp20.Block11.COV.sync

mawk -f ../scripts/add_cov_sync_IS CASE.B11.ISsum4.sync | mawk -v x=$AV_COV '$8 >= x'  > CASE.B11.ISsum4.cov.sync
mawk -f ../scripts/add_cov_sync <(cut -f16-19 --complement CASE.dp20.Block11.COV.sync) > CASE.dp20.Block11.COV

source activate random_draw

#python ../scripts/sub_sample.py CASE.dp20.Block11.COV CASE.B11.ISsum4nh.sync CASE.B11.ISs.sync
python ../scripts/sub_sample.py CASE.B11.ISsum4.cov.sync CASE.B11.ISsum4nh.sync CASE.B11.ISs.sync

cat <(echo -e "CHROM\tPOS\tREF\tIS_RS1\tIS_RS2\tIS_RS3\tIS_R4") CASE.B11.ISs.sync > CASE.B11.ISsum.sync

paste <(cut -f1,2,3,4 CASE.B11.ISsum.sync) <(cut -f4 CASE.dp20.Block11.COV.sync) <(cut -f5 CASE.B11.ISsum.sync) <(cut -f 5 CASE.dp20.Block11.COV.sync) <(cut -f6 CASE.B11.ISsum.sync) <(cut -f6 CASE.dp20.Block11.COV.sync) <(cut -f7 CASE.B11.ISsum.sync) <(cut -f7 CASE.dp20.Block11.COV.sync) > CA.B11.sync

head -1 CA.B11.sync
tail -n +2 CA.B11.sync > CA.B11.input

paste <(cut -f1,2,3,4 CASE.B11.ISsum.sync) <(cut -f8 CASE.dp20.Block11.COV.sync) <(cut -f5 CASE.B11.ISsum.sync) <(cut -f 9 CASE.dp20.Block11.COV.sync) <(cut -f6 CASE.B11.ISsum.sync) <(cut -f10 CASE.dp20.Block11.COV.sync) <(cut -f7 CASE.B11.ISsum.sync) <(cut -f11 CASE.dp20.Block11.COV.sync) > CASE.B11.sync

head -1 CASE.B11.sync
tail -n +2 CASE.B11.sync > CASE.B11.input

paste <(cut -f1,2,3,4 CASE.B11.ISsum.sync) <(cut -f20 CASE.dp20.Block11.COV.sync) <(cut -f5 CASE.B11.ISsum.sync) <(cut -f 21 CASE.dp20.Block11.COV.sync) <(cut -f6 CASE.B11.ISsum.sync) <(cut -f22 CASE.dp20.Block11.COV.sync) <(cut -f7 CASE.B11.ISsum.sync) <(cut -f23 CASE.dp20.Block11.COV.sync) > SE.B11.sync

head -1 SE.B11.sync
tail -n +2 SE.B11.sync > SE.B11.input

paste <(cut -f1,2,3,4 CASE.B11.ISsum.sync) <(cut -f12 CASE.dp20.Block11.COV.sync) <(cut -f5 CASE.B11.ISsum.sync) <(cut -f 13 CASE.dp20.Block11.COV.sync) <(cut -f6 CASE.B11.ISsum.sync) <(cut -f14 CASE.dp20.Block11.COV.sync) <(cut -f7 CASE.B11.ISsum.sync) <(cut -f15 CASE.dp20.Block11.COV.sync) > CON.B11.sync

head -1 CON.B11.sync
tail -n +2 CON.B11.sync > CON.B11.input
```
#### B12


```{bash, eval=FALSE}
source activate CASE

bash ../scripts/sum.sh <(cut -f1,2,3,16-19 CASE.dp20.Block12.cov.sync) > CASE.B12.IS.sync
paste CASE.B12.IS.sync <(cut -f4 CASE.B12.IS.sync) <(cut -f4 CASE.B12.IS.sync) <(cut -f4 CASE.B12.IS.sync) > CASE.B12.ISsum4.sync

AV_COV=$(mawk -f ../scripts/add_cov_sync <(cut -f16-19 --complement CASE.dp20.Block12.cov.sync) | mawk '{sum=sum+$22} END {print sum/NR}')

echo $AV_COV

mawk -f ../scripts/add_cov_sync CASE.B12.ISsum4.sync | mawk -v x=$AV_COV '$8 >= x' | mawk '!/CHR/' | cut -f1-7 > CASE.B12.ISsum4nh.sync

paste CASE.dp20.Block12.cov.sync <(mawk -f ../scripts/add_cov_sync CASE.B12.ISsum4.sync ) | mawk -v x=$AV_COV '$34 >= x' | cut -f1-26 > temp.sync

mv -f temp.sync CASE.dp20.Block12.COV.sync

mawk -f ../scripts/add_cov_sync_IS CASE.B12.ISsum4.sync | mawk -v x=$AV_COV '$8 >= x'  > CASE.B12.ISsum4nh.cov.sync

mawk -f ../scripts/add_cov_sync <(cut -f16-19,24- --complement CASE.dp20.Block12.COV.sync) > CASE.dp20.Block12.COV


paste CASE.dp20.Block12.COV <(cut -f8 CASE.B12.ISsum4nh.cov.sync) | mawk -v OFS='\t' '{if ($22 > $23) {$22=$23; print $0} else {print $0}}' > temp.cov.sync

cut -f1-22 temp.cov.sync > CASE.dp20.Block12.COV
rm temp.cov.sync

```

```{bash, eval=FALSE}
source activate random_draw

#python ../scripts/sub_sample.py CASE.dp20.Block12.COV CASE.B12.ISsum4nh.sync CASE.B12.ISs.sync
python ../scripts/sub_sample.py CASE.B12.ISsum4nh.cov.sync CASE.B12.ISsum4nh.sync CASE.B12.ISs.sync

cat <(echo -e "CHROM\tPOS\tREF\tIS_RS1\tIS_RS2\tIS_RS3\tIS_R4") CASE.B12.ISs.sync > CASE.B12.ISsum.sync

paste <(cut -f1,2,3,4 CASE.B12.ISsum.sync) <(cut -f4 CASE.dp20.Block12.COV.sync) <(cut -f5 CASE.B12.ISsum.sync) <(cut -f 5 CASE.dp20.Block12.COV.sync) <(cut -f6 CASE.B12.ISsum.sync) <(cut -f6 CASE.dp20.Block12.COV.sync) <(cut -f7 CASE.B12.ISsum.sync) <(cut -f7 CASE.dp20.Block12.COV.sync) > CA.B12.sync

head -1 CA.B12.sync
tail -n +2 CA.B12.sync > CA.B12.input

paste <(cut -f1,2,3,4 CASE.B12.ISsum.sync) <(cut -f8 CASE.dp20.Block12.COV.sync) <(cut -f5 CASE.B12.ISsum.sync) <(cut -f 9 CASE.dp20.Block12.COV.sync) <(cut -f6 CASE.B12.ISsum.sync) <(cut -f10 CASE.dp20.Block12.COV.sync) <(cut -f7 CASE.B12.ISsum.sync) <(cut -f11 CASE.dp20.Block12.COV.sync) > CASE.B12.sync

head -1 CASE.B12.sync
tail -n +2 CASE.B12.sync > CASE.B12.input

paste <(cut -f1,2,3,4 CASE.B12.ISsum.sync) <(cut -f20 CASE.dp20.Block12.COV.sync) <(cut -f5 CASE.B12.ISsum.sync) <(cut -f 21 CASE.dp20.Block12.COV.sync) <(cut -f6 CASE.B12.ISsum.sync) <(cut -f22 CASE.dp20.Block12.COV.sync) <(cut -f7 CASE.B12.ISsum.sync) <(cut -f23 CASE.dp20.Block12.COV.sync) > SE.B12.sync

head -1 SE.B12.sync
tail -n +2 SE.B12.sync > SE.B12.input

paste <(cut -f1,2,3,4 CASE.B12.ISsum.sync) <(cut -f12 CASE.dp20.Block12.COV.sync) <(cut -f5 CASE.B12.ISsum.sync) <(cut -f 13 CASE.dp20.Block12.COV.sync) <(cut -f6 CASE.B12.ISsum.sync) <(cut -f14 CASE.dp20.Block12.COV.sync) <(cut -f7 CASE.B12.ISsum.sync) <(cut -f15 CASE.dp20.Block12.COV.sync) > CON.B12.sync

head -1 CON.B12.sync
tail -n +2 CON.B12.sync > CON.B12.input

```
### Calculate P-values

#### Modified CMH
```{r}
ca.b10.sync <- read.sync(file="CA.B10.input", gen=c(0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3,3))
ca.b10.cov <- poolSeq::coverage(ca.b10.sync,gen=c(0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3,3))
ca.b10.af <- af(ca.b10.sync,gen=c(0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3,3))

case.b10.sync <- read.sync(file="CASE.B10.input", gen=c(0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3,3))
case.b10.cov <- poolSeq::coverage(case.b10.sync,gen=c(0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3,3))
case.b10.af <- af(case.b10.sync,gen=c(0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3,3))

se.b10.sync <- read.sync(file="SE.B10.input", gen=c(0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3,3))
se.b10.cov <- poolSeq::coverage(se.b10.sync,gen=c(0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3,3))
se.b10.af <- af(se.b10.sync,gen=c(0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3,3))

con.b10.sync <- read.sync(file="CON.B10.input", gen=c(0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3,3))
con.b10.cov <- poolSeq::coverage(con.b10.sync,gen=c(0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3,3))
con.b10.af <- af(con.b10.sync,gen=c(0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3,3))
```

```{r}
ca.b10.pvals <- adapted.cmh.test(freq=ca.b10.af, coverage=ca.b10.cov, Ne=rep(250, 3), gen=c(0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3,3), poolSize=rep(c(40000,10000), ncol(ca.b10.af)/2), MeanStart = TRUE, mincov =20)

pcadf <- as.data.table(cbind(row.names(ca.b10.af),ca.b10.pvals))
colnames(pcadf) <- c("Locus","PVAL")
pcadf$GROUP <- "PCA"


case.b10.pvals <- adapted.cmh.test(freq=case.b10.af, coverage=case.b10.cov, Ne=rep(250, 3), gen=c(0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3,3), poolSize=rep(c(40000,10000), ncol(case.b10.af)/2), MeanStart = TRUE, mincov =20)

pcasedf <- as.data.table(cbind(row.names(case.b10.af),case.b10.pvals))
colnames(pcasedf) <- c("Locus","PVAL")
pcasedf$GROUP <- "PCASE"


se.b10.pvals <- adapted.cmh.test(freq=se.b10.af, coverage=se.b10.cov, Ne=rep(250, 3), gen=c(0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3,3), poolSize=rep(c(40000,10000), ncol(se.b10.af)/2), MeanStart = TRUE, mincov =20)

psedf <- as.data.table(cbind(row.names(se.b10.af),se.b10.pvals))
colnames(psedf) <- c("Locus","PVAL")
psedf$GROUP <- "PSE"


con.b10.pvals <- adapted.cmh.test(freq=con.b10.af, coverage=con.b10.cov, Ne=rep(250, 3), gen=c(0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3,3), poolSize=rep(c(40000,10000), ncol(con.b10.af)/2), MeanStart = TRUE, mincov =20)

pcondf <- as.data.table(cbind(row.names(con.b10.af),con.b10.pvals))
colnames(pcondf) <- c("Locus","PVAL")
pcondf$GROUP <- "PCON"

B10.pval.table <- bind_rows(pcadf,pcasedf,pcondf,psedf)
B10.pval.table <- B10.pval.table %>%
  separate(Locus, into = c("CHROM", "BP"), sep = "\\.(?=[^.]+$)")
B10.pval.table$PVAL <- as.numeric(B10.pval.table$PVAL)
```

```{r}
ca.b11.sync <- read.sync(file="CA.B11.input", gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4 ))
ca.b11.cov <- poolSeq::coverage(ca.b11.sync,gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4 ))
ca.b11.af <- af(ca.b11.sync,gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4 ))

case.b11.sync <- read.sync(file="CASE.B11.input", gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4 ))
case.b11.cov <- poolSeq::coverage(case.b11.sync,gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4 ))
case.b11.af <- af(case.b11.sync,gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4 ))

se.b11.sync <- read.sync(file="SE.B11.input", gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4 ))
se.b11.cov <- poolSeq::coverage(se.b11.sync,gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4 ))
se.b11.af <- af(se.b11.sync,gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4 ))

con.b11.sync <- read.sync(file="CON.B11.input", gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4 ))
con.b11.cov <- poolSeq::coverage(con.b11.sync,gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4 ))
con.b11.af <- af(con.b11.sync,gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4 ))
```

```{r}
ca.b11.pvals <- adapted.cmh.test(freq=ca.b11.af, coverage=ca.b11.cov, Ne=rep(1000, 4), gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4, 4), poolSize=rep(c(40000,10000), ncol(ca.b11.af)/2), MeanStart = TRUE, mincov =14)

pcadf <- as.data.table(cbind(row.names(ca.b11.af),ca.b11.pvals))
colnames(pcadf) <- c("Locus","PVAL")
pcadf$GROUP <- "PCA"

case.b11.pvals <- adapted.cmh.test(freq=case.b11.af, coverage=case.b11.cov, Ne=rep(1000, 4), gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4, 4), poolSize=rep(c(40000,10000), ncol(case.b11.af)/2), MeanStart = TRUE, mincov =14)

pcasedf <- as.data.table(cbind(row.names(case.b11.af),case.b11.pvals))
colnames(pcasedf) <- c("Locus","PVAL")
pcasedf$GROUP <- "PCASE"

se.b11.pvals <- adapted.cmh.test(freq=se.b11.af, coverage=se.b11.cov, Ne=rep(1000, 4), gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4, 4), poolSize=rep(c(40000,10000), ncol(se.b11.af)/2), MeanStart = TRUE, mincov =14)

psedf <- as.data.table(cbind(row.names(se.b11.af),se.b11.pvals))
colnames(psedf) <- c("Locus","PVAL")
psedf$GROUP <- "PSE"

con.b11.pvals <- adapted.cmh.test(freq=con.b11.af, coverage=con.b11.cov, Ne=rep(1000, 4), gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4, 4), poolSize=rep(c(40000,10000), ncol(con.b11.af)/2), MeanStart = TRUE, mincov =14)

pcondf <- as.data.table(cbind(row.names(con.b11.af),con.b11.pvals))
colnames(pcondf) <- c("Locus","PVAL")
pcondf$GROUP <- "PCON"


B11.pval.table <- bind_rows(pcadf,pcasedf,pcondf,psedf)
B11.pval.table <- B11.pval.table %>%
  separate(Locus, into = c("CHROM", "BP"), sep = "\\.(?=[^.]+$)")
B11.pval.table$PVAL <- as.numeric(B11.pval.table$PVAL)
```

```{r}
ca.b12.sync <- read.sync(file="CA.B12.input", gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4 ))
ca.b12.cov <- poolSeq::coverage(ca.b12.sync,gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4 ))
ca.b12.af <- af(ca.b12.sync,gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4 ))

case.b12.sync <- read.sync(file="CASE.B12.input", gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4 ))
case.b12.cov <- poolSeq::coverage(case.b12.sync,gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4 ))
case.b12.af <- af(case.b12.sync,gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4 ))

se.b12.sync <- read.sync(file="SE.B12.input", gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4 ))
se.b12.cov <- poolSeq::coverage(se.b12.sync,gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4 ))
se.b12.af <- af(se.b12.sync,gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4 ))

con.b12.sync <- read.sync(file="CON.B12.input", gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4 ))
con.b12.cov <- poolSeq::coverage(con.b12.sync,gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4 ))
con.b12.af <- af(con.b12.sync,gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4 ))
```
```{r}
ca.b12.pvals <- adapted.cmh.test(freq=ca.b12.af, coverage=ca.b12.cov, Ne=rep(1000, 4), gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4, 4), poolSize=rep(c(40000,10000), ncol(ca.b12.af)/2), MeanStart = TRUE, mincov =20)

pcadf <- as.data.table(cbind(row.names(ca.b12.af),ca.b12.pvals))
colnames(pcadf) <- c("Locus","PVAL")
pcadf$GROUP <- "PCA"

case.b12.pvals <- adapted.cmh.test(freq=case.b12.af, coverage=case.b12.cov, Ne=rep(1000, 4), gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4, 4), poolSize=rep(c(40000,10000), ncol(case.b12.af)/2), MeanStart = TRUE, mincov =20)

pcasedf <- as.data.table(cbind(row.names(case.b12.af),case.b12.pvals))
colnames(pcasedf) <- c("Locus","PVAL")
pcasedf$GROUP <- "PCASE"

se.b12.pvals <- adapted.cmh.test(freq=se.b12.af, coverage=se.b12.cov, Ne=rep(1000, 4), gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4, 4), poolSize=rep(c(40000,10000), ncol(se.b12.af)/2), MeanStart = TRUE, mincov =20)

psedf <- as.data.table(cbind(row.names(se.b12.af),se.b12.pvals))
colnames(psedf) <- c("Locus","PVAL")
psedf$GROUP <- "PSE"



con.b12.pvals <- adapted.cmh.test(freq=con.b12.af, coverage=con.b12.cov, Ne=rep(1000, 4), gen=c(0, 1, 0, 1, 0, 1, 0, 1), repl=c(1, 1, 2, 2, 3, 3, 4, 4), poolSize=rep(c(40000,10000), ncol(con.b12.af)/2), MeanStart = TRUE, mincov =20)

pcondf <- as.data.table(cbind(row.names(con.b12.af),con.b12.pvals))
colnames(pcondf) <- c("Locus","PVAL")
pcondf$GROUP <- "PCON"

B12.pval.table <- bind_rows(pcadf,pcasedf,pcondf,psedf)
B12.pval.table <- B12.pval.table %>%
  separate(Locus, into = c("CHROM", "BP"), sep = "\\.(?=[^.]+$)")
B12.pval.table$PVAL <- as.numeric(B12.pval.table$PVAL)
```

### Across all blocks
#### Create sync file
```{bash, eval=FALSE}
source activate CASE

head -1 CASE.All.Blocks.cov.sync > h.temp
tail -n +2 CASE.All.Blocks.cov.sync | sort -k1,1 -k2,2n > b.temp

cat h.temp b.temp > CASE.All.Blocks.cov.s.sync
rm h.temp b.temp
cp CASE.All.Blocks.cov.sync CASE.All.Blocks.cov.s.sync

bash ../scripts/sum.sh <(cut -f1,2,3,37,39,41,43 CASE.All.Blocks.cov.s.sync) > CASE.B10.AB.ISsum.sync
bash ../scripts/sum.sh <(cut -f1,2,3,38,40,42,44 CASE.All.Blocks.cov.s.sync) > CASE.B11.AB.ISsum.sync
bash ../scripts/sum.sh <(cut -f1,2,3,45-48 CASE.All.Blocks.cov.s.sync) > CASE.B12.AB.ISsum.sync


paste CASE.All.Blocks.cov.s.sync <(mawk -f ../scripts/add_cov_sync CASE.B10.AB.ISsum.sync | cut -f5 ) <(mawk -f ../scripts/add_cov_sync CASE.B11.AB.ISsum.sync | cut -f 5) <(mawk -f ../scripts/add_cov_sync CASE.B12.AB.ISsum.sync | cut -f5) | mawk '$63 >72 && $64 > 72 && $65 > 72 && $61 > 1' | cut -f1-62 > CASE.All.Blocks.cov.fil.sync

bash ../scripts/sum.sh <(cut -f1,2,3,37,39,41,43 CASE.All.Blocks.cov.fil.sync) > CASE.B10.AB.ISsum.sync
bash ../scripts/sum.sh <(cut -f1,2,3,38,40,42,44 CASE.All.Blocks.cov.fil.sync) > CASE.B11.AB.ISsum.sync
bash ../scripts/sum.sh <(cut -f1,2,3,45-48 CASE.All.Blocks.cov.fil.sync) > CASE.B12.AB.ISsum.sync

mawk -f ../scripts/add_cov_sync <(cut -f1-3,7,9,12,15,19,22,26,30,32,51,52,55  CASE.All.Blocks.cov.fil.sync ) > B10.AB.cov.sync
mawk -f ../scripts/add_cov_sync <(cut -f1-3,5,10,14,16,23,24,27,29,35,49,54,58 CASE.All.Blocks.cov.fil.sync) > B11.AB.cov.sync
#mawk -f ../scripts/add_cov_sync <(cut -f1-3,5,8,10,14,16,21,23,24,27,29,33,35,49,53,54,58 CASE.All.Blocks.cov.fil.sync) > B11.AB.cov.sync

mawk -f ../scripts/add_cov_sync <(cut -f1-3,4,6,13,17,18,20,28,31,34,56,57,59 CASE.All.Blocks.cov.fil.sync) > B12.AB.cov.sync
#mawk -f ../scripts/add_cov_sync <(cut -f1-3,4,6,11,13,17,18,20,25,28,31,34,36,50,56,57,59 CASE.All.Blocks.cov.fil.sync) > B12.AB.cov.sync

#paste CASE.B10.AB.ISsum.sync <(cut -f4 CASE.B10.AB.ISsum.sync) <(cut -f4 CASE.B10.AB.ISsum.sync)   > CASE.B10.AB.ISsum3.sync

#paste CASE.B11.AB.ISsum.sync <(cut -f4 CASE.B11.AB.ISsum.sync) <(cut -f4 CASE.B11.AB.ISsum.sync)  > CASE.B11.AB.ISsum4.sync

#paste CASE.B12.AB.ISsum.sync <(cut -f4 CASE.B12.AB.ISsum.sync) <(cut -f4 CASE.B12.AB.ISsum.sync)  > CASE.B12.AB.ISsum4.sync

paste CASE.B10.AB.ISsum.sync <(cut -f4 CASE.B10.AB.ISsum.sync) <(cut -f4 CASE.B10.AB.ISsum.sync) <(cut -f4 CASE.B10.AB.ISsum.sync)  > CASE.B10.AB.ISsum3.sync
paste CASE.B11.AB.ISsum.sync <(cut -f4 CASE.B11.AB.ISsum.sync) <(cut -f4 CASE.B11.AB.ISsum.sync) <(cut -f4 CASE.B11.AB.ISsum.sync)  > CASE.B11.AB.ISsum4.sync
paste CASE.B12.AB.ISsum.sync <(cut -f4 CASE.B12.AB.ISsum.sync) <(cut -f4 CASE.B12.AB.ISsum.sync) <(cut -f4 CASE.B12.AB.ISsum.sync)  > CASE.B12.AB.ISsum4.sync


mawk -f ../scripts/add_cov_sync_IS CASE.B10.AB.ISsum3.sync  > CASE.B10.AB.ISsum3.cov.sync
mawk -f ../scripts/add_cov_sync_IS CASE.B11.AB.ISsum4.sync  > CASE.B11.AB.ISsum4.cov.sync
mawk -f ../scripts/add_cov_sync_IS CASE.B12.AB.ISsum4.sync  > CASE.B12.AB.ISsum4.cov.sync

paste B10.AB.cov.sync <(cut -f7 CASE.B10.AB.ISsum3.cov.sync) | mawk -v OFS='\t' '{if (NR > 1 && $19 > $20) {$19=$20; print $0} else {print $0}}' > temp.cov.sync
cut -f1-18 temp.cov.sync > B10.AB.cov.sync

paste B11.AB.cov.sync <(cut -f7 CASE.B11.AB.ISsum4.cov.sync) | mawk -v OFS='\t' '{if (NR > 1 && $19 > $20) {$19=$20; print $0} else {print $0}}' > temp.cov.sync
cut -f1-18 temp.cov.sync > B11.AB.cov.sync

paste B12.AB.cov.sync <(cut -f7 CASE.B12.AB.ISsum4.cov.sync) | mawk -v OFS='\t' '{if (NR > 1 && $19 > $20) {$19=$20; print $0} else {print $0}}' > temp.cov.sync
cut -f1-18 temp.cov.sync > B12.AB.cov.sync
rm temp.cov.sync

```

```{bash, eval=FALSE}
source activate random_draw
python ../scripts/sub_sample.py CASE.B10.AB.ISsum3.cov.sync <( mawk '!/CHR/' CASE.B10.AB.ISsum3.sync) CASE.B10.ISs.AB.sync
python ../scripts/sub_sample.py CASE.B11.AB.ISsum4.cov.sync <( mawk '!/CHR/' CASE.B11.AB.ISsum4.sync) CASE.B11.ISs.AB.sync
python ../scripts/sub_sample.py CASE.B12.AB.ISsum4.cov.sync <(mawk '!/CHR/' CASE.B12.AB.ISsum4.sync) CASE.B12.ISs.AB.sync
```
```{bash}
cat <(echo -e "CHROM\tPOS\tREF\tISB11_RS1\tISB11_RS2\tISB11_RS3\tISB11_RS4") CASE.B11.ISs.AB.sync > CASE.B11.ISsum.AB.sync
cat <(echo -e "CHROM\tPOS\tREF\tISB10_RS1\tISB10_RS2\tISB10_RS3\tISB10_RS4") CASE.B10.ISs.AB.sync > CASE.B10.ISsum.AB.sync
cat <(echo -e "CHROM\tPOS\tREF\tISB12_RS1\tISB12_RS2\tISB12_RS3\tISB12_RS4") CASE.B12.ISs.AB.sync > CASE.B12.ISsum.AB.sync

paste <(cut -f1-4 CASE.B10.ISsum.AB.sync) <(cut -f15 CASE.All.Blocks.cov.fil.sync) <(cut -f5 CASE.B10.ISsum.AB.sync) <(cut -f19 CASE.All.Blocks.cov.fil.sync) <(cut -f6 CASE.B10.ISsum.AB.sync) <(cut -f22 CASE.All.Blocks.cov.fil.sync) <(cut -f4 CASE.B11.ISsum.AB.sync) <(cut -f16 CASE.All.Blocks.cov.fil.sync) <(cut -f5 CASE.B11.ISsum.AB.sync) <(cut -f21 CASE.All.Blocks.cov.fil.sync) <(cut -f6 CASE.B11.ISsum.AB.sync) <(cut -f23 CASE.All.Blocks.cov.fil.sync) <(cut -f7 CASE.B11.ISsum.AB.sync) <(cut -f24 CASE.All.Blocks.cov.fil.sync) <(cut -f4 CASE.B12.ISsum.AB.sync) <(cut -f17 CASE.All.Blocks.cov.fil.sync) <(cut -f5 CASE.B12.ISsum.AB.sync) <(cut -f18 CASE.All.Blocks.cov.fil.sync) <(cut -f6 CASE.B12.ISsum.AB.sync) <(cut -f20 CASE.All.Blocks.cov.fil.sync) <(cut -f7 CASE.B12.ISsum.AB.sync) <(cut -f25 CASE.All.Blocks.cov.fil.sync) > CASE.AB.sync

#paste <(cut -f1-4 CASE.B10.ISsum.AB.sync) <(cut -f15 CASE.All.Blocks.cov.fil.sync) <(cut -f5 CASE.B10.ISsum.AB.sync) <(cut -f19 CASE.All.Blocks.cov.fil.sync) <(cut -f6 CASE.B10.ISsum.AB.sync) <(cut -f22 CASE.All.Blocks.cov.fil.sync) <(cut -f4 CASE.B11.ISsum.AB.sync) <(cut -f16 CASE.All.Blocks.cov.fil.sync)  <(cut -f5 CASE.B11.ISsum.AB.sync) <(cut -f23 CASE.All.Blocks.cov.fil.sync) <(cut -f6 CASE.B11.ISsum.AB.sync) <(cut -f24 CASE.All.Blocks.cov.fil.sync) <(cut -f4 CASE.B12.ISsum.AB.sync) <(cut -f17 CASE.All.Blocks.cov.fil.sync) <(cut -f5 CASE.B12.ISsum.AB.sync) <(cut -f18 CASE.All.Blocks.cov.fil.sync) <(cut -f6 CASE.B12.ISsum.AB.sync) <(cut -f20 CASE.All.Blocks.cov.fil.sync)  > CASE.AB.sync

tail -n +2 CASE.AB.sync | mawk '$2 != 74609903 && $2 != 93711267 && $2 != 36030885' > CASE.AB.input 

paste <(cut -f1-4 CASE.B10.ISsum.AB.sync) <(cut -f7 CASE.All.Blocks.cov.fil.sync) <(cut -f5 CASE.B10.ISsum.AB.sync) <(cut -f9 CASE.All.Blocks.cov.fil.sync) <(cut -f6 CASE.B10.ISsum.AB.sync) <(cut -f12 CASE.All.Blocks.cov.fil.sync) <(cut -f4 CASE.B11.ISsum.AB.sync) <(cut -f5 CASE.All.Blocks.cov.fil.sync) <(cut -f5 CASE.B11.ISsum.AB.sync) <(cut -f8 CASE.All.Blocks.cov.fil.sync) <(cut -f6 CASE.B11.ISsum.AB.sync) <(cut -f10 CASE.All.Blocks.cov.fil.sync) <(cut -f7 CASE.B11.ISsum.AB.sync) <(cut -f14 CASE.All.Blocks.cov.fil.sync) <(cut -f4 CASE.B12.ISsum.AB.sync) <(cut -f4 CASE.All.Blocks.cov.fil.sync) <(cut -f5 CASE.B12.ISsum.AB.sync) <(cut -f6 CASE.All.Blocks.cov.fil.sync) <(cut -f6 CASE.B12.ISsum.AB.sync) <(cut -f11 CASE.All.Blocks.cov.fil.sync) <(cut -f7 CASE.B12.ISsum.AB.sync) <(cut -f13 CASE.All.Blocks.cov.fil.sync) > CA.AB.sync

#paste <(cut -f1-4 CASE.B10.ISsum.AB.sync) <(cut -f7 CASE.All.Blocks.cov.fil.sync) <(cut -f5 CASE.B10.ISsum.AB.sync) <(cut -f9 CASE.All.Blocks.cov.fil.sync) <(cut -f6 CASE.B10.ISsum.AB.sync) <(cut -f12 CASE.All.Blocks.cov.fil.sync) <(cut -f4 CASE.B11.ISsum.AB.sync) <(cut -f5 CASE.All.Blocks.cov.fil.sync)  <(cut -f5 CASE.B11.ISsum.AB.sync) <(cut -f10 CASE.All.Blocks.cov.fil.sync) <(cut -f6 CASE.B11.ISsum.AB.sync) <(cut -f14 CASE.All.Blocks.cov.fil.sync) <(cut -f4 CASE.B12.ISsum.AB.sync) <(cut -f4 CASE.All.Blocks.cov.fil.sync) <(cut -f5 CASE.B12.ISsum.AB.sync) <(cut -f6 CASE.All.Blocks.cov.fil.sync)  <(cut -f6 CASE.B12.ISsum.AB.sync) <(cut -f13 CASE.All.Blocks.cov.fil.sync) > CA.AB.sync

tail -n +2 CA.AB.sync | mawk '$2 != 93711267 && $2 != 59024150 && $2 != 2532550'> CA.AB.input 

paste <(cut -f1-4 CASE.B10.ISsum.AB.sync) <(cut -f26 CASE.All.Blocks.cov.fil.sync) <(cut -f5 CASE.B10.ISsum.AB.sync) <(cut -f30 CASE.All.Blocks.cov.fil.sync) <(cut -f6 CASE.B10.ISsum.AB.sync) <(cut -f32 CASE.All.Blocks.cov.fil.sync) <(cut -f4 CASE.B11.ISsum.AB.sync) <(cut -f27 CASE.All.Blocks.cov.fil.sync) <(cut -f5 CASE.B11.ISsum.AB.sync) <(cut -f29 CASE.All.Blocks.cov.fil.sync) <(cut -f6 CASE.B11.ISsum.AB.sync) <(cut -f33 CASE.All.Blocks.cov.fil.sync) <(cut -f7 CASE.B11.ISsum.AB.sync) <(cut -f35 CASE.All.Blocks.cov.fil.sync) <(cut -f4 CASE.B12.ISsum.AB.sync) <(cut -f28 CASE.All.Blocks.cov.fil.sync) <(cut -f5 CASE.B12.ISsum.AB.sync) <(cut -f31 CASE.All.Blocks.cov.fil.sync) <(cut -f6 CASE.B12.ISsum.AB.sync) <(cut -f34 CASE.All.Blocks.cov.fil.sync) <(cut -f7 CASE.B12.ISsum.AB.sync) <(cut -f36 CASE.All.Blocks.cov.fil.sync) > CON.AB.sync

#paste <(cut -f1-4 CASE.B10.ISsum.AB.sync) <(cut -f26 CASE.All.Blocks.cov.fil.sync) <(cut -f5 CASE.B10.ISsum.AB.sync) <(cut -f30 CASE.All.Blocks.cov.fil.sync) <(cut -f6 CASE.B10.ISsum.AB.sync) <(cut -f32 CASE.All.Blocks.cov.fil.sync) <(cut -f4 CASE.B11.ISsum.AB.sync) <(cut -f27 CASE.All.Blocks.cov.fil.sync) <(cut -f5 CASE.B11.ISsum.AB.sync) <(cut -f29 CASE.All.Blocks.cov.fil.sync) <(cut -f6 CASE.B11.ISsum.AB.sync) <(cut -f35 CASE.All.Blocks.cov.fil.sync) <(cut -f4 CASE.B12.ISsum.AB.sync) <(cut -f28 CASE.All.Blocks.cov.fil.sync) <(cut -f5 CASE.B12.ISsum.AB.sync) <(cut -f31 CASE.All.Blocks.cov.fil.sync) <(cut -f6 CASE.B12.ISsum.AB.sync) <(cut -f34 CASE.All.Blocks.cov.fil.sync)  > CON.AB.sync

tail -n +2 CON.AB.sync | mawk '$2 != 34804390 && $2 != 54895214 && $2 !=  49000140 && $2 != 15140923' > CON.AB.input 

paste <(cut -f1-4 CASE.B10.ISsum.AB.sync) <(cut -f51 CASE.All.Blocks.cov.fil.sync) <(cut -f5 CASE.B10.ISsum.AB.sync) <(cut -f52 CASE.All.Blocks.cov.fil.sync) <(cut -f6 CASE.B10.ISsum.AB.sync) <(cut -f55 CASE.All.Blocks.cov.fil.sync) <(cut -f4 CASE.B11.ISsum.AB.sync) <(cut -f49 CASE.All.Blocks.cov.fil.sync) <(cut -f5 CASE.B11.ISsum.AB.sync) <(cut -f53 CASE.All.Blocks.cov.fil.sync) <(cut -f6 CASE.B11.ISsum.AB.sync) <(cut -f54 CASE.All.Blocks.cov.fil.sync) <(cut -f7 CASE.B11.ISsum.AB.sync) <(cut -f58 CASE.All.Blocks.cov.fil.sync) <(cut -f4 CASE.B12.ISsum.AB.sync) <(cut -f50 CASE.All.Blocks.cov.fil.sync) <(cut -f5 CASE.B12.ISsum.AB.sync) <(cut -f56 CASE.All.Blocks.cov.fil.sync) <(cut -f6 CASE.B12.ISsum.AB.sync) <(cut -f57 CASE.All.Blocks.cov.fil.sync) <(cut -f7 CASE.B12.ISsum.AB.sync) <(cut -f59 CASE.All.Blocks.cov.fil.sync) > SE.AB.sync

#paste <(cut -f1-4 CASE.B10.ISsum.AB.sync) <(cut -f51 CASE.All.Blocks.cov.fil.sync) <(cut -f5 CASE.B10.ISsum.AB.sync) <(cut -f52 CASE.All.Blocks.cov.fil.sync) <(cut -f6 CASE.B10.ISsum.AB.sync) <(cut -f55 CASE.All.Blocks.cov.fil.sync) <(cut -f4 CASE.B11.ISsum.AB.sync) <(cut -f49 CASE.All.Blocks.cov.fil.sync) <(cut -f5 CASE.B11.ISsum.AB.sync) <(cut -f54 CASE.All.Blocks.cov.fil.sync) <(cut -f6 CASE.B11.ISsum.AB.sync) <(cut -f58 CASE.All.Blocks.cov.fil.sync)  <(cut -f4 CASE.B12.ISsum.AB.sync) <(cut -f56 CASE.All.Blocks.cov.fil.sync) <(cut -f5 CASE.B12.ISsum.AB.sync) <(cut -f57 CASE.All.Blocks.cov.fil.sync) <(cut -f6 CASE.B12.ISsum.AB.sync) <(cut -f59 CASE.All.Blocks.cov.fil.sync) > SE.AB.sync

tail -n +2 SE.AB.sync | mawk '$2 != 67902213 && $2 != 19828063 && $2 != 93711267 ' > SE.AB.input 

```
#### Calculate p-values
```{r}
ca.ab.sync <- read.sync(file="CA.AB.input",gen=c(0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1),repl=c(1,1,2,2,3,3,4 ,4,5,5,6,6,7,7,8,8,9,9,10,10,11,11 ))
ca.ab.cov <- poolSeq::coverage(ca.ab.sync,gen=c(0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1),repl=c(1,1,2,2,3, 3, 4 , 4,5,5,6,6,7,7,8,8,9,9,10,10,11,11 ))
ca.ab.af <- af(ca.ab.sync,gen=c(0, 1, 0, 1, 0, 1, 0, 1,0,1,0,1,0,1,0,1,0,1,0,1,0,1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4,5,5,6,6,7,7,8,8,9,9,10,10,11,11 ))

case.ab.sync <- read.sync(file="CASE.AB.input", gen=c(0, 1, 0, 1, 0, 1, 0, 1,0,1,0,1,0,1,0,1,0,1,0,1,0,1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4,5,5,6,6,7,7,8,8,9,9,10,10,11,11 ))
case.ab.cov <- poolSeq::coverage(case.ab.sync,gen=c(0, 1, 0, 1, 0, 1, 0, 1,0,1,0,1,0,1,0,1,0,1,0,1,0,1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4,5,5,6,6,7,7,8,8,9,9,10,10,11,11 ))
case.ab.af <- af(case.ab.sync,gen=c(0, 1, 0, 1, 0, 1, 0, 1,0,1,0,1,0,1,0,1,0,1,0,1,0,1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4,5,5,6,6,7,7,8,8,9,9,10,10,11,11 ))

se.ab.sync <- read.sync(file="SE.AB.input", gen=c(0, 1, 0, 1, 0, 1, 0, 1,0,1,0,1,0,1,0,1,0,1,0,1,0,1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4,5,5,6,6,7,7,8,8,9,9,10,10,11,11 ))
se.ab.cov <- poolSeq::coverage(se.ab.sync,gen=c(0, 1, 0, 1, 0, 1, 0, 1,0,1,0,1,0,1,0,1,0,1,0,1,0,1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4,5,5,6,6,7,7,8,8,9,9,10,10,11,11 ))
se.ab.af <- af(se.ab.sync,gen=c(0, 1, 0, 1, 0, 1, 0, 1,0,1,0,1,0,1,0,1,0,1,0,1,0,1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4,5,5,6,6,7,7,8,8,9,9,10,10,11,11 ))

con.ab.sync <- read.sync(file="CON.AB.input", gen=c(0, 1, 0, 1, 0, 1, 0, 1,0,1,0,1,0,1,0,1,0,1,0,1,0,1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4,5,5,6,6,7,7,8,8,9,9,10,10,11,11 ))
con.ab.cov <- poolSeq::coverage(con.ab.sync,gen=c(0, 1, 0, 1, 0, 1, 0, 1,0,1,0,1,0,1,0,1,0,1,0,1,0,1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4,5,5,6,6,7,7,8,8,9,9,10,10,11,11 ))
con.ab.af <- af(con.ab.sync,gen=c(0, 1, 0, 1, 0, 1, 0, 1,0,1,0,1,0,1,0,1,0,1,0,1,0,1), repl=c(1, 1, 2, 2, 3, 3, 4 , 4,5,5,6,6,7,7,8,8,9,9,10,10,11,11 ))
```

```{r}
ca.ab.pvals <- adapted.cmh.test(freq=ca.ab.af, coverage=ca.ab.cov, Ne=c(250,250,250,1000,1000,1000,1000,1000,1000,1000,1000), gen=c(0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1),repl=c(1,1,2,2,3,3,4 ,4,5,5,6,6,7,7,8,8,9,9,10,10,11,11 ), poolSize=rep(c(40000,10000), ncol(ca.ab.af)/2), MeanStart = TRUE, mincov =14)

pcadf <- as.data.table(cbind(row.names(ca.ab.af),ca.ab.pvals))
colnames(pcadf) <- c("Locus","PVAL")
pcadf$GROUP <- "PCA"

case.ab.pvals <- adapted.cmh.test(freq=case.ab.af, coverage=case.ab.cov, Ne=c(250,250,250,1000,1000,1000,1000,1000,1000,1000,1000), gen=c(0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1),repl=c(1,1,2,2,3,3,4 ,4,5,5,6,6,7,7,8,8,9,9,10,10,11,11 ), poolSize=rep(c(40000,10000), ncol(case.ab.af)/2), MeanStart = TRUE, mincov =14)

pcasedf <- as.data.table(cbind(row.names(case.ab.af),case.ab.pvals))
colnames(pcasedf) <- c("Locus","PVAL")
pcasedf$GROUP <- "PCASE"

se.ab.pvals <- adapted.cmh.test(freq=se.ab.af, coverage=se.ab.cov, Ne=c(250,250,250,1000,1000,1000,1000,1000,1000,1000,1000), gen=c(0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1),repl=c(1,1,2,2,3,3,4 ,4,5,5,6,6,7,7,8,8,9,9,10,10,11,11 ), poolSize=rep(c(40000,10000), ncol(se.ab.af)/2), MeanStart = TRUE, mincov =14)

psedf <- as.data.table(cbind(row.names(se.ab.af),se.ab.pvals))
colnames(psedf) <- c("Locus","PVAL")
psedf$GROUP <- "PSE"

con.ab.pvals <- adapted.cmh.test(freq=con.ab.af, coverage=con.ab.cov, Ne=c(250,250,250,1000,1000,1000,1000,1000,1000,1000,1000), gen=c(0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1,0,1),repl=c(1,1,2,2,3,3,4 ,4,5,5,6,6,7,7,8,8,9,9,10,10,11,11 ), poolSize=rep(c(40000,10000), ncol(con.ab.af)/2), MeanStart = TRUE, mincov =14)

pcondf <- as.data.table(cbind(row.names(con.ab.af),con.ab.pvals)) 
colnames(pcondf) <- c("Locus","PVAL")
pcondf$GROUP <- "PCON"


AB.pval.table <- bind_rows(pcadf,pcasedf,pcondf,psedf)
AB.pval.table <- AB.pval.table %>%
  separate(Locus, into = c("CHROM", "BP"), sep = "\\.(?=[^.]+$)")
AB.pval.table$PVAL <- as.numeric(AB.pval.table$PVAL)
```

## Determine Significant Loci
### New Way
```{r}
# ── Step 1: Convert raw p-values to q-values for each block ──────────────────
# Qvalue_convert applies the qvalue package (pi0 = 1) to CMH p-value tables,
# returning a data frame with q-values for each treatment (QCA, QCASE, QSE, QCON)

Qvalue_convert(B10.pval.table) -> B10.pv
Qvalue_convert(B11.pval.table) -> B11.pv
Qvalue_convert(B12.pval.table) -> B12.pv
Qvalue_convert(AB.pval.table) -> AB.pv
```

```{r}
# ── Step 2: Define FDR thresholds ────────────────────────────────────────────
# alpha  = primary FDR threshold applied to treatment q-values (QCA, QCASE, QSE)
# alpha2 = CON q-value floor: SNPs must have QCON > alpha2 to exclude loci
#          that are also differentiating in the control (likely artifacts or
#          family effects rather than treatment-driven selection)
#
# Per-block alpha corrections (applied to Aggregate and Block-Specific tiers):
#   B10.alpha = 0.001 — 10x stricter than base; B10 p-values are inflated by
#               genetic drift from fewer spawning broodstock, so a tighter
#               threshold is needed to prevent B10 from dominating non-core tiers.
#   B11.alpha = 0.1   — 10x looser than base; B11 has lower coverage and fewer
#               loci, so statistical power is reduced and the threshold is relaxed.
#   Core tiers (Tier A/B) do not apply these corrections because requiring signal
#   across multiple independent blocks already controls for block-specific drift.

# ── Helper: apply_treatment_filter ───────────────────────────────────────────
# After subsetting to SNPs significant for one treatment, zero out the Sig.*
# flags for the other two treatments. This ensures that when per-treatment
# subsets are combined with bind_rows(), each row is attributed to a single
# stressor and doesn't carry spurious significance flags from the subsetting
# source data frame.
apply_treatment_filter <- function(df, keep_treatment) {
  treatments <- c("Sig.CA", "Sig.CASE", "Sig.SE")
  other <- setdiff(treatments, keep_treatment)
  df[other] <- FALSE
  df
}

# top5pct_filter: within the already-significant loci (df), retain only those
# whose treatment q-value falls in the top 1% of that significant set.
# Quantiles are computed only on loci with QCON > 0.1 so that CON-significant
# loci with inflated treatment signal do not pull the threshold up against
# genuinely treatment-specific outliers.
top5pct_filter <- function(df) {
  df_con <- subset(df, QCON > 0.1)
  subset(df,
    (Sig.CASE == TRUE & QCASE < quantile(df_con$QCASE, na.rm = TRUE, probs = 0.01)) |
    (Sig.CA   == TRUE & QCA   < quantile(df_con$QCA,   na.rm = TRUE, probs = 0.01)) |
    (Sig.SE   == TRUE & QSE   < quantile(df_con$QSE,   na.rm = TRUE, probs = 0.01))
  )
}

# ── Step 3: Pool all three blocks (unfiltered) ───────────────────────────────
# pp1 is used later to identify CON-significant SNPs across the per-block data
pp1 <- rbind(B10.pv, B11.pv, B12.pv)

# ══════════════════════════════════════════════════════════════════════════════
# TIER A: q < 0.10, significant in ALL THREE BLOCKS (Sig.Loci.3)
# ══════════════════════════════════════════════════════════════════════════════
alpha  <- 0.10
alpha2 <- 0.10


ppsig.B10.1 <- Significat_subset(B10.pv, alpha,     alpha2)
ppsig.B11.1 <- Significat_subset(B11.pv, alpha, alpha2)
ppsig.B12.1 <- Significat_subset(B12.pv, alpha,     alpha2)

ppsig.B10.1$BLOCK <- 10
ppsig.B11.1$BLOCK <- 11
ppsig.B12.1$BLOCK <- 12

ppsig3.FDR10 <- rbind(ppsig.B10.1, ppsig.B11.1, ppsig.B12.1)

# Retain only SNPs significant for a given treatment in all 3 blocks (n() > 2),
# then zero out the other treatment flags before combining
all_sig.CA   <- subset(ppsig3.FDR10, Sig.CA   == TRUE) %>%
                  group_by(SNP) %>% filter(n() > 2) %>%
                  apply_treatment_filter("Sig.CA")

all_sig.CASE <- subset(ppsig3.FDR10, Sig.CASE == TRUE) %>%
                  group_by(SNP) %>% filter(n() > 2) %>%
                  apply_treatment_filter("Sig.CASE")

all_sig.SE   <- subset(ppsig3.FDR10, Sig.SE   == TRUE) %>%
                  group_by(SNP) %>% filter(n() > 2) %>%
                  apply_treatment_filter("Sig.SE")

all_sig <- bind_rows(all_sig.CA, all_sig.CASE, all_sig.SE)
write.table(all_sig, "Sig.Loci.3", sep = "\t", row.names = FALSE, quote = FALSE)

# ══════════════════════════════════════════════════════════════════════════════
# TIER B: q < 0.05, significant in AT LEAST TWO BLOCKS (Sig.Loci.2)
# ══════════════════════════════════════════════════════════════════════════════
alpha  <- 0.05
alpha2 <- 0.10
B11.alpha <- 0.1 # Block 11 correction: 0.10

ppsig.B10.05 <- Significat_subset(B10.pv, alpha,     alpha2)
ppsig.B11.05 <- Significat_subset(B11.pv, B11.alpha, alpha2)
ppsig.B12.05 <- Significat_subset(B12.pv, alpha,     alpha2)

ppsig.B10.05$BLOCK <- 10
ppsig.B11.05$BLOCK <- 11
ppsig.B12.05$BLOCK <- 12

ppsig3.FDR05 <- rbind(ppsig.B10.05, ppsig.B11.05, ppsig.B12.05)

# Retain SNPs significant for a given treatment in at least 2 blocks (n() > 1)
multi_sig.CA   <- subset(ppsig3.FDR05, Sig.CA   == TRUE) %>%
                    group_by(SNP) %>% filter(n() > 1) %>%
                    apply_treatment_filter("Sig.CA")

multi_sig.CASE <- subset(ppsig3.FDR05, Sig.CASE == TRUE) %>%
                    group_by(SNP) %>% filter(n() > 1) %>%
                    apply_treatment_filter("Sig.CASE")

multi_sig.SE   <- subset(ppsig3.FDR05, Sig.SE   == TRUE) %>%
                    group_by(SNP) %>% filter(n() > 1) %>%
                    apply_treatment_filter("Sig.SE")

multi_sig <- rbind(multi_sig.CA, multi_sig.CASE, multi_sig.SE)
write.table(multi_sig, "Sig.Loci.2", sep = "\t", row.names = FALSE, quote = FALSE)

# ── Per-block q < 0.01 intermediates ─────────────────────────────────────────
# ppsig3.FDR01 feeds BLOCK-SPECIFIC TIER and AGGREGATE TIER:
alpha  <- 0.01
alpha2 <- 0.10
B11.alpha <- 0.1  # Block 11 correction: 0.1
B10.alpha <- 0.001 # Block 10 correction: 0.001

ppsig.B10.01 <- Significat_subset(B10.pv, B10.alpha,     alpha2)
ppsig.B11.01 <- Significat_subset(B11.pv, B11.alpha, alpha2)
ppsig.B12.01 <- Significat_subset(B12.pv, alpha,     alpha2)

ppsig.B10.01$BLOCK <- 10
ppsig.B11.01$BLOCK <- 11
ppsig.B12.01$BLOCK <- 12

ppsig3.FDR01 <- rbind(ppsig.B10.01, ppsig.B11.01, ppsig.B12.01)
write.table(ppsig3.FDR01,    "Sig.Loci.FDR01.1",       sep = "\t", row.names = FALSE, quote = FALSE)
write.table(ppsig.B10.01,    "Sig.Loci.FDR01.Block10",  sep = "\t", row.names = FALSE, quote = FALSE)
write.table(ppsig.B11.01,    "Sig.Loci.FDR01.Block11",  sep = "\t", row.names = FALSE, quote = FALSE)
write.table(ppsig.B12.01,    "Sig.Loci.FDR01.Block12",  sep = "\t", row.names = FALSE, quote = FALSE)

# ══════════════════════════════════════════════════════════════════════════════
# BLOCK-SPECIFIC TIER: block-specific alpha thresholds AND top 1% of q-values
# ══════════════════════════════════════════════════════════════════════════════
# top5pct_filter selects the top 1% strongest signals among already-significant
# loci (quantile computed on CON-clean subset; QCON > 0.1).
# Block alphas: B10 = 0.001 (drift correction), B11 = 0.1 (power correction),
# B12 = 0.01 (base). Restricted to singletons via semi_join below.

ppsig.B10 <- Significat_subset(B10.pv, B10.alpha,     alpha2) %>% top5pct_filter()
ppsig.B11 <- Significat_subset(B11.pv, B11.alpha, alpha2) %>% top5pct_filter()
ppsig.B12 <- Significat_subset(B12.pv, alpha,     alpha2) %>% top5pct_filter()

ppsig.B10$BLOCK <- 10
ppsig.B11$BLOCK <- 11
ppsig.B12$BLOCK <- 12

singleton   <- read.table("singleton.loci",         header = TRUE)
sing.lowvar <- read.table("singleton.loci.lowvar",  header = TRUE)
sing.lowcov <- read.table("singleton.loci.lowcov",  header = TRUE)

BS_all       <- rbind(ppsig.B10, ppsig.B11, ppsig.B12)
ppsig1.s        <- semi_join(BS_all, singleton,   by = "SNP")
ppsig1.s.lowvar <- semi_join(BS_all, sing.lowvar, by = "SNP")
ppsig1.s.lowcov <- semi_join(BS_all, sing.lowcov, by = "SNP")

# ══════════════════════════════════════════════════════════════════════════════
# AGGREGATE TIER: per-block q < 0.01 in ≥1 block AND q < 0.0001 in all-blocks (AB)
# ══════════════════════════════════════════════════════════════════════════════
# These loci have modest per-block signal that cross-validates against the
# pooled all-blocks analysis. Detected in aggregate rather than any single
# spawning block — indicating consistent but weak selection below individual-block
# detection power. BLOCK 33 is a dummy identifier for the AB dataset.
ppsig1.ab       <- Significat_subset(AB.pv, 0.0001, alpha2)
ppsig1.ab$BLOCK <- 33

agg.SE <- bind_rows(subset(ppsig3.FDR01, Sig.SE   == TRUE),
                    subset(ppsig1.ab,    Sig.SE   == TRUE)) %>%
          group_by(SNP) %>% filter(n() > 1) %>%
          apply_treatment_filter("Sig.SE")

agg.CASE <- bind_rows(subset(ppsig3.FDR01, Sig.CASE == TRUE),
                      subset(ppsig1.ab,    Sig.CASE == TRUE)) %>%
            group_by(SNP) %>% filter(n() > 1) %>%
            apply_treatment_filter("Sig.CASE")

agg.CA <- bind_rows(subset(ppsig3.FDR01, Sig.CA   == TRUE),
                    subset(ppsig1.ab,    Sig.CA   == TRUE)) %>%
          group_by(SNP) %>% filter(n() > 1) %>%
          apply_treatment_filter("Sig.CA")

aggregate.sig <- bind_rows(agg.SE, agg.CASE, agg.CA)

# ══════════════════════════════════════════════════════════════════════════════
# CON FILTER
# ══════════════════════════════════════════════════════════════════════════════
conpp1   <- subset(pp1,   QCON < 0.01)
conpp.AB <- subset(AB.pv, QCON < 0.001)
all_con  <- bind_rows(conpp1, conpp.AB) %>% group_by(SNP) %>% filter(n() > 1)
all_con  <- subset(all_con, QCON / QCASE < 10 & QCON / QCA < 10 & QCON / QSE < 10)
write.table(all_con, "ALL.CON.SNPS", sep = "\t", row.names = FALSE, quote = FALSE)

# ══════════════════════════════════════════════════════════════════════════════
# FINAL UNION: all three tiers combined, CON-filtered
# ══════════════════════════════════════════════════════════════════════════════
total.sig <- anti_join(
  bind_rows(all_sig, multi_sig, aggregate.sig, ppsig1.s),
  all_con,
  by = "SNP"
)
write.table(total.sig, "Total.Significant.uf.Loci", sep = "\t", row.names = FALSE, quote = FALSE)

# ══════════════════════════════════════════════════════════════════════════════
# THREE-WAY SPLIT of significant loci
# ══════════════════════════════════════════════════════════════════════════════
# Tiers are assigned hierarchically (Core > Aggregate > Block-Specific) so that
# each locus appears in exactly one tier.
#
# Exception: low-variation singletons that appear in the Aggregate candidates
# are reclassified as Block-Specific. For these loci the Aggregate all-blocks
# signal is driven by a single polymorphic spawn — the other two blocks are
# near-fixed (MAF < 0.015), so the AB result is not cross-block validation.
# bs_source records whether a Block-Specific locus originated from the
# Aggregate candidates ("Aggregate") or directly from per-block outlier filtering ("Single").

# Core (Tiers A and B): strong replicated signal across multiple independent
# spawning blocks. Consistent response regardless of block-specific variation
# in effluent composition or larval pool standing genetic variation.
core.sig <- anti_join(
  bind_rows(all_sig, multi_sig),
  all_con,
  by = "SNP"
)
write.table(core.sig, "Sig.Loci.Core", sep = "\t", row.names = FALSE, quote = FALSE)

# Aggregate: Core excluded first; then lowvar singletons split off to Block-Specific.
# Remaining loci cross-validate a per-block signal against the all-blocks analysis
# across spawns with adequate MAF — genuine weak consistent selection.
agg_candidates <- anti_join(aggregate.sig, core.sig, by = "SNP")
agg_to_bs      <- semi_join(agg_candidates, sing.lowvar, by = "SNP") %>%
                  anti_join(all_con, by = "SNP") %>%
                  mutate(bs_source = "Aggregate")
aggregate.sig  <- anti_join(agg_candidates, sing.lowvar, by = "SNP") %>%
                  anti_join(all_con, by = "SNP")
write.table(aggregate.sig, "Sig.Loci.Aggregate", sep = "\t", row.names = FALSE, quote = FALSE)

# Block-Specific: two sources combined, annotated by bs_source.
# "Single"    — top-5% per-block outliers among singleton loci (testable in 1–2 blocks
#               only due to low coverage or near-fixation in absent spawns).
# "Aggregate" — lowvar singletons reclassified from Aggregate: near-fixed in absent
#               blocks, so AB signal was single-spawn-driven rather than cross-validated.
bs_single <- anti_join(
  anti_join(
    anti_join(ppsig1.s, core.sig, by = "SNP"),
    aggregate.sig, by = "SNP"
  ),
  all_con,
  by = "SNP"
) %>% mutate(bs_source = "Single")

block.specific <- bind_rows(bs_single, agg_to_bs)
write.table(block.specific, "Sig.Loci.Block-Specific", sep = "\t", row.names = FALSE, quote = FALSE)
```


#### Old Way
```{r}
Qvalue_convert(B10.pval.table) ->B10.pv
Qvalue_convert(B11.pval.table) ->B11.pv
Qvalue_convert(B12.pval.table) ->B12.pv
```

```{r}
pp1 <- rbind(B10.pv,B11.pv,B12.pv)

alpha = 0.1
B11.alpha = alpha * 1
alpha2 =0.1

ppsig.B10.1 <- Significat_subset(B10.pv,alpha,alpha2)
ppsig.B11.1 <- Significat_subset(B11.pv,B11.alpha,alpha2)
ppsig.B12.1 <- Significat_subset(B12.pv,alpha,alpha2)

ppsig.B10.1$BLOCK <- 10
ppsig.B11.1$BLOCK <- 11
ppsig.B12.1$BLOCK <- 12

ppsig3.FDR10 <- bind_rows(ppsig.B10.1,ppsig.B11.1,ppsig.B12.1)

all_sig.CA<- subset(ppsig3.FDR10, Sig.CA == "TRUE") %>% group_by(SNP) %>% filter(n()>2)
all_sig.CA$Sig.CASE<- FALSE
all_sig.CA$Sig.SE<- FALSE

all_sig.CASE<- subset(ppsig3.FDR10, Sig.CASE == "TRUE") %>% group_by(SNP) %>% filter(n()>2)
all_sig.CASE$Sig.CA<- FALSE
all_sig.CASE$Sig.SE<- FALSE

all_sig.SE<- subset(ppsig3.FDR10, Sig.SE == "TRUE") %>% group_by(SNP) %>% filter(n()>2)
all_sig.SE$Sig.CASE<- FALSE
all_sig.SE$Sig.CA<- FALSE

#all_sig <- ppsig3.FDR10 %>% group_by(SNP) %>% filter(n()>2)
all_sig <- bind_rows(all_sig.CA,all_sig.CASE,all_sig.SE)

write.table(all_sig, "Sig.Loci.3", sep="\t", row.names = FALSE, quote = FALSE)

alpha = 0.05
B11.alpha = alpha * 2
alpha2 =0.1

ppsig.B10.05 <- Significat_subset(B10.pv,alpha,alpha2)
ppsig.B11.05 <- Significat_subset(B11.pv,B11.alpha,alpha2)
ppsig.B12.05 <- Significat_subset(B12.pv,alpha,alpha2)

ppsig.B10.05$BLOCK <- 10
ppsig.B11.05$BLOCK <- 11
ppsig.B12.05$BLOCK <- 12

ppsig3.FDR05 <- rbind(ppsig.B10.05,ppsig.B11.05,ppsig.B12.05)

multi_sig.CA<- subset(ppsig3.FDR05, Sig.CA == "TRUE") %>% group_by(SNP) %>% filter(n()>1)
multi_sig.CA$Sig.CASE <- FALSE
multi_sig.CA$Sig.SE <- FALSE

multi_sig.CASE<- subset(ppsig3.FDR05, Sig.CASE == "TRUE") %>% group_by(SNP) %>% filter(n()>1)
multi_sig.CASE$Sig.CA <- FALSE
multi_sig.CASE$Sig.SE <- FALSE

multi_sig.SE<- subset(ppsig3.FDR05, Sig.SE == "TRUE") %>% group_by(SNP) %>% filter(n()>1)
multi_sig.SE$Sig.CA <- FALSE
multi_sig.SE$Sig.CASE <- FALSE

multi_sig <- rbind(multi_sig.CA,multi_sig.CASE,multi_sig.SE)

#multi_sig.CA<- subset(ppsig3.FDR05, QCA < B11.alpha) %>% group_by(SNP) %>% filter(n()>1)
#multi_sig.CASE<- subset(ppsig3.FDR05, QCASE < B11.alpha) %>% group_by(SNP) %>% filter(n()>1)
#multi_sig.SE<- subset(ppsig3.FDR05, QSE < B11.alpha) %>% group_by(SNP) %>% filter(n()>1)

#multi_sig <- rbind(ppsig3.FDR05 %>% group_by(SNP) %>% filter(n()>1))
#multi_sig <- rbind(multi_sig.CA,multi_sig.CASE,multi_sig.SE)

write.table(multi_sig, "Sig.Loci.2", sep="\t", row.names = FALSE, quote = FALSE)

alpha = 0.01
alpha2 =0.1
B11.alpha = alpha *2

ppsig.B10.01 <- Significat_subset(B10.pv,alpha,alpha2)
ppsig.B11.01 <- Significat_subset(B11.pv,B11.alpha,alpha2)
ppsig.B12.01 <- Significat_subset(B12.pv,alpha,alpha2)

conpp1 <- subset(pp1, QCON < alpha)

ppsig.B10.01$BLOCK <- 10
ppsig.B11.01$BLOCK <- 11
ppsig.B12.01$BLOCK <- 12

ppsig3.FDR01 <- rbind(ppsig.B10.01,ppsig.B11.01,ppsig.B12.01)

write.table(ppsig3.FDR01, "Sig.Loci.FDR01.1", sep="\t", row.names = FALSE, quote = FALSE)
write.table(ppsig.B10.01, "Sig.Loci.FDR01.Block10", sep="\t", row.names = FALSE, quote = FALSE)
write.table(ppsig.B11.01, "Sig.Loci.FDR01.Block11", sep="\t", row.names = FALSE, quote = FALSE)
write.table(ppsig.B12.01, "Sig.Loci.FDR01.Block12", sep="\t", row.names = FALSE, quote = FALSE)

multi_sig.CA.01<- subset(ppsig3.FDR01, Sig.CA == "TRUE") %>% group_by(SNP) %>% filter(n()>1)
multi_sig.CA.01$Sig.CASE <- FALSE
multi_sig.CA.01$Sig.SE <- FALSE

multi_sig.CASE.01<- subset(ppsig3.FDR01, Sig.CASE == "TRUE") %>% group_by(SNP) %>% filter(n()>1)
multi_sig.CASE.01$Sig.CA <- FALSE
multi_sig.CASE.01$Sig.SE <- FALSE

multi_sig.SE.01<- subset(ppsig3.FDR01, Sig.SE == "TRUE") %>% group_by(SNP) %>% filter(n()>1)
multi_sig.SE.01$Sig.CA <- FALSE
multi_sig.SE.01$Sig.CASE <- FALSE

multi_sig.01 <- rbind(multi_sig.CA.01,multi_sig.CASE.01,multi_sig.SE.01)

write.table(multi_sig.01, "Sig.Loci.FDR01.2", sep="\t", row.names = FALSE, quote = FALSE)

alpha = 0.01
alpha2 =0.1
B11.alpha = alpha * 2


ppsig.B10 <- Significat_subset(B10.pv,alpha,alpha2)
ppsig.B10 <- subset(ppsig.B10, Sig.CASE == TRUE & QCASE < quantile(ppsig.B10$QCASE, na.rm = TRUE, probs = 0.01)
                    | Sig.CA == TRUE & QCA < quantile(ppsig.B10$QCA, na.rm = TRUE, probs = 0.01)
                    | Sig.SE == TRUE & QSE < quantile(ppsig.B10$QSE, na.rm = TRUE, probs = 0.01)
                    )
ppsig.B11 <- Significat_subset(B11.pv,B11.alpha,alpha2)
ppsig.B11 <- subset(ppsig.B11, Sig.CASE == TRUE & QCASE < quantile(ppsig.B11$QCASE, na.rm = TRUE, probs = 0.01)
                    | Sig.CA == TRUE & QCA < quantile(ppsig.B11$QCA, na.rm = TRUE, probs = 0.01)
                    | Sig.SE == TRUE & QSE < quantile(ppsig.B11$QSE, na.rm = TRUE, probs = 0.01)
                    )
ppsig.B12 <- Significat_subset(B12.pv,alpha,alpha2)
ppsig.B12 <- subset(ppsig.B12, Sig.CASE == TRUE & QCASE < quantile(ppsig.B12$QCASE, na.rm = TRUE, probs = 0.01)
                    | Sig.CA == TRUE & QCA < quantile(ppsig.B12$QCA, na.rm = TRUE, probs = 0.01)
                    | Sig.SE == TRUE & QSE < quantile(ppsig.B12$QSE, na.rm = TRUE, probs = 0.01)
                    )

ppsig.B10$BLOCK <- 10
ppsig.B11$BLOCK <- 11
ppsig.B12$BLOCK <- 12

singleton <- read.table("singleton.loci",header=TRUE)

ppsig1.s <- semi_join(rbind(ppsig.B10,ppsig.B11,ppsig.B12),singleton, by = "SNP")


```




```{r}
Qvalue_convert(AB.pval.table) -> AB.pv
```
```{r}

alpha = 0.01
alpha2 =0.1

ppsig.AB <- Significat_subset(AB.pv,alpha,alpha2)


all_sig.AB.CA<- subset(ppsig.AB, Sig.CA == "TRUE") 
all_sig.AB.CA$Sig.CASE <- FALSE
all_sig.AB.CA$Sig.SE <- FALSE

all_sig.AB.CASE<- subset(ppsig.AB, Sig.CASE == "TRUE") 
all_sig.AB.CASE$Sig.SE <- FALSE
all_sig.AB.CASE$Sig.CA <- FALSE

all_sig.AB.SE<- subset(ppsig.AB, Sig.SE == "TRUE") 
all_sig.AB.SE$Sig.CASE <- FALSE
all_sig.AB.SE$Sig.CA <- FALSE

all_sig.AB.AT <- rbind(all_sig.AB.CA,all_sig.AB.CASE,all_sig.AB.SE)

write.table(all_sig.AB.AT, "Sig.Loci.FDR01.AB", sep="\t", row.names = FALSE, quote = FALSE)


alphaAB = 0.0001
alpha2 =0.1


ppsig1.ab <-Significat_subset(AB.pv,alphaAB,alpha2)
write.table(ppsig1.ab, "Sig.Loci.FDR0001.AB", sep="\t", row.names = FALSE, quote = FALSE)

conpp.AB <- subset(AB.pv, QCON < 0.001)
all_con <- bind_rows(conpp1,conpp.AB) %>% group_by(SNP) %>% filter(n()>1)
#all_con <- bind_rows(conpp1,conpp.AB) 
all_con <- subset(all_con,QCON / QCASE < 10 & QCON / QCA < 10 & QCON/ QSE < 10)

write.table(all_con, "ALL.CON.SNPS", sep="\t", row.names = FALSE, quote = FALSE)

ppsig.AB$BLOCK <- 33
ppsig1.ab$BLOCK <-33

#multiple.sig.o<- bind_rows(ppsig1 %>% distinct(SNP, .keep_all = TRUE),ppsig1.ab) %>% group_by(SNP) %>% filter(n()>1)

multiple.sig.SE <- bind_rows(subset(ppsig3.FDR01, Sig.SE == TRUE), subset(ppsig1.ab, Sig.SE == TRUE)) %>% group_by(SNP) %>% filter(n()>1)
multiple.sig.SE$Sig.CA <- FALSE
multiple.sig.SE$Sig.CASE <- FALSE

multiple.sig.CASE <- bind_rows(subset(ppsig3.FDR01, Sig.CASE == TRUE), subset(ppsig1.ab, Sig.CASE == TRUE)) %>% group_by(SNP) %>% filter(n()>1)
multiple.sig.CASE$Sig.CA <- FALSE
multiple.sig.CASE$Sig.SE <- FALSE

multiple.sig.CA<- bind_rows(subset(ppsig3.FDR01, Sig.CA == TRUE), subset(ppsig1.ab, Sig.CA == TRUE)) %>% group_by(SNP) %>% filter(n()>1)
multiple.sig.CA$Sig.SE <- FALSE
multiple.sig.CA$Sig.CASE <- FALSE

multiple.sig.o <- bind_rows(multiple.sig.SE, multiple.sig.CASE, multiple.sig.CA)

total.sig <- anti_join(bind_rows(multiple.sig.o,all_sig,multi_sig, multi_sig.01, ppsig1.s),all_con, by = "SNP")

write.table(total.sig, "Total.Significant.uf.Loci", sep="\t", row.names = FALSE, quote = FALSE)
```
### Proximity Control Loci filter
```{bash}
source activate CASE

cut -f2,3 Total.Significant.uf.Loci | tail -n +2 | sort -k1,2 | uniq | mawk '{print $1 "\t" $2-1 "\t" $2}' | bedtools sort -i - > CASE.Total.Significant.uf.loci.bed

bedtools intersect -wb -a  <(mawk '{print $2"\t"$3-1"\t"$3}' ALL.CON.SNPS ) -b ~/CASE/analysis/sorted.ref3.0.gene.bed | grep -oh "gene=LOC.*;g" | sed 's/gene=//g' | sed 's/;g//g' | sort | uniq > CON.LOCI

bedtools intersect -wb -a  <(mawk '{print $2"\t"$3-1"\t"$3}' ALL.CON.SNPS ) -b ~/CASE/analysis/sorted.ref3.0.gene.bed | cut -f4- | bedtools sort | bedtools merge > con.loci.filter.bed

cat <(echo -e "SNP\tCHROM\tBP") <(bedtools intersect -a CASE.Total.Significant.uf.loci.bed -b con.loci.filter.bed | mawk '{print $1"_"$3"\t"$1"\t"$3}') > ToFilter.Con.Loci.txt
```



```{r}
con_filter <- read.table("ToFilter.Con.Loci.txt",header=TRUE)

total.sig <- unique(anti_join(total.sig,con_filter, by = "SNP"))

write.table(total.sig, "Total.Significant.Loci", sep="\t", row.names = FALSE, quote = FALSE)


grouped_total.sig <- group_and_average(total.sig)

write.table(grouped_total.sig, "Total.Significant.Grouped.Loci", sep="\t", row.names = FALSE, quote = FALSE)

totalsig.CA <- subset(total.sig, Sig.CA == TRUE & Sig.SE == FALSE )
totalsig.SE <- subset(total.sig, Sig.CA == FALSE & Sig.SE == TRUE )
totalsig.both <- subset(total.sig, Sig.CA == TRUE & Sig.SE == TRUE )
totalsig.CASE <- subset(total.sig, Sig.CASE == TRUE )

write.table(totalsig.CA, "sig.ca", sep="\t", row.names = FALSE, quote = FALSE)
write.table(totalsig.SE, "sig.se", sep="\t", row.names = FALSE, quote = FALSE)
write.table(totalsig.both, "sig.both", sep="\t", row.names = FALSE, quote = FALSE)
write.table(totalsig.CASE, "sig.case", sep="\t", row.names = FALSE, quote = FALSE)

```

```{bash}
cat <(echo -e "SNP\tGroup") <(mawk '{if (NR > 1) print $1"\tSE"}' sig.se ) <(mawk '{if (NR > 1) print $1"\tCA"}' sig.ca ) <(mawk '{if (NR > 1) print $1"\tBoth"}' sig.both ) > sig.table
```

### Tier-specific CON filtering and treatment splits
```{bash}
source activate CASE

# ─── bedtools CON-filtering for each locus tier ──────────────────────────────
# con.loci.filter.bed (built above from ALL.CON.SNPS x gene model) is
# reference-derived and applies equally to all tiers. core.sig, aggregate.sig,
# and block.specific were already R-level filtered with anti_join(... , all_con);
# this step removes any remaining loci overlapping CON-associated gene regions.

# Core (Tiers A and B: strong replicated signal across multiple blocks)
cut -f2,3 Sig.Loci.Core | tail -n +2 | sort -k1,2 | uniq | \
  mawk '{print $1 "\t" $2-1 "\t" $2}' | bedtools sort -i - > Core.loci.bed
cat <(echo -e "SNP\tCHROM\tBP") \
  <(bedtools intersect -a Core.loci.bed -b con.loci.filter.bed | \
    mawk '{print $1"_"$3"\t"$1"\t"$3}') > ToFilter.Con.Core.Loci.txt

# Aggregate (q<0.01 per-block AND q<0.0001 all-blocks; consistent weak signal)
cut -f2,3 Sig.Loci.Aggregate | tail -n +2 | sort -k1,2 | uniq | \
  mawk '{print $1 "\t" $2-1 "\t" $2}' | bedtools sort -i - > Agg.loci.bed
cat <(echo -e "SNP\tCHROM\tBP") \
  <(bedtools intersect -a Agg.loci.bed -b con.loci.filter.bed | \
    mawk '{print $1"_"$3"\t"$1"\t"$3}') > ToFilter.Con.Agg.Loci.txt

# Block-Specific (top 5% outliers among singletons; filename quoted due to hyphen)
cut -f2,3 "Sig.Loci.Block-Specific" | tail -n +2 | sort -k1,2 | uniq | \
  mawk '{print $1 "\t" $2-1 "\t" $2}' | bedtools sort -i - > BS.loci.bed
cat <(echo -e "SNP\tCHROM\tBP") \
  <(bedtools intersect -a BS.loci.bed -b con.loci.filter.bed | \
    mawk '{print $1"_"$3"\t"$1"\t"$3}') > ToFilter.Con.BS.Loci.txt
```

```{r}
# ─── Secondary CON filter (bedtools-derived) for each tier ───────────────────
# Applies the gene-region-based CON filter (bedtools intersect result) on top
# of the R-level anti_join filter already applied during locus definition.

# Core
con_filter.core <- read.table("ToFilter.Con.Core.Loci.txt", header = TRUE)
core.sig <- unique(anti_join(core.sig, con_filter.core, by = "SNP"))
write.table(core.sig, "Core.Significant.Loci",
            sep = "\t", row.names = FALSE, quote = FALSE)
grouped_core.sig <- group_and_average(core.sig)
write.table(grouped_core.sig, "Core.Significant.Grouped.Loci",
            sep = "\t", row.names = FALSE, quote = FALSE)

# Aggregate
con_filter.agg <- read.table("ToFilter.Con.Agg.Loci.txt", header = TRUE)
aggregate.sig <- unique(anti_join(aggregate.sig, con_filter.agg, by = "SNP"))
write.table(aggregate.sig, "Agg.Significant.Loci",
            sep = "\t", row.names = FALSE, quote = FALSE)
grouped_aggregate.sig <- group_and_average(aggregate.sig)
write.table(grouped_aggregate.sig, "Agg.Significant.Grouped.Loci",
            sep = "\t", row.names = FALSE, quote = FALSE)

# Block-Specific
con_filter.bs <- read.table("ToFilter.Con.BS.Loci.txt", header = TRUE)
block.specific <- unique(anti_join(block.specific, con_filter.bs, by = "SNP"))
write.table(block.specific, "BS.Significant.Loci",
            sep = "\t", row.names = FALSE, quote = FALSE)
grouped_block.specific <- group_and_average(block.specific)
write.table(grouped_block.specific, "BS.Significant.Grouped.Loci",
            sep = "\t", row.names = FALSE, quote = FALSE)

# ─── Per-treatment splits for each tier ──────────────────────────────────────
# Mirrors the total.sig treatment splits above.
# Sig.CA, Sig.SE, Sig.CASE are logical columns; "both" = loci sig in both CA and SE.
# Empty subsets are possible for sparse tiers in some treatment categories.

# Core
coresig.CA   <- subset(core.sig, Sig.CA == TRUE  & Sig.SE == FALSE)
coresig.SE   <- subset(core.sig, Sig.CA == FALSE & Sig.SE == TRUE)
coresig.both <- subset(core.sig, Sig.CA == TRUE  & Sig.SE == TRUE)
coresig.CASE <- subset(core.sig, Sig.CASE == TRUE)
write.table(coresig.CA,   "sig.core.ca",   sep = "\t", row.names = FALSE, quote = FALSE)
write.table(coresig.SE,   "sig.core.se",   sep = "\t", row.names = FALSE, quote = FALSE)
write.table(coresig.both, "sig.core.both", sep = "\t", row.names = FALSE, quote = FALSE)
write.table(coresig.CASE, "sig.core.case", sep = "\t", row.names = FALSE, quote = FALSE)

# Aggregate
aggsig.CA   <- subset(aggregate.sig, Sig.CA == TRUE  & Sig.SE == FALSE)
aggsig.SE   <- subset(aggregate.sig, Sig.CA == FALSE & Sig.SE == TRUE)
aggsig.both <- subset(aggregate.sig, Sig.CA == TRUE  & Sig.SE == TRUE)
aggsig.CASE <- subset(aggregate.sig, Sig.CASE == TRUE)
write.table(aggsig.CA,   "sig.agg.ca",   sep = "\t", row.names = FALSE, quote = FALSE)
write.table(aggsig.SE,   "sig.agg.se",   sep = "\t", row.names = FALSE, quote = FALSE)
write.table(aggsig.both, "sig.agg.both", sep = "\t", row.names = FALSE, quote = FALSE)
write.table(aggsig.CASE, "sig.agg.case", sep = "\t", row.names = FALSE, quote = FALSE)

# Block-Specific
bssig.CA   <- subset(block.specific, Sig.CA == TRUE  & Sig.SE == FALSE)
bssig.SE   <- subset(block.specific, Sig.CA == FALSE & Sig.SE == TRUE)
bssig.both <- subset(block.specific, Sig.CA == TRUE  & Sig.SE == TRUE)
bssig.CASE <- subset(block.specific, Sig.CASE == TRUE)
write.table(bssig.CA,   "sig.bs.ca",   sep = "\t", row.names = FALSE, quote = FALSE)
write.table(bssig.SE,   "sig.bs.se",   sep = "\t", row.names = FALSE, quote = FALSE)
write.table(bssig.both, "sig.bs.both", sep = "\t", row.names = FALSE, quote = FALSE)
write.table(bssig.CASE, "sig.bs.case", sep = "\t", row.names = FALSE, quote = FALSE)
```

```{bash}
# ─── Per-tier sig.table files (mirrors sig.table for total) ──────────────────
for TIER in Core Agg BS; do
  TIER_LC="${TIER,,}"
  cat <(echo -e "SNP\tGroup") \
    <(mawk '{if (NR > 1) print $1"\tSE"}'   sig.${TIER_LC}.se  ) \
    <(mawk '{if (NR > 1) print $1"\tCA"}'   sig.${TIER_LC}.ca  ) \
    <(mawk '{if (NR > 1) print $1"\tBoth"}' sig.${TIER_LC}.both) > sig.${TIER_LC}.table
done
```


```{bash}
source activate CASE

cut -f2,3 Total.Significant.Loci | tail -n +2 | sort -k1,2 | uniq | mawk '{print $1 "\t" $2-1 "\t" $2}' | bedtools sort -i - > CASE.Total.Significant.loci.bed
bedtools slop -b 100 -i CASE.Total.Significant.loci.bed  -g ../reference.fasta.fai  | bedtools merge -i - >  CASE.Total.Significant.loci.intervals.bed


bedtools intersect -wb -a CASE.Total.Significant.loci.bed -b ~/CASE/analysis/sorted.ref3.0.gene.bed | grep -oh "gene=LOC.*;g" | sed 's/gene=//g' | sed 's/;g//g' | sort | uniq > Sig.loci.TOTAL.CASE.LOC

``` 


```{bash}
source activate CASE

mawk '$14 == "TRUE" ' Total.Significant.Loci | sort -k1,2 | mawk '{print $2 "\t" $3-1 "\t" $3}' | uniq  > CA.Significant.loci.bed
bedtools intersect -wb -a CA.Significant.loci.bed -b ~/CASE/analysis/sorted.ref3.0.gene.bed | grep -oh "gene=LOC.*;g" | sed 's/gene=//g' | sed 's/;g//g' | sort | uniq > Sig.loci.1.CA.LOC

mawk '$15 =="TRUE"' Total.Significant.Loci | sort -k1,2  |  mawk '{print $2 "\t" $3-1 "\t" $3}'| uniq  > SE.Significant.loci.bed
bedtools intersect -wb -a SE.Significant.loci.bed -b ~/CASE/analysis/sorted.ref3.0.gene.bed | grep -oh "gene=LOC.*;g" | sed 's/gene=//g' | sed 's/;g//g' | sort | uniq > Sig.loci.1.SE.LOC

mawk '$13 == "TRUE"' Total.Significant.Loci | sort -k1,2 |   mawk '{print $2 "\t" $3-1 "\t" $3}' | uniq  > CASE.Significant.loci.bed
bedtools intersect -wb -a CASE.Significant.loci.bed -b ~/CASE/analysis/sorted.ref3.0.gene.bed | grep -oh "gene=LOC.*;g" | sed 's/gene=//g' | sed 's/;g//g' | sort | uniq > Sig.loci.1.CASE.LOC

mawk '$11 == "TRUE" && $13 == "TRUE"  && $12 == "FALSE"' Total.Significant.Grouped.Loci | mawk '{print $14 "\t" $15-1 "\t" $15}'| uniq  > SE.CASE.Significant.loci.bed

bedtools intersect -wb -a SE.CASE.Significant.loci.bed -b ~/CASE/analysis/sorted.ref3.0.gene.bed | grep -oh "gene=LOC.*;g" | sed 's/gene=//g' | sed 's/;g//g' | sort | uniq > Sig.loci.SE.CASE.LOC

mawk '$11 == "TRUE" && $13 == "TRUE"  && $12 == "TRUE"' Total.Significant.Grouped.Loci | mawk '{print $14 "\t" $15-1 "\t" $15}'| uniq  > SE.CASE.CA.Significant.loci.bed

bedtools intersect -wb -a SE.CASE.CA.Significant.loci.bed -b ~/CASE/analysis/sorted.ref3.0.gene.bed | grep -oh "gene=LOC.*;g" | sed 's/gene=//g' | sed 's/;g//g' | sort | uniq > Sig.loci.SE.CASE.CA.LOC

mawk '$11 == "FALSE" && $13 == "TRUE"  && $12 == "TRUE"' Total.Significant.Grouped.Loci | mawk '{print $14 "\t" $15-1 "\t" $15}'| uniq  > SE.CA.Significant.loci.bed

mawk '$11 == "TRUE" && $13 == "FALSE"  && $12 == "TRUE"' Total.Significant.Grouped.Loci | mawk '{print $14 "\t" $15-1 "\t" $15}'| uniq  > CA.CASE.Significant.loci.bed

mawk '$11 == "FALSE" && $13 == "TRUE"  && $12 == "FALSE"' Total.Significant.Grouped.Loci | mawk '{print $14 "\t" $15-1 "\t" $15}'| uniq  > SE.ONLY.Significant.loci.bed

mawk '$11 == "TRUE" && $13 == "FALSE"  && $12 == "FALSE"' Total.Significant.Grouped.Loci | mawk '{print $14 "\t" $15-1 "\t" $15}'| uniq  > CASE.ONLY.Significant.loci.bed

mawk '$11 == "FALSE" && $13 == "FALSE"  && $12 == "TRUE"' Total.Significant.Grouped.Loci | mawk '{print $14 "\t" $15-1 "\t" $15}'| uniq  > CA.ONLY.Significant.loci.bed

cat CA.ONLY.Significant.loci.bed CA.CASE.Significant.loci.bed| sort|  uniq  > CA.factor.Significant.loci.bed

cat SE.ONLY.Significant.loci.bed SE.CASE.Significant.loci.bed| sort | uniq  > SE.factor.Significant.loci.bed
```

```{bash}
source activate CASE


#B10
mawk '$14 == "TRUE"' Sig.Loci.FDR01.Block10 | sort -k1,2  | mawk '{print $2 "\t" $3-1 "\t" $3}'| uniq  > CA.Significant.B10.loci.bed
bedtools intersect -wb -a CA.Significant.B10.loci.bed -b ~/CASE/analysis/sorted.ref3.0.gene.bed | grep -oh "gene=LOC.*;g" | sed 's/gene=//g' | sed 's/;g//g' | sort | uniq > Sig.loci.B10.CA.LOC

mawk '$15 == "TRUE" ' Sig.Loci.FDR01.Block10 | sort -k1,2  |  mawk '{print $2 "\t" $3-1 "\t" $3}' | uniq  > SE.Significant.B10.loci.bed
bedtools intersect -wb -a SE.Significant.B10.loci.bed -b ~/CASE/analysis/sorted.ref3.0.gene.bed | grep -oh "gene=LOC.*;g" | sed 's/gene=//g' | sed 's/;g//g' | sort | uniq > Sig.loci.B10.SE.LOC

mawk '$13 == "TRUE" ' Sig.Loci.FDR01.Block10 | sort -k1,2 |  mawk '{print $2 "\t" $3-1 "\t" $3}' | uniq  > CASE.Significant.B10.loci.bed
bedtools intersect -wb -a CASE.Significant.B10.loci.bed -b ~/CASE/analysis/sorted.ref3.0.gene.bed | grep -oh "gene=LOC.*;g" | sed 's/gene=//g' | sed 's/;g//g' | sort | uniq > Sig.loci.B10.CASE.LOC

#B11
mawk '$14 == "TRUE"' Sig.Loci.FDR01.Block11 | sort -k1,2  | mawk '{print $2 "\t" $3-1 "\t" $3}'  | uniq > CA.Significant.B11.loci.bed
bedtools intersect -wb -a CA.Significant.B11.loci.bed -b ~/CASE/analysis/sorted.ref3.0.gene.bed | grep -oh "gene=LOC.*;g" | sed 's/gene=//g' | sed 's/;g//g' | sort | uniq > Sig.loci.B11.CA.LOC

mawk '$15 == "TRUE" ' Sig.Loci.FDR01.Block11 | sort -k1,2 |  mawk '{print $2 "\t" $3-1 "\t" $3}' | uniq > SE.Significant.B11.loci.bed
bedtools intersect -wb -a SE.Significant.B11.loci.bed -b ~/CASE/analysis/sorted.ref3.0.gene.bed | grep -oh "gene=LOC.*;g" | sed 's/gene=//g' | sed 's/;g//g' | sort | uniq > Sig.loci.B11.SE.LOC

mawk '$13 == "TRUE" ' Sig.Loci.FDR01.Block11 | sort -k1,2  |  mawk '{print $2 "\t" $3-1 "\t" $3}' | uniq  > CASE.Significant.B11.loci.bed
bedtools intersect -wb -a CASE.Significant.B11.loci.bed -b ~/CASE/analysis/sorted.ref3.0.gene.bed | grep -oh "gene=LOC.*;g" | sed 's/gene=//g' | sed 's/;g//g' | sort | uniq > Sig.loci.B11.CASE.LOC

#B12
mawk '$14 == "TRUE" ' Sig.Loci.FDR01.Block12 | sort -k1,2 | mawk '{print $2 "\t" $3-1 "\t" $3}' | uniq  > CA.Significant.B12.loci.bed
bedtools intersect -wb -a CA.Significant.B12.loci.bed -b ~/CASE/analysis/sorted.ref3.0.gene.bed | grep -oh "gene=LOC.*;g" | sed 's/gene=//g' | sed 's/;g//g' | sort | uniq > Sig.loci.B12.CA.LOC

mawk '$15 == "TRUE" ' Sig.Loci.FDR01.Block12 | sort -k1,2  |  mawk '{print $2 "\t" $3-1 "\t" $3}' | uniq  > SE.Significant.B12.loci.bed
bedtools intersect -wb -a SE.Significant.B12.loci.bed -b ~/CASE/analysis/sorted.ref3.0.gene.bed | grep -oh "gene=LOC.*;g" | sed 's/gene=//g' | sed 's/;g//g' | sort | uniq > Sig.loci.B12.SE.LOC

mawk '$13 == "TRUE" ' Sig.Loci.FDR01.Block12 | sort -k1,2  |  mawk '{print $2 "\t" $3-1 "\t" $3}' | uniq  > CASE.Significant.B12.loci.bed
bedtools intersect -wb -a CASE.Significant.B12.loci.bed -b ~/CASE/analysis/sorted.ref3.0.gene.bed | grep -oh "gene=LOC.*;g" | sed 's/gene=//g' | sed 's/;g//g' | sort | uniq > Sig.loci.B12.CASE.LOC
```

### Tier-specific gene annotation
```{r}
# ─── Column index verification ────────────────────────────────────────────────
# The bash chunks below use fixed column indices. This block verifies those
# indices against the actual file headers before any gene annotation runs.
# stop() halts the pipeline with a diagnostic message on mismatch (e.g., if
# group_and_average column order changes upstream).
#
# Expected schema for *.Significant.Loci (same as Total.Significant.Loci):
#   col 13 = Sig.CASE, col 14 = Sig.CA, col 15 = Sig.SE
# Expected schema for *.Significant.Grouped.Loci (group_and_average output):
#   col 11 = Sig.CASE, col 12 = Sig.CA, col 13 = Sig.SE, col 14 = CHROM, col 15 = BP

verify_col_indices <- function(filepath, expected) {
  hdr <- colnames(read.table(filepath, header = TRUE, nrows = 1, sep = "\t"))
  for (nm in names(expected)) {
    idx <- expected[[nm]]
    actual <- if (length(hdr) >= idx) hdr[idx] else "<missing>"
    if (actual != nm) {
      stop(sprintf(
        "Column index mismatch in '%s': expected col %d = '%s', found '%s'.\nFull header: %s",
        filepath, idx, nm, actual,
        paste(sprintf("[%d]%s", seq_along(hdr), hdr), collapse = " ")
      ))
    }
  }
  invisible(TRUE)
}

loci_expected    <- list(Sig.CASE = 13L, Sig.CA = 14L, Sig.SE = 15L)
grouped_expected <- list(Sig.CASE = 11L, Sig.CA = 12L, Sig.SE = 13L, CHROM = 14L, BP = 15L)

# Baseline check on total files to confirm column schema before checking tiers
verify_col_indices("Total.Significant.Loci",         loci_expected)
verify_col_indices("Total.Significant.Grouped.Loci", grouped_expected)
message("Total: column indices verified")

for (tier in c("Core", "Agg", "BS")) {
  verify_col_indices(paste0(tier, ".Significant.Loci"),         loci_expected)
  verify_col_indices(paste0(tier, ".Significant.Grouped.Loci"), grouped_expected)
  message(tier, ": column indices verified")
}
message("All column index checks passed. Proceeding to gene annotation.")
```

```{bash}
source activate CASE

GENE_BED=~/CASE/analysis/sorted.ref3.0.gene.bed

# ─── Total LOC gene lists per tier ───────────────────────────────────────────

cut -f2,3 Core.Significant.Loci | tail -n +2 | sort -k1,2 | uniq | \
  mawk '{print $1 "\t" $2-1 "\t" $2}' | bedtools sort -i - > Core.Significant.loci.bed
bedtools intersect -wb -a Core.Significant.loci.bed -b $GENE_BED | \
  grep -oh "gene=LOC.*;g" | sed 's/gene=//g' | sed 's/;g//g' | sort | uniq > Sig.loci.Core.TOTAL.LOC

cut -f2,3 BS.Significant.Loci | tail -n +2 | sort -k1,2 | uniq | \
  mawk '{print $1 "\t" $2-1 "\t" $2}' | bedtools sort -i - > BS.Significant.loci.bed
bedtools intersect -wb -a BS.Significant.loci.bed -b $GENE_BED | \
  grep -oh "gene=LOC.*;g" | sed 's/gene=//g' | sed 's/;g//g' | sort | uniq > Sig.loci.BS.TOTAL.LOC

cut -f2,3 Agg.Significant.Loci | tail -n +2 | sort -k1,2 | uniq | \
  mawk '{print $1 "\t" $2-1 "\t" $2}' | bedtools sort -i - > Agg.Significant.loci.bed
bedtools intersect -wb -a Agg.Significant.loci.bed -b $GENE_BED | \
  grep -oh "gene=LOC.*;g" | sed 's/gene=//g' | sed 's/;g//g' | sort | uniq > Sig.loci.Agg.TOTAL.LOC
```

```{bash}
source activate CASE

GENE_BED=~/CASE/analysis/sorted.ref3.0.gene.bed

# ─── Per-treatment LOC lists per tier ────────────────────────────────────────
# Column indices (verified by the R chunk above):
#   *.Significant.Loci:         col 13 = Sig.CASE, col 14 = Sig.CA, col 15 = Sig.SE
#   *.Significant.Grouped.Loci: col 11 = Sig.CASE, col 12 = Sig.CA, col 13 = Sig.SE
#                               col 14 = CHROM, col 15 = BP
# Empty output files are expected for sparse tiers in some treatment categories.

for TIER in Core Agg BS; do
  LOCI="${TIER}.Significant.Loci"

  # CA (col 14)
  mawk '$14 == "TRUE"' $LOCI | sort -k1,2 | mawk '{print $2 "\t" $3-1 "\t" $3}' | uniq \
    > CA.${TIER}.loci.bed
  bedtools intersect -wb -a CA.${TIER}.loci.bed -b $GENE_BED | \
    grep -oh "gene=LOC.*;g" | sed 's/gene=//g' | sed 's/;g//g' | sort | uniq \
    > Sig.loci.${TIER}.CA.LOC

  # SE (col 15)
  mawk '$15 == "TRUE"' $LOCI | sort -k1,2 | mawk '{print $2 "\t" $3-1 "\t" $3}' | uniq \
    > SE.${TIER}.loci.bed
  bedtools intersect -wb -a SE.${TIER}.loci.bed -b $GENE_BED | \
    grep -oh "gene=LOC.*;g" | sed 's/gene=//g' | sed 's/;g//g' | sort | uniq \
    > Sig.loci.${TIER}.SE.LOC

  # CASE (col 13)
  mawk '$13 == "TRUE"' $LOCI | sort -k1,2 | mawk '{print $2 "\t" $3-1 "\t" $3}' | uniq \
    > CASE.${TIER}.loci.bed
  bedtools intersect -wb -a CASE.${TIER}.loci.bed -b $GENE_BED | \
    grep -oh "gene=LOC.*;g" | sed 's/gene=//g' | sed 's/;g//g' | sort | uniq \
    > Sig.loci.${TIER}.CASE.LOC
done
```

```{bash}
source activate CASE

GENE_BED=~/CASE/analysis/sorted.ref3.0.gene.bed

# ─── Pairwise and triple-treatment LOC lists per tier ────────────────────────
# Grouped.Loci column indices: col 11 = Sig.CASE, col 12 = Sig.CA, col 13 = Sig.SE
#                              col 14 = CHROM, col 15 = BP
# Core tier will have the most populated combination sets; Agg and BS
# output may be empty in some categories, which is expected and interpretable.

for TIER in Core Agg BS; do
  GLOCI="${TIER}.Significant.Grouped.Loci"

  # SE+CASE but not CA
  mawk '$11 == "TRUE" && $13 == "TRUE" && $12 == "FALSE"' $GLOCI | \
    mawk '{print $14 "\t" $15-1 "\t" $15}' | uniq > SE.CASE.${TIER}.loci.bed
  bedtools intersect -wb -a SE.CASE.${TIER}.loci.bed -b $GENE_BED | \
    grep -oh "gene=LOC.*;g" | sed 's/gene=//g' | sed 's/;g//g' | sort | uniq \
    > Sig.loci.${TIER}.SE.CASE.LOC

  # SE+CASE+CA
  mawk '$11 == "TRUE" && $13 == "TRUE" && $12 == "TRUE"' $GLOCI | \
    mawk '{print $14 "\t" $15-1 "\t" $15}' | uniq > SE.CASE.CA.${TIER}.loci.bed
  bedtools intersect -wb -a SE.CASE.CA.${TIER}.loci.bed -b $GENE_BED | \
    grep -oh "gene=LOC.*;g" | sed 's/gene=//g' | sed 's/;g//g' | sort | uniq \
    > Sig.loci.${TIER}.SE.CASE.CA.LOC

  # CA factor: CA-only + CA+CASE loci (all loci responding to acidification)
  mawk '$12 == "TRUE" && $11 == "FALSE" && $13 == "FALSE"' $GLOCI | \
    mawk '{print $14 "\t" $15-1 "\t" $15}' | uniq > CA.ONLY.${TIER}.loci.bed
  mawk '$12 == "TRUE" && $11 == "TRUE"  && $13 == "FALSE"' $GLOCI | \
    mawk '{print $14 "\t" $15-1 "\t" $15}' | uniq > CA.CASE.${TIER}.loci.bed
  cat CA.ONLY.${TIER}.loci.bed CA.CASE.${TIER}.loci.bed | sort | uniq > CA.factor.${TIER}.loci.bed
  bedtools intersect -wb -a CA.factor.${TIER}.loci.bed -b $GENE_BED | \
    grep -oh "gene=LOC.*;g" | sed 's/gene=//g' | sed 's/;g//g' | sort | uniq \
    > Sig.loci.${TIER}.CA.factor.LOC

  # SE factor: SE-only + SE+CASE loci (all loci responding to sewage effluent)
  mawk '$13 == "TRUE" && $11 == "FALSE" && $12 == "FALSE"' $GLOCI | \
    mawk '{print $14 "\t" $15-1 "\t" $15}' | uniq > SE.ONLY.${TIER}.loci.bed
  mawk '$13 == "TRUE" && $11 == "TRUE"  && $12 == "FALSE"' $GLOCI | \
    mawk '{print $14 "\t" $15-1 "\t" $15}' | uniq > SE.CASE.ONLY.${TIER}.loci.bed
  cat SE.ONLY.${TIER}.loci.bed SE.CASE.ONLY.${TIER}.loci.bed | sort | uniq > SE.factor.${TIER}.loci.bed
  bedtools intersect -wb -a SE.factor.${TIER}.loci.bed -b $GENE_BED | \
    grep -oh "gene=LOC.*;g" | sed 's/gene=//g' | sed 's/;g//g' | sort | uniq \
    > Sig.loci.${TIER}.SE.factor.LOC
done
```

## GO Analysis
```{r}
source("../gprofiler2W.R")
#library(gprofiler2)
#set_base_url("http://biit.cs.ut.ee/gprofiler_beta")


gostres <- gost(query = list("CASE" = read.table("Sig.loci.1.CASE.LOC",header=FALSE), "SE" = read.table("Sig.loci.1.SE.LOC",header=FALSE), "CA" = read.table("Sig.loci.1.CA.LOC",header=FALSE)), organism = "cvgca002022765v4", multi_query = FALSE,user_threshold = 0.05,domain_scope = "known")

p <-gostplot(gostres, capped = TRUE, interactive = FALSE)

p <- p+ theme_black() + theme(legend.position = "none")

pp <- publish_gostplot(p, width = NA, height = NA, filename = NULL )

png(filename="TestGO.png", type="cairo",units="px", width=4000, height=2500, res=300, bg="transparent")

pp
dev.off()
```

### Tier-specific gprofiler2 GO enrichment

```{r}
# Core loci — multi-block, Tiers A–C locus set
gostres.core <- gost(
  query         = list(
    "CASE" = read.table("Sig.loci.Core.CASE.LOC", header = FALSE),
    "SE"   = read.table("Sig.loci.Core.SE.LOC",   header = FALSE),
    "CA"   = read.table("Sig.loci.Core.CA.LOC",   header = FALSE)
  ),
  organism       = "cvgca002022765v4",
  multi_query    = FALSE,
  user_threshold = 0.05,
  domain_scope   = "known"
)
p.core   <- gostplot(gostres.core, capped = TRUE, interactive = FALSE)
p.core   <- p.core + theme_black() + theme(legend.position = "none")
pp.core  <- publish_gostplot(p.core, width = NA, height = NA, filename = NULL)
png(filename = "TestGO.Core.png", type = "cairo", units = "px",
    width = 4000, height = 2500, res = 300, bg = "transparent")
pp.core
dev.off()

# Block-Specific loci
gostres.bs <- gost(
  query         = list(
    "CASE" = read.table("Sig.loci.BS.CASE.LOC", header = FALSE),
    "SE"   = read.table("Sig.loci.BS.SE.LOC",   header = FALSE),
    "CA"   = read.table("Sig.loci.BS.CA.LOC",   header = FALSE)
  ),
  organism       = "cvgca002022765v4",
  multi_query    = FALSE,
  user_threshold = 0.05,
  domain_scope   = "known"
)
p.bs   <- gostplot(gostres.bs, capped = TRUE, interactive = FALSE)
p.bs   <- p.bs + theme_black() + theme(legend.position = "none")
pp.bs  <- publish_gostplot(p.bs, width = NA, height = NA, filename = NULL)
png(filename = "TestGO.BS.png", type = "cairo", units = "px",
    width = 4000, height = 2500, res = 300, bg = "transparent")
pp.bs
dev.off()

# Aggregate loci — per-block + all-blocks cross-validated locus set
gostres.agg <- gost(
  query         = list(
    "CASE" = read.table("Sig.loci.Agg.CASE.LOC", header = FALSE),
    "SE"   = read.table("Sig.loci.Agg.SE.LOC",   header = FALSE),
    "CA"   = read.table("Sig.loci.Agg.CA.LOC",   header = FALSE)
  ),
  organism       = "cvgca002022765v4",
  multi_query    = FALSE,
  user_threshold = 0.05,
  domain_scope   = "known"
)
p.agg   <- gostplot(gostres.agg, capped = TRUE, interactive = FALSE)
p.agg   <- p.agg + theme_black() + theme(legend.position = "none")
pp.agg  <- publish_gostplot(p.agg, width = NA, height = NA, filename = NULL)
png(filename = "TestGO.Agg.png", type = "cairo", units = "px",
    width = 4000, height = 2500, res = 300, bg = "transparent")
pp.agg
dev.off()
```

## Gene Ontology Enrichment Analysis with topGO

### Download and prepare GO annotation

```{bash, eval=FALSE}
source activate CASE
mkdir -p ./GO
cd ./GO

wget https://ftp.ncbi.nlm.nih.gov/genomes/all/GCF/002/022/765/GCF_002022765.2_C_virginica-3.0/GCF_002022765.2_C_virginica-3.0_gene_ontology.gaf.gz

gunzip GCF_002022765.2_C_virginica-3.0_gene_ontology.gaf.gz

mv GCF_002022765.2_C_virginica-3.0_gene_ontology.gaf gene_ontology.gaf
```

### Create gene-to-GO mapping file

Making a tab file with gene ID and GO IDs. Each gene has one row with all associated GO terms separated by semicolons.

```{bash, eval=FALSE}
cd ./GO

awk 'NR>9 {print $3 "\t" $5}' gene_ontology.gaf | 
sed '1i gene_name\tGeneOntologyIDs' | 
sort | awk '
NR==1 {print; next}
$1!=prev {
if (NR>2) print prev "\t" goids;
prev=$1;
goids=$2;
next
}
{
goids=goids "; " $2
}
END {print prev "\t" goids}
' > gene2go_full.tab
```

### Extract GO terms for candidate genes (by stressor category)

```{bash, eval=TRUE}
cd ./GO

# All outlier loci
grep -F -f ../Sig.loci.TOTAL.CASE.LOC gene2go_full.tab > ALL_cand_genes_GO.tab
awk 'BEGIN {print "gene_name\tGeneOntologyIDs"} {print}' ALL_cand_genes_GO.tab > ALL_cand_genes_GO_head.tab

# CA stressor loci
grep -F -f ../Sig.loci.1.CA.LOC gene2go_full.tab > CA_cand_genes_GO.tab
awk 'BEGIN {print "gene_name\tGeneOntologyIDs"} {print}' CA_cand_genes_GO.tab > CA_cand_genes_GO_head.tab

# SE stressor loci
grep -F -f ../Sig.loci.1.SE.LOC gene2go_full.tab > SE_cand_genes_GO.tab
awk 'BEGIN {print "gene_name\tGeneOntologyIDs"} {print}' SE_cand_genes_GO.tab > SE_cand_genes_GO_head.tab

# CASE (CA+SE combined) stressor loci
grep -F -f ../Sig.loci.1.CASE.LOC gene2go_full.tab > CASE_cand_genes_GO.tab
awk 'BEGIN {print "gene_name\tGeneOntologyIDs"} {print}' CASE_cand_genes_GO.tab > CASE_cand_genes_GO_head.tab
```

### Extract GO terms for tier-specific candidate genes

```{bash, eval=TRUE}
cd ./GO

# --- Core loci (Tiers A–C, multi-block) ---
grep -F -f ../Sig.loci.Core.TOTAL.LOC  gene2go_full.tab > Core_ALL_cand_genes_GO.tab
awk 'BEGIN {print "gene_name\tGeneOntologyIDs"} {print}' Core_ALL_cand_genes_GO.tab  > Core_ALL_cand_genes_GO_head.tab

grep -F -f ../Sig.loci.Core.CA.LOC     gene2go_full.tab > Core_CA_cand_genes_GO.tab
awk 'BEGIN {print "gene_name\tGeneOntologyIDs"} {print}' Core_CA_cand_genes_GO.tab   > Core_CA_cand_genes_GO_head.tab

grep -F -f ../Sig.loci.Core.SE.LOC     gene2go_full.tab > Core_SE_cand_genes_GO.tab
awk 'BEGIN {print "gene_name\tGeneOntologyIDs"} {print}' Core_SE_cand_genes_GO.tab   > Core_SE_cand_genes_GO_head.tab

grep -F -f ../Sig.loci.Core.CASE.LOC   gene2go_full.tab > Core_CASE_cand_genes_GO.tab
awk 'BEGIN {print "gene_name\tGeneOntologyIDs"} {print}' Core_CASE_cand_genes_GO.tab > Core_CASE_cand_genes_GO_head.tab

# --- Block-Specific loci ---
grep -F -f ../Sig.loci.BS.TOTAL.LOC    gene2go_full.tab > BS_ALL_cand_genes_GO.tab
awk 'BEGIN {print "gene_name\tGeneOntologyIDs"} {print}' BS_ALL_cand_genes_GO.tab    > BS_ALL_cand_genes_GO_head.tab

grep -F -f ../Sig.loci.BS.CA.LOC       gene2go_full.tab > BS_CA_cand_genes_GO.tab
awk 'BEGIN {print "gene_name\tGeneOntologyIDs"} {print}' BS_CA_cand_genes_GO.tab     > BS_CA_cand_genes_GO_head.tab

grep -F -f ../Sig.loci.BS.SE.LOC       gene2go_full.tab > BS_SE_cand_genes_GO.tab
awk 'BEGIN {print "gene_name\tGeneOntologyIDs"} {print}' BS_SE_cand_genes_GO.tab     > BS_SE_cand_genes_GO_head.tab

grep -F -f ../Sig.loci.BS.CASE.LOC     gene2go_full.tab > BS_CASE_cand_genes_GO.tab
awk 'BEGIN {print "gene_name\tGeneOntologyIDs"} {print}' BS_CASE_cand_genes_GO.tab   > BS_CASE_cand_genes_GO_head.tab

# --- Aggregate loci (per-block + all-blocks cross-validated) ---
# Note: these files may be empty if aggregate loci map to no annotated genes;
# downstream R code handles empty input gracefully via run_topGO_analysis().
grep -F -f ../Sig.loci.Agg.TOTAL.LOC  gene2go_full.tab > Agg_ALL_cand_genes_GO.tab
awk 'BEGIN {print "gene_name\tGeneOntologyIDs"} {print}' Agg_ALL_cand_genes_GO.tab  > Agg_ALL_cand_genes_GO_head.tab

grep -F -f ../Sig.loci.Agg.CA.LOC     gene2go_full.tab > Agg_CA_cand_genes_GO.tab
awk 'BEGIN {print "gene_name\tGeneOntologyIDs"} {print}' Agg_CA_cand_genes_GO.tab   > Agg_CA_cand_genes_GO_head.tab

grep -F -f ../Sig.loci.Agg.SE.LOC     gene2go_full.tab > Agg_SE_cand_genes_GO.tab
awk 'BEGIN {print "gene_name\tGeneOntologyIDs"} {print}' Agg_SE_cand_genes_GO.tab   > Agg_SE_cand_genes_GO_head.tab

grep -F -f ../Sig.loci.Agg.CASE.LOC   gene2go_full.tab > Agg_CASE_cand_genes_GO.tab
awk 'BEGIN {print "gene_name\tGeneOntologyIDs"} {print}' Agg_CASE_cand_genes_GO.tab > Agg_CASE_cand_genes_GO_head.tab
```

### Load libraries and gene-to-GO data

```{r}
library(topGO)
library(tidyr)

all_gene2go <- read.delim("GO/gene2go_full.tab", sep="\t")
gene2go_topgo <- readMappings("GO/gene2go_full.tab", IDsep=";", sep="\t")
all_genes <- as.character(unique(all_gene2go$gene_name))

topDiffGenes <- function(allScore) {
  return(allScore < 0.05)
}
```

### Define GO enrichment function

This function runs topGO for all three ontologies (BP, CC, MF), extracts significant GO terms, maps them back to candidate genes, and returns the combined results.

```{r}
run_topGO_analysis <- function(cand_gene_file, all_genes, gene2go_topgo, label) {
  
  # Load candidate gene-to-GO mapping
  cand_gene2go <- read.delim(cand_gene_file, sep="\t")
  cand_genes <- as.character(unique(cand_gene2go$gene_name))
  
  cat(paste0("\n--- ", label, " ---\n"))
  cat(paste0("Number of candidate genes with GO annotations: ", length(cand_genes), "\n"))
  
  # Create gene list
  GeneList <- factor(as.integer(all_genes %in% cand_genes))
  names(GeneList) <- all_genes
  
  # Separate GO terms for gene-level mapping later
  cand_gene2go_sep <- cand_gene2go %>%
    separate_rows(GeneOntologyIDs, sep = ";")
  cand_gene2go_sep$GeneOntologyIDs <- trimws(cand_gene2go_sep$GeneOntologyIDs)
  
  results_list <- list()
  
  # --- Biological Processes ---
  GO_BP <- new("topGOdata", ontology="BP", gene2GO=gene2go_topgo, 
               allGenes=GeneList, annot = annFUN.gene2GO, geneSel=topDiffGenes)
  GO_BP_FE <- runTest(GO_BP, algorithm="weight01", statistic="fisher")
  GO_BP_table <- GenTable(GO_BP, Fisher = GO_BP_FE, orderBy = "Fisher", topNodes = 100, numChar = 100)
  GO_BP_table$Fisher <- as.numeric(GO_BP_table$Fisher)
  GO_BP_sig <- GO_BP_table[GO_BP_table$Fisher < 0.05,]
  
  if(nrow(GO_BP_sig) > 0) {
    GO_BP_sig$GO.ID <- trimws(GO_BP_sig$GO.ID)
    GO_BP_sig_gene <- cand_gene2go_sep %>%
      left_join(GO_BP_sig, by = c("GeneOntologyIDs" = "GO.ID")) %>%
      na.omit()
    GO_BP_sig_gene$ontology <- "Biological Processes"
    results_list[["BP"]] <- GO_BP_sig_gene
  }
  
  # --- Cellular Components ---
  GO_CC <- new("topGOdata", ontology="CC", gene2GO=gene2go_topgo, 
               allGenes=GeneList, annot = annFUN.gene2GO, geneSel=topDiffGenes)
  GO_CC_FE <- runTest(GO_CC, algorithm="weight01", statistic="fisher")
  GO_CC_table <- GenTable(GO_CC, Fisher = GO_CC_FE, orderBy = "Fisher", topNodes = 100, numChar = 100)
  GO_CC_table$Fisher <- as.numeric(GO_CC_table$Fisher)
  GO_CC_sig <- GO_CC_table[GO_CC_table$Fisher < 0.05,]
  
  if(nrow(GO_CC_sig) > 0) {
    GO_CC_sig$GO.ID <- trimws(GO_CC_sig$GO.ID)
    GO_CC_sig_gene <- cand_gene2go_sep %>%
      left_join(GO_CC_sig, by = c("GeneOntologyIDs" = "GO.ID")) %>%
      na.omit()
    GO_CC_sig_gene$ontology <- "Cellular Components"
    results_list[["CC"]] <- GO_CC_sig_gene
  }
  
  # --- Molecular Functions ---
  GO_MF <- new("topGOdata", ontology="MF", gene2GO=gene2go_topgo, 
               allGenes=GeneList, annot = annFUN.gene2GO, geneSel=topDiffGenes)
  GO_MF_FE <- runTest(GO_MF, algorithm="weight01", statistic="fisher")
  GO_MF_table <- GenTable(GO_MF, Fisher = GO_MF_FE, orderBy = "Fisher", topNodes = 100, numChar = 100)
  GO_MF_table$Fisher <- as.numeric(GO_MF_table$Fisher)
  GO_MF_sig <- GO_MF_table[GO_MF_table$Fisher < 0.05,]
  
  if(nrow(GO_MF_sig) > 0) {
    GO_MF_sig$GO.ID <- trimws(GO_MF_sig$GO.ID)
    GO_MF_sig_gene <- cand_gene2go_sep %>%
      left_join(GO_MF_sig, by = c("GeneOntologyIDs" = "GO.ID")) %>%
      na.omit()
    GO_MF_sig_gene$ontology <- "Molecular Functions"
    results_list[["MF"]] <- GO_MF_sig_gene
  }
  
  # Combine all ontologies
  if(length(results_list) > 0) {
    combined <- do.call(rbind, results_list)
    combined <- combined %>% mutate(prop.sig.genes = Significant/Annotated)
    combined <- unique(combined)
    combined$stressor <- label
    return(combined)
  } else {
    cat(paste0("No significant GO terms found for ", label, "\n"))
    return(NULL)
  }
}
```

### Run GO enrichment for all four categories

```{r}
# All outlier loci
GO_ALL <- run_topGO_analysis("GO/ALL_cand_genes_GO_head.tab", all_genes, gene2go_topgo, "All Outliers")

# CA stressor
GO_CA <- run_topGO_analysis("GO/CA_cand_genes_GO_head.tab", all_genes, gene2go_topgo, "CA")

# SE stressor
GO_SE <- run_topGO_analysis("GO/SE_cand_genes_GO_head.tab", all_genes, gene2go_topgo, "SE")

# CASE (CA+SE combined) stressor
GO_CASE <- run_topGO_analysis("GO/CASE_cand_genes_GO_head.tab", all_genes, gene2go_topgo, "CASE")
```

### Run GO enrichment for Core loci

```{r}
# Core loci: multi-block, Tiers A–C; highest-confidence locus set
GO_Core_ALL  <- run_topGO_analysis("GO/Core_ALL_cand_genes_GO_head.tab",  all_genes, gene2go_topgo, "Core: All Outliers")
GO_Core_CA   <- run_topGO_analysis("GO/Core_CA_cand_genes_GO_head.tab",   all_genes, gene2go_topgo, "Core: CA")
GO_Core_SE   <- run_topGO_analysis("GO/Core_SE_cand_genes_GO_head.tab",   all_genes, gene2go_topgo, "Core: SE")
GO_Core_CASE <- run_topGO_analysis("GO/Core_CASE_cand_genes_GO_head.tab", all_genes, gene2go_topgo, "Core: CASE")
```

### Run GO enrichment for Block-Specific loci

```{r}
# Block-Specific loci: per-block outlier singletons and reclassified Aggregate loci
GO_BS_ALL  <- run_topGO_analysis("GO/BS_ALL_cand_genes_GO_head.tab",  all_genes, gene2go_topgo, "Block-Specific: All Outliers")
GO_BS_CA   <- run_topGO_analysis("GO/BS_CA_cand_genes_GO_head.tab",   all_genes, gene2go_topgo, "Block-Specific: CA")
GO_BS_SE   <- run_topGO_analysis("GO/BS_SE_cand_genes_GO_head.tab",   all_genes, gene2go_topgo, "Block-Specific: SE")
GO_BS_CASE <- run_topGO_analysis("GO/BS_CASE_cand_genes_GO_head.tab", all_genes, gene2go_topgo, "Block-Specific: CASE")
```

### Run GO enrichment for Aggregate loci

```{r}
# Aggregate loci: per-block + all-blocks cross-validated; may return NULL if too few annotated genes
GO_Agg_ALL  <- run_topGO_analysis("GO/Agg_ALL_cand_genes_GO_head.tab",  all_genes, gene2go_topgo, "Aggregate: All Outliers")
GO_Agg_CA   <- run_topGO_analysis("GO/Agg_CA_cand_genes_GO_head.tab",   all_genes, gene2go_topgo, "Aggregate: CA")
GO_Agg_SE   <- run_topGO_analysis("GO/Agg_SE_cand_genes_GO_head.tab",   all_genes, gene2go_topgo, "Aggregate: SE")
GO_Agg_CASE <- run_topGO_analysis("GO/Agg_CASE_cand_genes_GO_head.tab", all_genes, gene2go_topgo, "Aggregate: CASE")
```

### Save results

```{r}
if(!is.null(GO_ALL))  write.csv(GO_ALL,  "GO/ALL_GO_en_sig_gene.csv", row.names = FALSE)
if(!is.null(GO_CA))   write.csv(GO_CA,   "GO/CA_GO_en_sig_gene.csv", row.names = FALSE)
if(!is.null(GO_SE))   write.csv(GO_SE,   "GO/SE_GO_en_sig_gene.csv", row.names = FALSE)
if(!is.null(GO_CASE)) write.csv(GO_CASE, "GO/CASE_GO_en_sig_gene.csv", row.names = FALSE)
```

### Save tier-specific topGO results

```{r}
# Core
if(!is.null(GO_Core_ALL))  write.csv(GO_Core_ALL,  "GO/Core_ALL_GO_en_sig_gene.csv",  row.names = FALSE)
if(!is.null(GO_Core_CA))   write.csv(GO_Core_CA,   "GO/Core_CA_GO_en_sig_gene.csv",   row.names = FALSE)
if(!is.null(GO_Core_SE))   write.csv(GO_Core_SE,   "GO/Core_SE_GO_en_sig_gene.csv",   row.names = FALSE)
if(!is.null(GO_Core_CASE)) write.csv(GO_Core_CASE, "GO/Core_CASE_GO_en_sig_gene.csv", row.names = FALSE)

# Block-Specific
if(!is.null(GO_BS_ALL))  write.csv(GO_BS_ALL,  "GO/BS_ALL_GO_en_sig_gene.csv",  row.names = FALSE)
if(!is.null(GO_BS_CA))   write.csv(GO_BS_CA,   "GO/BS_CA_GO_en_sig_gene.csv",   row.names = FALSE)
if(!is.null(GO_BS_SE))   write.csv(GO_BS_SE,   "GO/BS_SE_GO_en_sig_gene.csv",   row.names = FALSE)
if(!is.null(GO_BS_CASE)) write.csv(GO_BS_CASE, "GO/BS_CASE_GO_en_sig_gene.csv", row.names = FALSE)

# Aggregate
if(!is.null(GO_Agg_ALL))  write.csv(GO_Agg_ALL,  "GO/Agg_ALL_GO_en_sig_gene.csv",  row.names = FALSE)
if(!is.null(GO_Agg_CA))   write.csv(GO_Agg_CA,   "GO/Agg_CA_GO_en_sig_gene.csv",   row.names = FALSE)
if(!is.null(GO_Agg_SE))   write.csv(GO_Agg_SE,   "GO/Agg_SE_GO_en_sig_gene.csv",   row.names = FALSE)
if(!is.null(GO_Agg_CASE)) write.csv(GO_Agg_CASE, "GO/Agg_CASE_GO_en_sig_gene.csv", row.names = FALSE)
```

### Plot GO enrichment for each stressor category

```{r, fig.width=10, fig.height=14}
plot_GO <- function(go_data, title_label) {
  if(is.null(go_data) || nrow(go_data) == 0) {
    cat(paste0("No significant GO terms to plot for ", title_label, "\n"))
    return(NULL)
  }
  
  p <- ggplot(go_data, aes(x = Term, y = -log(Fisher), size = prop.sig.genes, fill = -log(Fisher))) +
    expand_limits(y = 1.5) +
    geom_hline(yintercept = -log10(0.01), linetype = "longdash", colour = "black", linewidth = .6) +
    geom_hline(yintercept = -log10(0.001), linetype = "solid", colour = "black", linewidth = .6) +
    geom_point(shape = 21) + 
    scale_size(range = c(2, 12)) + 
    scale_fill_continuous(low = "#1AD3D1FF", high = "#4686FBFF") +
    xlab('') + 
    ylab('Enrichment score') +
    ggtitle(title_label) +
    theme_bw() +
    facet_grid(vars(ontology), scales = "free", space = "free_y") +
    coord_flip()
  
  return(p)
}

# Plot each category
GO_ALL_plot  <- plot_GO(GO_ALL, "All Outlier Loci")
GO_CA_plot   <- plot_GO(GO_CA, "CA Stressor")
GO_SE_plot   <- plot_GO(GO_SE, "SE Stressor")
GO_CASE_plot <- plot_GO(GO_CASE, "CASE Stressor (CA+SE)")

# Print plots
if(!is.null(GO_ALL_plot))  print(GO_ALL_plot)
if(!is.null(GO_CA_plot))   print(GO_CA_plot)
if(!is.null(GO_SE_plot))   print(GO_SE_plot)
if(!is.null(GO_CASE_plot)) print(GO_CASE_plot)
```

### Save GO enrichment plots

```{r}
save_GO_plot <- function(plot, filename, height = 4000) {
  if(!is.null(plot)) {
    png(filename = filename,
        type = "cairo",
        width = 2000,
        height = height,
        res = 200,
        bg = "transparent")
    print(plot)
    dev.off()
  }
}

save_GO_plot(GO_ALL_plot,  "GO/GO_enrichment_ALL.png")
save_GO_plot(GO_CA_plot,   "GO/GO_enrichment_CA.png")
save_GO_plot(GO_SE_plot,   "GO/GO_enrichment_SE.png")
save_GO_plot(GO_CASE_plot, "GO/GO_enrichment_CASE.png")
```

### Plot and save tier-specific GO enrichment

```{r, fig.width=10, fig.height=14}
# --- Core loci ---
GO_Core_ALL_plot  <- plot_GO(GO_Core_ALL,  "Core: All Outlier Loci")
GO_Core_CA_plot   <- plot_GO(GO_Core_CA,   "Core: CA Stressor")
GO_Core_SE_plot   <- plot_GO(GO_Core_SE,   "Core: SE Stressor")
GO_Core_CASE_plot <- plot_GO(GO_Core_CASE, "Core: CASE Stressor (CA+SE)")

if(!is.null(GO_Core_ALL_plot))  print(GO_Core_ALL_plot)
if(!is.null(GO_Core_CA_plot))   print(GO_Core_CA_plot)
if(!is.null(GO_Core_SE_plot))   print(GO_Core_SE_plot)
if(!is.null(GO_Core_CASE_plot)) print(GO_Core_CASE_plot)

save_GO_plot(GO_Core_ALL_plot,  "GO/GO_enrichment_Core_ALL.png")
save_GO_plot(GO_Core_CA_plot,   "GO/GO_enrichment_Core_CA.png")
save_GO_plot(GO_Core_SE_plot,   "GO/GO_enrichment_Core_SE.png")
save_GO_plot(GO_Core_CASE_plot, "GO/GO_enrichment_Core_CASE.png")

# --- Block-Specific loci ---
GO_BS_ALL_plot  <- plot_GO(GO_BS_ALL,  "Block-Specific: All Outlier Loci")
GO_BS_CA_plot   <- plot_GO(GO_BS_CA,   "Block-Specific: CA Stressor")
GO_BS_SE_plot   <- plot_GO(GO_BS_SE,   "Block-Specific: SE Stressor")
GO_BS_CASE_plot <- plot_GO(GO_BS_CASE, "Block-Specific: CASE Stressor (CA+SE)")

if(!is.null(GO_BS_ALL_plot))  print(GO_BS_ALL_plot)
if(!is.null(GO_BS_CA_plot))   print(GO_BS_CA_plot)
if(!is.null(GO_BS_SE_plot))   print(GO_BS_SE_plot)
if(!is.null(GO_BS_CASE_plot)) print(GO_BS_CASE_plot)

save_GO_plot(GO_BS_ALL_plot,  "GO/GO_enrichment_BS_ALL.png")
save_GO_plot(GO_BS_CA_plot,   "GO/GO_enrichment_BS_CA.png")
save_GO_plot(GO_BS_SE_plot,   "GO/GO_enrichment_BS_SE.png")
save_GO_plot(GO_BS_CASE_plot, "GO/GO_enrichment_BS_CASE.png")

# --- Aggregate loci ---
GO_Agg_ALL_plot  <- plot_GO(GO_Agg_ALL,  "Aggregate: All Outlier Loci")
GO_Agg_CA_plot   <- plot_GO(GO_Agg_CA,   "Aggregate: CA Stressor")
GO_Agg_SE_plot   <- plot_GO(GO_Agg_SE,   "Aggregate: SE Stressor")
GO_Agg_CASE_plot <- plot_GO(GO_Agg_CASE, "Aggregate: CASE Stressor (CA+SE)")

if(!is.null(GO_Agg_ALL_plot))  print(GO_Agg_ALL_plot)
if(!is.null(GO_Agg_CA_plot))   print(GO_Agg_CA_plot)
if(!is.null(GO_Agg_SE_plot))   print(GO_Agg_SE_plot)
if(!is.null(GO_Agg_CASE_plot)) print(GO_Agg_CASE_plot)

save_GO_plot(GO_Agg_ALL_plot,  "GO/GO_enrichment_Agg_ALL.png")
save_GO_plot(GO_Agg_CA_plot,   "GO/GO_enrichment_Agg_CA.png")
save_GO_plot(GO_Agg_SE_plot,   "GO/GO_enrichment_Agg_SE.png")
save_GO_plot(GO_Agg_CASE_plot, "GO/GO_enrichment_Agg_CASE.png")
```

### Combined GO enrichment plot (all stressors)

```{r, fig.width=16, fig.height=14}
# Combine all results into a single data frame for a faceted comparison
GO_combined <- bind_rows(GO_ALL, GO_CA, GO_SE, GO_CASE)

if(nrow(GO_combined) > 0) {
  GO_combined$stressor <- factor(GO_combined$stressor, levels = c("All Outliers", "CA", "SE", "CASE"))
  
  GO_combined_plot <- ggplot(GO_combined, aes(x = Term, y = -log(Fisher), size = prop.sig.genes, fill = -log(Fisher))) +
    expand_limits(y = 1.5) +
    geom_hline(yintercept = -log10(0.01), linetype = "longdash", colour = "black", linewidth = .6) +
    geom_hline(yintercept = -log10(0.001), linetype = "solid", colour = "black", linewidth = .6) +
    geom_point(shape = 21) + 
    scale_size(range = c(2, 10)) + 
    scale_fill_continuous(low = "#1AD3D1FF", high = "#4686FBFF") +
    xlab('') + 
    ylab('Enrichment score') +
    ggtitle("GO Enrichment by Stressor") +
    theme_bw() +
    facet_grid(ontology ~ stressor, scales = "free_y", space = "free_y") +
    coord_flip()
  
  print(GO_combined_plot)
  
  png(filename = "GO/GO_enrichment_combined_stressors.png",
      type = "cairo",
      width = 3500,
      height = 3000,
      res = 200,
      bg = "transparent")
  print(GO_combined_plot)
  dev.off()
}
```




# Manhattan Plots

## Tier highlight helpers

```{r}
# lighten_color(): blend a hex color with white.
# factor = 0 returns the original; factor = 1 returns white.
lighten_color <- function(col, factor = 0.5) {
  v <- col2rgb(col) / 255
  rgb(v[1] + (1 - v[1]) * factor,
      v[2] + (1 - v[2]) * factor,
      v[3] + (1 - v[3]) * factor)
}

# make_tier_palette(): given a base treatment color, return a named fill vector
# for scale_fill_manual(). Core = full color, Aggregate and Block-Specific are
# progressively lighter tints of the same hue.
make_tier_palette <- function(base_color) {
  c(
    "Core"           = base_color,
    "Aggregate"      = lighten_color(base_color, 0.45),
    "Block-Specific" = lighten_color(base_color, 0.72)
  )
}

# Shape mapping for Locus Tier (fillable shapes only; square reserved for Control Treatment Group)
tier_shape <- c("Core" = 21, "Aggregate" = 23, "Block-Specific" = 25)

# build_tier_highlights(): given the ggman data frame (dfm) for one block and
# one treatment column, returns a data frame with a Tier factor column.
# Pass the result to geom_point(fill = Tier) + scale_fill_manual(make_tier_palette(...)).
#
# Arguments:
#   dfm             — ggman plot data frame (output of ggman()[[1]])
#   block_num       — integer block ID (10, 11, or 12)
#   treatment_col   — string name of the significance column (e.g. "Sig.CASE")
#   highlight_color — base treatment color (e.g. "#009E73" for CASE, "#0072B2"
#                     for SE, "#E69F00" for CA) — passed to make_tier_palette()
#                     for scale_fill_manual() in the calling plot code
build_tier_highlights <- function(dfm, block_num, treatment_col, highlight_color = NULL) {
  h.core <- core.sig       %>% filter(BLOCK == block_num, .data[[treatment_col]] == TRUE)
  h.agg  <- aggregate.sig  %>% filter(BLOCK == block_num, .data[[treatment_col]] == TRUE)
  # Block-Specific: no BLOCK filter — highlight any known singleton outlier visible in
  # this plot regardless of which block it was identified in. block.specific already
  # carries correct BLOCK provenance; we're not conflating blocks, just displaying known
  # outliers wherever they appear significant.
  h.bs   <- block.specific %>% filter(.data[[treatment_col]] == TRUE)

  bind_rows(
    semi_join(dfm, h.core, by = "SNP") %>% mutate(Tier = "Core"),
    semi_join(dfm, h.agg,  by = "SNP") %>% mutate(Tier = "Aggregate"),
    semi_join(dfm, h.bs,   by = "SNP") %>% mutate(Tier = "Block-Specific")
  ) %>%
    mutate(Tier = factor(Tier, levels = c("Core", "Aggregate", "Block-Specific")))
}
```

#### CASE
```{r, warning =FALSE, eval = TRUE}
# Treatment color and tier tint palette for CASE Manhattan plots
tier_fill <- make_tier_palette("#009E73")

b10.h <- subset(total.sig,  BLOCK == "10" & Sig.CASE == TRUE)
b10.c <- subset(B10.pv, QCON < 0.1)


B10.pp <- B10.pv %>%
  mutate(
    Group = case_when(
      SNP %in% b10.c$SNP ~ "Control Treatment Filtered",
      SNP %in% all_con$SNP ~ "Control Treatment Filtered",
      SNP %in% con_filter$SNP ~ "Control Treatment Filtered",
      SNP %in% singleton$SNP ~ "Single-Block",
      TRUE ~ "Shared SNP"
    )
  )

man <-ggman(B10.pp, pvalue="QCASE", chr="CHR", snp="SNP",bp="BP", relative.positions = TRUE ,sigLine = NA, pointSize=1.5,title = "", alpha = 0.5)

dfm <- man[[1]]

dfm$chrom_alt <- factor(dfm$chrom_alt, levels=c(0,1))

# Highlight each block using tier-colored points (Core/Aggregate/Block-Specific)
dfmo <- build_tier_highlights(dfm, block_num = 10, treatment_col = "Sig.CASE")

dfmsplit <- split(dfm, dfm$chrom)
xbreaks <- sapply(dfmsplit,function(x) {
    midpoint <- length(x$index)/2
    if(midpoint <1) midpoint <- 1
    return(x$index[midpoint])
})
b10.CASE <-ggplot(dfm, aes(x= index, y=marker, colour = as.factor(chrom_alt)))+
  geom_point(aes(alpha=marker, shape=Group, size = marker))+
  geom_point(data=subset(dfmo, Tier=="Core"),           aes(x=index, y=marker, fill=Tier), shape=21, size=3, color="black", alpha=0.9)+
  geom_point(data=subset(dfmo, Tier=="Aggregate"),      aes(x=index, y=marker, fill=Tier), shape=23, size=3, color="black", alpha=0.9)+
  geom_point(data=subset(dfmo, Tier=="Block-Specific"), aes(x=index, y=marker, fill=Tier), shape=25, size=3, color="black", alpha=0.9)+
  scale_fill_manual(values=tier_fill, name="Locus Tier") +
  scale_x_continuous(breaks = xbreaks, labels = names(xbreaks),expand = c(0,0),limits = c(0,max(dfm$index)+10)) +
  guides(colour="none", alpha="none", size="none",
         fill=guide_legend(override.aes=list(shape=c(21,23,25)))) +
  scale_y_continuous(expand = c(0,0),limits=c(0,max(dfm$marker+1,na.rm=TRUE)))+
  scale_size_continuous(range = c(0.25,3)) +
  scale_alpha_continuous(range=c(0.05,0.8), limits= c(0,50))+
  ggtitle("Block 10") +
  labs(x = "Chromosome") +
  theme_classic()+
  labs(y=expression(-Log10(q-value))) +
  scale_shape_manual(values=c(15,21,16))+
  scale_color_manual(values=c("grey", "dark grey"), guide="none")+
  guides(shape = guide_legend(override.aes = list(color = "grey", size = 5, linetype =0) ) )

b11.h <- subset(total.sig,  BLOCK == "11" & Sig.CASE == TRUE)
b11.c <- subset(B11.pv, QCON < 0.1)

B11.pp <- B11.pv %>%
  mutate(
    Group = case_when(
      SNP %in% b11.c$SNP ~ "Control Treatment Filtered",
      SNP %in% all_con$SNP ~ "Control Treatment Filtered",
      SNP %in% con_filter$SNP ~ "Control Treatment Filtered",
      SNP %in% singleton$SNP ~ "Single-Block",
      TRUE ~ "Shared SNP"
    )
  )

man <-ggman(B11.pp, pvalue="QCASE", chr="CHR", snp="SNP",bp="BP", relative.positions = TRUE ,sigLine = NA, pointSize=1.5,title = "", alpha = 0.5)

dfm <- man[[1]]

dfm$chrom_alt <- factor(dfm$chrom_alt, levels=c(0,1))


dfmo <- build_tier_highlights(dfm, block_num = 11, treatment_col = "Sig.CASE")

dfmsplit <- split(dfm, dfm$chrom)
xbreaks <- sapply(dfmsplit,function(x) {
    midpoint <- length(x$index)/2
    if(midpoint <1) midpoint <- 1
    return(x$index[midpoint])
})

b11.CASE <-ggplot(dfm, aes(x= index, y=marker, colour = as.factor(chrom_alt)))+
  geom_point(aes(alpha=marker, shape=Group, size = marker))+
  geom_point(data=subset(dfmo, Tier=="Core"),           aes(x=index, y=marker, fill=Tier), shape=21, size=3, color="black", alpha=0.9)+
  geom_point(data=subset(dfmo, Tier=="Aggregate"),      aes(x=index, y=marker, fill=Tier), shape=23, size=3, color="black", alpha=0.9)+
  geom_point(data=subset(dfmo, Tier=="Block-Specific"), aes(x=index, y=marker, fill=Tier), shape=25, size=3, color="black", alpha=0.9)+
  scale_fill_manual(values=tier_fill, name="Locus Tier") +
  scale_x_continuous(breaks = xbreaks, labels = names(xbreaks),expand = c(0,0),limits = c(0,max(dfm$index)+10)) +
  guides(colour="none", alpha="none", size="none",
         fill=guide_legend(override.aes=list(shape=c(21,23,25)))) +
  scale_y_continuous(expand = c(0,0),limits=c(0,max(dfm$marker+1,na.rm=TRUE)))+
  scale_size_continuous(range = c(0.25,3)) +
  scale_alpha_continuous(range=c(0.05,0.8), limits= c(0,8))+
  labs(x = "Chromosome") +
  ggtitle("Block 11") +
  theme_classic()+
  labs(y=expression(-Log10(q-value))) +
  scale_shape_manual(values=c(15,21,16))+
  scale_color_manual(values=c("grey", "dark grey"), guide="none") +
  guides(shape = guide_legend(override.aes = list(color = "grey", size = 5, linetype =0) ) )


b12.h <- subset(total.sig,  BLOCK == "12" & Sig.CASE == TRUE)
b12.c <- subset(B12.pv, QCON < 0.1)

B12.pp <- B12.pv %>%
  mutate(
    Group = case_when(
      SNP %in% b12.c$SNP ~ "Control Treatment Filtered",
      SNP %in% all_con$SNP ~ "Control Treatment Filtered",
      SNP %in% con_filter$SNP ~ "Control Treatment Filtered",
      SNP %in% singleton$SNP ~ "Single-Block",
      TRUE ~ "Shared SNP"
    )
  )

man <-ggman(B12.pp, pvalue="QCASE", chr="CHR", snp="SNP",bp="BP", relative.positions = TRUE ,sigLine = NA, pointSize=1.5,title = "", alpha = 0.5)

dfm <- man[[1]]

dfm$chrom_alt <- factor(dfm$chrom_alt, levels=c(0,1))

dfmo <- build_tier_highlights(dfm, block_num = 12, treatment_col = "Sig.CASE")

dfmsplit <- split(dfm, dfm$chrom)
xbreaks <- sapply(dfmsplit,function(x) {
    midpoint <- length(x$index)/2
    if(midpoint <1) midpoint <- 1
    return(x$index[midpoint])
})

b12.CASE <-ggplot(dfm, aes(x= index, y=marker, colour = as.factor(chrom_alt)))+
  geom_point(aes(alpha=marker, shape=Group, size = marker))+
  geom_point(data=subset(dfmo, Tier=="Core"),           aes(x=index, y=marker, fill=Tier), shape=21, size=3, color="black", alpha=0.9)+
  geom_point(data=subset(dfmo, Tier=="Aggregate"),      aes(x=index, y=marker, fill=Tier), shape=23, size=3, color="black", alpha=0.9)+
  geom_point(data=subset(dfmo, Tier=="Block-Specific"), aes(x=index, y=marker, fill=Tier), shape=25, size=3, color="black", alpha=0.9)+
  scale_fill_manual(values=tier_fill, name="Locus Tier") +
  scale_x_continuous(breaks = xbreaks, labels = names(xbreaks),expand = c(0,0),limits = c(0,max(dfm$index)+10)) +
  guides(colour="none", alpha="none", size="none",
         fill=guide_legend(override.aes=list(shape=c(21,23,25)))) +
  #scale_y_continuous(expand = c(0,0),limits=c(0,max(dfm$marker+1,na.rm=TRUE)))+
  scale_y_continuous(expand = c(0,0),limits=c(0,20))+ #Removes two outliers near end of CHR5
  labs(x = "Chromosome") +
  ggtitle("Block 12") +
  scale_alpha_continuous(range=c(0.05,0.8), limits= c(0,20))+
  scale_size_continuous(range = c(0.25,3), limits=c(0,20)) +
  theme_classic()+
  labs(y=expression(-Log10(q-value))) +
  scale_shape_manual(values=c(15,21,16))+
  scale_color_manual(values=c("grey", "dark grey"), guide="none") +
  guides(shape = guide_legend(override.aes = list(color = "grey", size = 5, linetype =0) ) )
```
```{r}
png(filename="CASEmpHighlighted.png", type="cairo",units="px", width=5600, height=3000, res=300, bg="transparent")

(b10.CASE / b11.CASE /b12.CASE )  + plot_annotation(tag_levels = 'A') + plot_layout(guides = 'collect') 

null <- dev.off()
```

#### SE
```{r, warning =FALSE, eval = FALSE}
# Treatment color and tier tint palette for SE Manhattan plots
tier_fill <- make_tier_palette("#0072B2")

b10.h <- subset(total.sig,  BLOCK == "10" & Sig.SE == TRUE)
b10.c <- subset(B10.pv, QCON < 0.1)

B10.pp <- B10.pv %>%
  mutate(
    Group = case_when(
      SNP %in% b10.c$SNP ~ "Control Treatment Filtered",
      SNP %in% all_con$SNP ~ "Control Treatment Filtered",
      SNP %in% con_filter$SNP ~ "Control Treatment Filtered",
      SNP %in% singleton$SNP ~ "Single-Block",
      TRUE ~ "Shared SNP"
    )
  )

man <-ggman(B10.pp, pvalue="QSE", chr="CHR", snp="SNP",bp="BP", relative.positions = TRUE ,sigLine = NA, pointSize=1.5,title = "", alpha = 0.5)

dfm <- man[[1]]

dfm$chrom_alt <- factor(dfm$chrom_alt, levels=c(0,1))

dfmo <- build_tier_highlights(dfm, block_num = 10, treatment_col = "Sig.SE")

dfmsplit <- split(dfm, dfm$chrom)
xbreaks <- sapply(dfmsplit,function(x) {
    midpoint <- length(x$index)/2
    if(midpoint <1) midpoint <- 1
    return(x$index[midpoint])
})

b10.SE <-ggplot(dfm, aes(x= index, y=marker, colour = as.factor(chrom_alt)))+
  geom_point(aes(alpha=marker, shape=Group, size = marker))+
  geom_point(data=subset(dfmo, Tier=="Core"),           aes(x=index, y=marker, fill=Tier), shape=21, size=3, color="black", alpha=0.9)+
  geom_point(data=subset(dfmo, Tier=="Aggregate"),      aes(x=index, y=marker, fill=Tier), shape=23, size=3, color="black", alpha=0.9)+
  geom_point(data=subset(dfmo, Tier=="Block-Specific"), aes(x=index, y=marker, fill=Tier), shape=25, size=3, color="black", alpha=0.9)+
  scale_fill_manual(values=tier_fill, name="Locus Tier") +
  scale_x_continuous(breaks = xbreaks, labels = names(xbreaks),expand = c(0,0),limits = c(0,max(dfm$index)+10)) +
  guides(colour="none", alpha="none", size="none",
         fill=guide_legend(override.aes=list(shape=c(21,23,25)))) +
  scale_y_continuous(expand = c(0,0),limits=c(0,max(dfm$marker+1,na.rm=TRUE)))+
  ggtitle("Block 10") +
  labs(x = "Chromosome") +
  scale_size_continuous(range = c(0.25,3)) +
  scale_alpha_continuous(range=c(0.05,0.8), limits= c(0,50))+
  theme_classic()+
  labs(y=expression(-Log10(q-value))) +
  scale_shape_manual(values=c(15,21,16))+
  scale_color_manual(values=c("grey", "dark grey"), guide="none") +
  guides(shape = guide_legend(override.aes = list(color = "grey", size = 5, linetype =0) ) )

b11.h <- subset(total.sig,  BLOCK == "11" & Sig.SE == TRUE)
b11.c <- subset(B11.pv, QCON < 0.1)

B11.pp <- B11.pv %>%
  mutate(
    Group = case_when(
      SNP %in% b11.c$SNP ~ "Control Treatment Filtered",
      SNP %in% all_con$SNP ~ "Control Treatment Filtered",
      SNP %in% con_filter$SNP ~ "Control Treatment Filtered",
      SNP %in% singleton$SNP ~ "Single-Block",
      TRUE ~ "Shared SNP"
    )
  )

man <-ggman(B11.pp, pvalue="QSE", chr="CHR", snp="SNP",bp="BP", relative.positions = TRUE ,sigLine = NA, pointSize=1.5,title = "", alpha = 0.5)

dfm <- man[[1]]

dfm$chrom_alt <- factor(dfm$chrom_alt, levels=c(0,1))


dfmo <- build_tier_highlights(dfm, block_num = 11, treatment_col = "Sig.SE")

dfmsplit <- split(dfm, dfm$chrom)
xbreaks <- sapply(dfmsplit,function(x) {
    midpoint <- length(x$index)/2
    if(midpoint <1) midpoint <- 1
    return(x$index[midpoint])
})

b11.SE <-ggplot(dfm, aes(x= index, y=marker, colour = as.factor(chrom_alt)))+
  geom_point(aes(alpha=marker, shape=Group, size = marker))+
  geom_point(data=subset(dfmo, Tier=="Core"),           aes(x=index, y=marker, fill=Tier), shape=21, size=3, color="black", alpha=0.9)+
  geom_point(data=subset(dfmo, Tier=="Aggregate"),      aes(x=index, y=marker, fill=Tier), shape=23, size=3, color="black", alpha=0.9)+
  geom_point(data=subset(dfmo, Tier=="Block-Specific"), aes(x=index, y=marker, fill=Tier), shape=25, size=3, color="black", alpha=0.9)+
  scale_fill_manual(values=tier_fill, name="Locus Tier") +
  scale_x_continuous(breaks = xbreaks, labels = names(xbreaks),expand = c(0,0),limits = c(0,max(dfm$index)+10)) +
  guides(colour="none", alpha="none", size="none",
         fill=guide_legend(override.aes=list(shape=c(21,23,25)))) +
  scale_y_continuous(expand = c(0,0),limits=c(0,max(dfm$marker+1,na.rm=TRUE)))+
  labs(x = "Chromosome") +
  ggtitle("Block 11") +
  theme_classic()+
  scale_size_continuous(range = c(0.25,3)) +
  labs(y=expression(-Log10(q-value))) +
  scale_shape_manual(values=c(15,21,16))+
  scale_color_manual(values=c("grey", "dark grey"), guide="none") +
  guides(shape = guide_legend(override.aes = list(color = "grey", size = 5, linetype =0) ) )


b12.h <- subset(total.sig,  BLOCK == "12" & Sig.SE == TRUE)
b12.c <- subset(B12.pv, QCON < 0.1)

B12.pp <- B12.pv %>%
  mutate(
    Group = case_when(
      SNP %in% b12.c$SNP ~ "Control Treatment Filtered",
      SNP %in% all_con$SNP ~ "Control Treatment Filtered",
      SNP %in% con_filter$SNP ~ "Control Treatment Filtered",
      SNP %in% singleton$SNP ~ "Single-Block",
      TRUE ~ "Shared SNP"
    )
  )

man <-ggman(B12.pp, pvalue="QSE", chr="CHR", snp="SNP",bp="BP", relative.positions = TRUE ,sigLine = NA, pointSize=1.5,title = "", alpha = 0.5)

dfm <- man[[1]]

dfm$chrom_alt <- factor(dfm$chrom_alt, levels=c(0,1))

dfmo <- build_tier_highlights(dfm, block_num = 12, treatment_col = "Sig.SE")

dfmsplit <- split(dfm, dfm$chrom)
xbreaks <- sapply(dfmsplit,function(x) {
    midpoint <- length(x$index)/2
    if(midpoint <1) midpoint <- 1
    return(x$index[midpoint])
})

b12.SE <-ggplot(dfm, aes(x= index, y=marker, colour = as.factor(chrom_alt)))+
  geom_point(aes(alpha=marker, shape=Group, size = marker))+
  geom_point(data=subset(dfmo, Tier=="Core"),           aes(x=index, y=marker, fill=Tier), shape=21, size=3, color="black", alpha=0.9)+
  geom_point(data=subset(dfmo, Tier=="Aggregate"),      aes(x=index, y=marker, fill=Tier), shape=23, size=3, color="black", alpha=0.9)+
  geom_point(data=subset(dfmo, Tier=="Block-Specific"), aes(x=index, y=marker, fill=Tier), shape=25, size=3, color="black", alpha=0.9)+
  scale_fill_manual(values=tier_fill, name="Locus Tier") +
  scale_x_continuous(breaks = xbreaks, labels = names(xbreaks),expand = c(0,0),limits = c(0,max(dfm$index)+10)) +
  guides(colour="none", alpha="none", size="none",
         fill=guide_legend(override.aes=list(shape=c(21,23,25)))) +
  #scale_y_continuous(expand = c(0,0),limits=c(0,max(dfm$marker+1,na.rm=TRUE)))+
  scale_y_continuous(expand = c(0,0),limits=c(0,15))+ #Removes two singleton loci at end of CHR 5
  labs(x = "Chromosome") +
  scale_size_continuous(range = c(0.25,3), limits= c(0,15)) +
  ggtitle("Block 12") +
  theme_classic()+
  labs(y=expression(-Log10(q-value))) +
  scale_shape_manual(values=c(15,21,16))+
  scale_color_manual(values=c("grey", "dark grey"), guide="none") +
  guides(shape = guide_legend(override.aes = list(color = "grey", size = 5, linetype =0) ) )

```
```{r}
png(filename="SEmpHighlighted.png", type="cairo",units="px", width=5600, height=3000, res=300, bg="transparent")

(b10.SE / b11.SE /b12.SE )  + plot_annotation(tag_levels = 'A') + plot_layout(guides = 'collect') 
#(b10.SE / b11.SE /b12.SE )  + plot_annotation(tag_levels = 'A') & theme_black()
#man+scale_fill_manual(values = c("#009E73","#E69F00", "#0072B2"),name = "Legend")
null <- dev.off()
```

#### CA
```{r, warning =FALSE, eval = FALSE}
# Treatment color and tier tint palette for CA Manhattan plots
tier_fill <- make_tier_palette("#E69F00")

b10.h <- subset(total.sig,  BLOCK == "10" & Sig.CA == TRUE)
b10.c <- subset(B10.pv, QCON < 0.1)

B10.pp <- B10.pv %>%
  mutate(
    Group = case_when(
      SNP %in% b10.c$SNP ~ "Control Treatment Filtered",
      SNP %in% all_con$SNP ~ "Control Treatment Filtered",
      SNP %in% con_filter$SNP ~ "Control Treatment Filtered",
      SNP %in% singleton$SNP ~ "Single-Block",
      TRUE ~ "Shared SNP"
    )
  )

man <-ggman(B10.pp, pvalue="QCA", chr="CHR", snp="SNP",bp="BP", relative.positions = TRUE ,sigLine = NA, pointSize=1.5,title = "", alpha = 0.5)

dfm <- man[[1]]

dfm$chrom_alt <- factor(dfm$chrom_alt, levels=c(0,1))

dfmo <- build_tier_highlights(dfm, block_num = 10, treatment_col = "Sig.CA")

dfmsplit <- split(dfm, dfm$chrom)
xbreaks <- sapply(dfmsplit,function(x) {
    midpoint <- length(x$index)/2
    if(midpoint <1) midpoint <- 1
    return(x$index[midpoint])
})

b10.CA <-ggplot(dfm, aes(x= index, y=marker, colour = as.factor(chrom_alt)))+
  geom_point(aes(alpha=marker, shape=Group, size = marker))+
  geom_point(data=subset(dfmo, Tier=="Core"),           aes(x=index, y=marker, fill=Tier), shape=21, size=3, color="black", alpha=0.9)+
  geom_point(data=subset(dfmo, Tier=="Aggregate"),      aes(x=index, y=marker, fill=Tier), shape=23, size=3, color="black", alpha=0.9)+
  geom_point(data=subset(dfmo, Tier=="Block-Specific"), aes(x=index, y=marker, fill=Tier), shape=25, size=3, color="black", alpha=0.9)+
  scale_fill_manual(values=tier_fill, name="Locus Tier") +
  scale_x_continuous(breaks = xbreaks, labels = names(xbreaks),expand = c(0,0),limits = c(0,max(dfm$index)+10)) +
  guides(colour="none", alpha="none", size="none",
         fill=guide_legend(override.aes=list(shape=c(21,23,25)))) +
  #scale_y_continuous(expand = c(0,0),limits=c(0,max(dfm$marker+1,na.rm=TRUE)))+
  scale_y_continuous(expand = c(0,0),limits=c(0,32))+ #Limit manually set, removes 3 control filtered loci in CHR 2
  ggtitle("Block 10") +
  labs(x = "Chromosome") +
  scale_size_continuous(range = c(0.25,3), limits=c(0,32)) +
  theme_classic()+
  labs(y=expression(-Log10(q-value))) +
  scale_shape_manual(values=c(15,21,16))+
  scale_color_manual(values=c("grey", "dark grey"), guide="none") +
  guides(shape = guide_legend(override.aes = list(color = "grey", size = 5, linetype =0) ) )

b11.h <- subset(total.sig,  BLOCK == "11" & Sig.CA == TRUE)
b11.c <- subset(B11.pv, QCON < 0.1)

B11.pp <- B11.pv %>%
  mutate(
    Group = case_when(
      SNP %in% b11.c$SNP ~ "Control Treatment Filtered",
      SNP %in% all_con$SNP ~ "Control Treatment Filtered",
      SNP %in% con_filter$SNP ~ "Control Treatment Filtered",
      SNP %in% singleton$SNP ~ "Single-Block",
      TRUE ~ "Shared SNP"
    )
  )

man <-ggman(B11.pp, pvalue="QCA", chr="CHR", snp="SNP",bp="BP", relative.positions = TRUE ,sigLine = NA, pointSize=1.5,title = "", alpha = 0.5)

dfm <- man[[1]]

dfm$chrom_alt <- factor(dfm$chrom_alt, levels=c(0,1))


dfmo <- build_tier_highlights(dfm, block_num = 11, treatment_col = "Sig.CA")

dfmsplit <- split(dfm, dfm$chrom)
xbreaks <- sapply(dfmsplit,function(x) {
    midpoint <- length(x$index)/2
    if(midpoint <1) midpoint <- 1
    return(x$index[midpoint])
})

b11.CA <-ggplot(dfm, aes(x= index, y=marker, colour = as.factor(chrom_alt)))+
  geom_point(aes(alpha=marker, shape=Group, size = marker))+
  geom_point(data=subset(dfmo, Tier=="Core"),           aes(x=index, y=marker, fill=Tier), shape=21, size=3, color="black", alpha=0.9)+
  geom_point(data=subset(dfmo, Tier=="Aggregate"),      aes(x=index, y=marker, fill=Tier), shape=23, size=3, color="black", alpha=0.9)+
  geom_point(data=subset(dfmo, Tier=="Block-Specific"), aes(x=index, y=marker, fill=Tier), shape=25, size=3, color="black", alpha=0.9)+
  scale_fill_manual(values=tier_fill, name="Locus Tier") +
  scale_x_continuous(breaks = xbreaks, labels = names(xbreaks),expand = c(0,0),limits = c(0,max(dfm$index)+10)) +
  guides(colour="none", alpha="none", size="none",
         fill=guide_legend(override.aes=list(shape=c(21,23,25)))) +
  scale_y_continuous(expand = c(0,0),limits=c(0,max(dfm$marker+1,na.rm=TRUE)))+
  labs(x = "Chromosome") +
  ggtitle("Block 11") +
  scale_size_continuous(range = c(0.25,3)) +
  theme_classic()+
  labs(y=expression(-Log10(q-value))) +
  scale_shape_manual(values=c(15,21,16))+
  scale_color_manual(values=c("grey", "dark grey"), guide="none") +
  guides(shape = guide_legend(override.aes = list(color = "grey", size = 5, linetype =0) ) )


b12.h <- subset(total.sig,  BLOCK == "12" & Sig.CA == TRUE)
b12.c <- subset(B12.pv, QCON < 0.1)

B12.pp <- B12.pv %>%
  mutate(
    Group = case_when(
      SNP %in% b12.c$SNP ~ "Control Treatment Filtered",
      SNP %in% all_con$SNP ~ "Control Treatment Filtered",
      SNP %in% con_filter$SNP ~ "Control Treatment Filtered",
      SNP %in% singleton$SNP ~ "Single-Block",
      TRUE ~ "Shared SNP"
    )
  )

man <-ggman(B12.pp, pvalue="QCA", chr="CHR", snp="SNP",bp="BP", relative.positions = TRUE ,sigLine = NA, pointSize=1.5,title = "", alpha = 0.5)

dfm <- man[[1]]

dfm$chrom_alt <- factor(dfm$chrom_alt, levels=c(0,1))

dfmo <- build_tier_highlights(dfm, block_num = 12, treatment_col = "Sig.CA")

dfmsplit <- split(dfm, dfm$chrom)
xbreaks <- sapply(dfmsplit,function(x) {
    midpoint <- length(x$index)/2
    if(midpoint <1) midpoint <- 1
    return(x$index[midpoint])
})

b12.CA <-ggplot(dfm, aes(x= index, y=marker, colour = as.factor(chrom_alt)))+
  geom_point(aes(alpha=marker, shape=Group, size = marker))+
  geom_point(data=subset(dfmo, Tier=="Core"),           aes(x=index, y=marker, fill=Tier), shape=21, size=3, color="black", alpha=0.9)+
  geom_point(data=subset(dfmo, Tier=="Aggregate"),      aes(x=index, y=marker, fill=Tier), shape=23, size=3, color="black", alpha=0.9)+
  geom_point(data=subset(dfmo, Tier=="Block-Specific"), aes(x=index, y=marker, fill=Tier), shape=25, size=3, color="black", alpha=0.9)+
  scale_fill_manual(values=tier_fill, name="Locus Tier") +
  scale_x_continuous(breaks = xbreaks, labels = names(xbreaks),expand = c(0,0),limits = c(0,max(dfm$index)+10)) +
  guides(colour="none", alpha="none", size="none",
         fill=guide_legend(override.aes=list(shape=c(21,23,25)))) +
  #scale_y_continuous(expand = c(0,0),limits=c(0,max(dfm$marker+1,na.rm=TRUE)))+
  scale_y_continuous(expand = c(0,0),limits=c(0,20))+ #removes two singleton loci near end of CHR 5
  labs(x = "Chromosome") +
  scale_size_continuous(range = c(0.25,3), limits=c(0,20)) +
  ggtitle("Block 12") +
  theme_classic()+
  labs(y=expression(-Log10(q-value))) +
  scale_shape_manual(values=c(15,21,16))+
  scale_color_manual(values=c("grey", "dark grey"), guide="none")
```
```{r}
png(filename="CAmpHighlighted.png", type="cairo",units="px", width=5600, height=3000, res=300, bg="transparent")

(b10.CA / b11.CA /b12.CA )  + plot_annotation(tag_levels = 'A') + plot_layout(guides = 'collect') 
#(b10.CA / b11.CA /b12.CA )  + plot_annotation(tag_levels = 'A') & theme_black()
#man+scale_fill_manual(values = c("#009E73","#E69F00", "#0072B2"),name = "Legend")
null <- dev.off()
```


# Venn Diagrams
```{r}
library(VennDiagram)

sig.CA <- nrow(unique(subset(grouped_total.sig, Sig.CA == "TRUE",c(SNP))))
sig.SE <- nrow(unique(subset(grouped_total.sig, Sig.SE == "TRUE",c(SNP))))
sig.CASE <- nrow(unique(subset(grouped_total.sig, Sig.CASE == "TRUE",c(SNP))))

sig.CA.SE <- nrow(unique(subset(grouped_total.sig, Sig.CA == "TRUE" & Sig.SE == "TRUE",c(SNP) )))
sig.CA.CASE <- nrow(unique(subset(grouped_total.sig,Sig.CA == "TRUE" & Sig.CASE == "TRUE",c(SNP) )))

sig.SE.CASE <- nrow(unique(subset(grouped_total.sig, Sig.CASE == "TRUE" & Sig.SE == "TRUE" ,c(SNP))))

sig.all <- nrow(unique(subset(grouped_total.sig, Sig.CASE == "TRUE" & Sig.CA == "TRUE" & Sig.SE == "TRUE",c(SNP))))
#sig.all <- nrow(subset(pp1, Sig.CA == TRUE & Sig.SE == TRUE  & Sig.CASE == TRUE & QPCADAPT < alpha))

png(filename="Ven.png", type="cairo",units="px", width=3000, height=3000, res=200, bg="transparent")

venn.plot <- draw.triple.venn(
  area1=sig.CA, area2=sig.SE, area3=sig.CASE, 
  n12= sig.CA.SE, n13=sig.CA.CASE, 
  n23=sig.SE.CASE,
  n123=sig.all, cex=5,
  category = c("CA", "SE", "CASE"),
  fill = cbPaletteSmall3,cat.cex = rep(5, 3),
  cat.col = cbPaletteSmall3, label.col = rep("white", 7))

dev.off()
grid.draw(venn.plot)
grid.newpage()

png(filename="VenBO.png", type="cairo",units="px", width=3000, height=3000, res=200, bg="transparent")
venn.plot <- draw.triple.venn(
  area1=sig.CA, area2=sig.SE, area3=sig.CASE, 
  n12= sig.CA.SE, n13=sig.CA.CASE, 
  n23=sig.SE.CASE,
  n123=sig.all, cex=5,
  category = c("CA", "SE", "CASE"),
  fill = cbPaletteSmall3,cat.cex = rep(5, 3),
  cat.col = cbPaletteSmall3, label.col = rep("black", 7))
dev.off()
```
### B10 Only
```{r}
sig.CA <- nrow(unique(subset(ppsig.B10.01, Sig.CA == TRUE,c(SNP))))
sig.SE <- nrow(unique(subset(ppsig.B10.01, Sig.SE == TRUE ,c(SNP))))
sig.CASE <- nrow(unique(subset(ppsig.B10.01, Sig.CASE == TRUE,c(SNP))))

sig.CA.SE <- nrow(unique(subset(ppsig.B10.01,Sig.CA == TRUE & Sig.SE == TRUE,c(SNP) )))
sig.CA.CASE <- nrow(unique(subset(ppsig.B10.01,Sig.CA == TRUE & Sig.CASE == TRUE ,c(SNP) )))

sig.SE.CASE <- nrow(unique(subset(ppsig.B10.01, Sig.SE == TRUE & Sig.CASE == TRUE ,c(SNP))))

sig.all <- nrow(unique(subset(ppsig.B10.01, Sig.CA == TRUE & Sig.SE == TRUE & Sig.CASE == TRUE,c(SNP))))
#sig.all <- nrow(subset(pp1, Sig.CA == TRUE & Sig.SE == TRUE  & Sig.CASE == TRUE & QPCADAPT < alpha))

png(filename="VenB10.png", type="cairo",units="px", width=3000, height=3000, res=200, bg="transparent")

venn.plot <- draw.triple.venn(
  area1=sig.CA, area2=sig.SE, area3=sig.CASE, 
  n12= sig.CA.SE, n13=sig.CA.CASE, 
  n23=sig.SE.CASE,
  n123=sig.all, cex=5,
  category = c("CA", "SE", "CASE"),
  fill = cbPaletteSmall3,cat.cex = rep(5, 3),
  cat.col = cbPaletteSmall3, label.col = rep("white", 7))
dev.off()
png(filename="VenBOB10.png", type="cairo",units="px", width=3000, height=3000, res=200, bg="transparent")
venn.plot <- draw.triple.venn(
  area1=sig.CA, area2=sig.SE, area3=sig.CASE, 
  n12= sig.CA.SE, n13=sig.CA.CASE, 
  n23=sig.SE.CASE,
  n123=sig.all, cex=5,
  category = c("CA", "SE", "CASE"),
  fill = cbPaletteSmall3,cat.cex = rep(5, 3),
  cat.col = cbPaletteSmall3, label.col = rep("black", 7))
dev.off()
```
### B11 Only
```{r}
sig.CA <- nrow(unique(subset(ppsig.B11.01, Sig.CA == TRUE,c(SNP))))
sig.SE <- nrow(unique(subset(ppsig.B11.01, Sig.SE == TRUE,c(SNP))))
sig.CASE <- nrow(unique(subset(ppsig.B11.01, Sig.CASE == TRUE,c(SNP))))

sig.CA.SE <- nrow(unique(subset(ppsig.B11.01, Sig.CA == TRUE & Sig.SE == TRUE,c(SNP) )))
sig.CA.CASE <- nrow(unique(subset(ppsig.B11.01,Sig.CA == TRUE & Sig.CASE == TRUE ,c(SNP) )))

sig.SE.CASE <- nrow(unique(subset(ppsig.B11.01, Sig.SE == TRUE & Sig.CASE == TRUE ,c(SNP))))

sig.all <- nrow(unique(subset(ppsig.B11.01, Sig.CA == TRUE & Sig.SE == TRUE & Sig.CASE == TRUE,c(SNP))))
#sig.all <- nrow(subset(pp1, Sig.CA == TRUE & Sig.SE == TRUE  & Sig.CASE == TRUE & QPCADAPT < alpha))

png(filename="VenB11.png", type="cairo",units="px", width=3000, height=3000, res=200, bg="transparent")

venn.plot <- draw.triple.venn(
  area1=sig.CA, area2=sig.SE, area3=sig.CASE, 
  n12= sig.CA.SE, n13=sig.CA.CASE, 
  n23=sig.SE.CASE,
  n123=sig.all, cex=5,
  category = c("CA", "SE", "CASE"),
  fill = cbPaletteSmall3,cat.cex = rep(5, 3),
  cat.col = cbPaletteSmall3, label.col = rep("white", 7))
dev.off()
png(filename="VenBOB11.png", type="cairo",units="px", width=3000, height=3000, res=200, bg="transparent")
venn.plot <- draw.triple.venn(
  area1=sig.CA, area2=sig.SE, area3=sig.CASE, 
  n12= sig.CA.SE, n13=sig.CA.CASE, 
  n23=sig.SE.CASE,
  n123=sig.all, cex=5,
  category = c("CA", "SE", "CASE"),
  fill = cbPaletteSmall3,cat.cex = rep(5, 3),
  cat.col = cbPaletteSmall3, label.col = rep("black", 7))
dev.off()
```

### B12 Only
```{r}
library(VennDiagram)
alpha = 0.01
alpha2 = 0.1

#pp2 <- subset(pp1, QCON > alpha2)
sig.CA <- nrow(unique(subset(ppsig.B11.01, Sig.CA == TRUE,c(SNP))))
sig.SE <- nrow(unique(subset(ppsig.B11.01, Sig.SE == TRUE,c(SNP))))
sig.CASE <- nrow(unique(subset(ppsig.B11.01, Sig.CASE == TRUE,c(SNP))))

sig.CA.SE <- nrow(unique(subset(ppsig.B11.01, Sig.CA == TRUE & Sig.SE == TRUE,c(SNP) )))
sig.CA.CASE <- nrow(unique(subset(ppsig.B11.01,Sig.CA == TRUE & Sig.CASE == TRUE ,c(SNP) )))

sig.SE.CASE <- nrow(unique(subset(ppsig.B11.01, Sig.SE == TRUE & Sig.CASE == TRUE ,c(SNP))))

sig.all <- nrow(unique(subset(ppsig.B11.01, Sig.CA == TRUE & Sig.SE == TRUE & Sig.CASE == TRUE,c(SNP))))

png(filename="VenB12.png", type="cairo",units="px", width=3000, height=3000, res=200, bg="transparent")

venn.plot <- draw.triple.venn(
  area1=sig.CA, area2=sig.SE, area3=sig.CASE, 
  n12= sig.CA.SE, n13=sig.CA.CASE, 
  n23=sig.SE.CASE,
  n123=sig.all, cex=5,
  category = c("CA", "SE", "CASE"),
  fill = cbPaletteSmall3,cat.cex = rep(5, 3),
  cat.col = cbPaletteSmall3, label.col = rep("white", 7))
dev.off()
png(filename="VenBOB12.png", type="cairo",units="px", width=3000, height=3000, res=200, bg="transparent")
venn.plot <- draw.triple.venn(
  area1=sig.CA, area2=sig.SE, area3=sig.CASE, 
  n12= sig.CA.SE, n13=sig.CA.CASE, 
  n23=sig.SE.CASE,
  n123=sig.all, cex=5,
  category = c("CA", "SE", "CASE"),
  fill = cbPaletteSmall3,cat.cex = rep(5, 3),
  cat.col = cbPaletteSmall3, label.col = rep("black", 7))
dev.off()
```

### LOC Only
```{bash}
source activate CASE

cat Sig.loci.1.CA.LOC Sig.loci.1.SE.LOC | sort | uniq -c | mawk '$1 > 1'  | mawk '{print $2}' > Sig.loci.1.CA.SE.LOC
cat Sig.loci.1.CA.LOC Sig.loci.1.CASE.LOC | sort | uniq -c | mawk '$1 > 1'| mawk '{print $2}' > Sig.loci.1.CA.CASE.LOC
cat Sig.loci.1.SE.LOC Sig.loci.1.CASE.LOC | sort | uniq -c | mawk '$1 > 1' | mawk '{print $2}'> Sig.loci.1.SE.CASE.LOC
cat Sig.loci.1.SE.LOC Sig.loci.1.CASE.LOC Sig.loci.1.CA.LOC | sort | uniq -c | mawk '$1 > 2'| mawk '{print $2}' > Sig.loci.1.SE.CASE.CA.LOC

cat Sig.loci.1.CASE.LOC <(cat Sig.loci.1.SE.LOC Sig.loci.1.CASE.LOC Sig.loci.1.CA.LOC | sort | uniq -c | mawk '$1 < 2' | mawk '{print $2}') | sort | uniq -c | mawk '$1 > 1' | mawk '{print $2}' > Sig.loci.CASE.ONLY.LOC
cat Sig.loci.1.SE.LOC <(cat Sig.loci.1.SE.LOC Sig.loci.1.CASE.LOC Sig.loci.1.CA.LOC | sort | uniq -c | mawk '$1 < 2' | mawk '{print $2}') | sort | uniq -c | mawk '$1 > 1' | mawk '{print $2}' > Sig.loci.SE.ONLY.LOC
cat Sig.loci.1.CA.LOC <(cat Sig.loci.1.SE.LOC Sig.loci.1.CASE.LOC Sig.loci.1.CA.LOC | sort | uniq -c | mawk '$1 < 2' | mawk '{print $2}') | sort | uniq -c | mawk '$1 > 1' | mawk '{print $2}' > Sig.loci.CA.ONLY.LOC

grep -v -f Sig.loci.1.CA.LOC Sig.loci.1.SE.CASE.LOC > Sig.loci.CASE.SE.ONLY.LOC



cat Sig.loci.B10.CA.LOC Sig.loci.B10.SE.LOC | sort | uniq -c | mawk '$1 > 1'  | mawk '{print $2}' > Sig.loci.B10.CA.SE.LOC
cat Sig.loci.B10.CA.LOC Sig.loci.B10.CASE.LOC | sort | uniq -c | mawk '$1 > 1'| mawk '{print $2}' > Sig.loci.B10.CA.CASE.LOC
cat Sig.loci.B10.SE.LOC Sig.loci.B10.CASE.LOC | sort | uniq -c | mawk '$1 > 1' | mawk '{print $2}'> Sig.loci.B10.SE.CASE.LOC
cat Sig.loci.B10.SE.LOC Sig.loci.B10.CASE.LOC Sig.loci.B10.CA.LOC | sort | uniq -c | mawk '$1 > 2'| mawk '{print $2}' > Sig.loci.B10.SE.CASE.CA.LOC

cat Sig.loci.B10.CASE.LOC <(cat Sig.loci.B10.SE.LOC Sig.loci.B10.CASE.LOC Sig.loci.B10.CA.LOC | sort | uniq -c | mawk '$1 < 2' | mawk '{print $2}') | sort | uniq -c | mawk '$1 > 1' | mawk '{print $2}' > Sig.loci.B10.CASE.ONLY.LOC
cat Sig.loci.B10.SE.LOC <(cat Sig.loci.B10.SE.LOC Sig.loci.B10.CASE.LOC Sig.loci.B10.CA.LOC | sort | uniq -c | mawk '$1 < 2' | mawk '{print $2}') | sort | uniq -c | mawk '$1 > 1' | mawk '{print $2}' > Sig.loci.B10.SE.ONLY.LOC
cat Sig.loci.B10.CA.LOC <(cat Sig.loci.B10.SE.LOC Sig.loci.B10.CASE.LOC Sig.loci.B10.CA.LOC | sort | uniq -c | mawk '$1 < 2' | mawk '{print $2}') | sort | uniq -c | mawk '$1 > 1' | mawk '{print $2}' > Sig.loci.B10.CA.ONLY.LOC

grep -v -f Sig.loci.B10.CA.LOC Sig.loci.B10.SE.CASE.LOC > Sig.loci.B10.CASE.SE.ONLY.LOC

cat Sig.loci.B11.CA.LOC Sig.loci.B11.SE.LOC | sort | uniq -c | mawk '$1 > 1'  | mawk '{print $2}' > Sig.loci.B11.CA.SE.LOC
cat Sig.loci.B11.CA.LOC Sig.loci.B11.CASE.LOC | sort | uniq -c | mawk '$1 > 1'| mawk '{print $2}' > Sig.loci.B11.CA.CASE.LOC
cat Sig.loci.B11.SE.LOC Sig.loci.B11.CASE.LOC | sort | uniq -c | mawk '$1 > 1' | mawk '{print $2}'> Sig.loci.B11.SE.CASE.LOC
cat Sig.loci.B11.SE.LOC Sig.loci.B11.CASE.LOC Sig.loci.B11.CA.LOC | sort | uniq -c | mawk '$1 > 2'| mawk '{print $2}' > Sig.loci.B11.SE.CASE.CA.LOC

cat Sig.loci.B11.CASE.LOC <(cat Sig.loci.B11.SE.LOC Sig.loci.B11.CASE.LOC Sig.loci.B11.CA.LOC | sort | uniq -c | mawk '$1 < 2' | mawk '{print $2}') | sort | uniq -c | mawk '$1 > 1' | mawk '{print $2}' > Sig.loci.B11.CASE.ONLY.LOC
cat Sig.loci.B11.SE.LOC <(cat Sig.loci.B11.SE.LOC Sig.loci.B11.CASE.LOC Sig.loci.B11.CA.LOC | sort | uniq -c | mawk '$1 < 2' | mawk '{print $2}') | sort | uniq -c | mawk '$1 > 1' | mawk '{print $2}' > Sig.loci.B11.SE.ONLY.LOC
cat Sig.loci.B11.CA.LOC <(cat Sig.loci.B11.SE.LOC Sig.loci.B11.CASE.LOC Sig.loci.B11.CA.LOC | sort | uniq -c | mawk '$1 < 2' | mawk '{print $2}') | sort | uniq -c | mawk '$1 > 1' | mawk '{print $2}' > Sig.loci.B11.CA.ONLY.LOC

grep -v -f Sig.loci.B11.CA.LOC Sig.loci.B11.SE.CASE.LOC > Sig.loci.B11.CASE.SE.ONLY.LOC

cat Sig.loci.B12.CA.LOC Sig.loci.B12.SE.LOC | sort | uniq -c | mawk '$1 > 1'  | mawk '{print $2}' > Sig.loci.B12.CA.SE.LOC
cat Sig.loci.B12.CA.LOC Sig.loci.B12.CASE.LOC | sort | uniq -c | mawk '$1 > 1'| mawk '{print $2}' > Sig.loci.B12.CA.CASE.LOC
cat Sig.loci.B12.SE.LOC Sig.loci.B12.CASE.LOC | sort | uniq -c | mawk '$1 > 1' | mawk '{print $2}'> Sig.loci.B12.SE.CASE.LOC
cat Sig.loci.B12.SE.LOC Sig.loci.B12.CASE.LOC Sig.loci.B12.CA.LOC | sort | uniq -c | mawk '$1 > 2'| mawk '{print $2}' > Sig.loci.B12.SE.CASE.CA.LOC

cat Sig.loci.B12.CASE.LOC <(cat Sig.loci.B12.SE.LOC Sig.loci.B12.CASE.LOC Sig.loci.B12.CA.LOC | sort | uniq -c | mawk '$1 < 2' | mawk '{print $2}') | sort | uniq -c | mawk '$1 > 1' | mawk '{print $2}' > Sig.loci.B12.CASE.ONLY.LOC
cat Sig.loci.B12.SE.LOC <(cat Sig.loci.B12.SE.LOC Sig.loci.B12.CASE.LOC Sig.loci.B12.CA.LOC | sort | uniq -c | mawk '$1 < 2' | mawk '{print $2}') | sort | uniq -c | mawk '$1 > 1' | mawk '{print $2}' > Sig.loci.B12.SE.ONLY.LOC
cat Sig.loci.B12.CA.LOC <(cat Sig.loci.B12.SE.LOC Sig.loci.B12.CASE.LOC Sig.loci.B12.CA.LOC | sort | uniq -c | mawk '$1 < 2' | mawk '{print $2}') | sort | uniq -c | mawk '$1 > 1' | mawk '{print $2}' > Sig.loci.B12.CA.ONLY.LOC

grep -v -f Sig.loci.B12.CA.LOC Sig.loci.B12.SE.CASE.LOC > Sig.loci.B12.CASE.SE.ONLY.LOC

```

```{r}
library(VennDiagram)
alpha = 0.05
alpha2 = 0.1

Sig.loci.1.CA.LOC <- read.table("Sig.loci.1.CA.LOC", header =FALSE)
Sig.loci.1.SE.LOC <- read.table("Sig.loci.1.SE.LOC", header =FALSE)
Sig.loci.1.CASE.LOC <- read.table("Sig.loci.1.CASE.LOC", header =FALSE)

sig.CA <- nrow(unique(Sig.loci.1.CA.LOC))
sig.SE <- nrow(unique(Sig.loci.1.SE.LOC))
sig.CASE <- nrow(unique(Sig.loci.1.CASE.LOC))

sig.CA.SE <- nrow(unique(read.table("Sig.loci.1.CA.SE.LOC", header =FALSE)))
sig.CA.CASE <- nrow(unique(read.table("Sig.loci.1.CA.CASE.LOC", header =FALSE)))
sig.SE.CASE <- nrow(unique(read.table("Sig.loci.1.SE.CASE.LOC", header =FALSE)))

sig.all <- nrow(unique(read.table("Sig.loci.1.SE.CASE.CA.LOC", header =FALSE)))


png(filename="VenLOC.png", type="cairo",units="px", width=3000, height=3000, res=200, bg="transparent")
venn.plot <- draw.triple.venn(
  area1=sig.CA, area2=sig.SE, area3=sig.CASE, 
  n12= sig.CA.SE, n13=sig.CA.CASE, 
  n23=sig.SE.CASE,
  n123=sig.all, cex=5,
  category = c("CA", "SE", "CASE"),
  fill = cbPaletteSmall3,cat.cex = rep(5, 3),
  cat.col = cbPaletteSmall3, label.col = rep("white", 7))
dev.off()
grid.draw(venn.plot)
grid.newpage()
```
### B10
```{r}
library(VennDiagram)
alpha = 0.05
alpha2 = 0.1

Sig.loci.B10.CA.LOC <- read.table("Sig.loci.B10.CA.LOC", header =FALSE)
Sig.loci.B10.SE.LOC <- read.table("Sig.loci.B10.SE.LOC", header =FALSE)
Sig.loci.B10.CASE.LOC <- read.table("Sig.loci.B10.CASE.LOC", header =FALSE)

sig.CA <- nrow(unique(Sig.loci.B10.CA.LOC))
sig.SE <- nrow(unique(Sig.loci.B10.SE.LOC))
sig.CASE <- nrow(unique(Sig.loci.B10.CASE.LOC))

sig.CA.SE <- nrow(unique(read.table("Sig.loci.B10.CA.SE.LOC", header =FALSE)))
sig.CA.CASE <- nrow(unique(read.table("Sig.loci.B10.CA.CASE.LOC", header =FALSE)))
sig.SE.CASE <- nrow(unique(read.table("Sig.loci.B10.SE.CASE.LOC", header =FALSE)))

sig.all <- nrow(unique(read.table("Sig.loci.B10.SE.CASE.CA.LOC", header =FALSE)))


png(filename="VenB10LOC.png", type="cairo",units="px", width=3000, height=3000, res=200, bg="transparent")
venn.plot <- draw.triple.venn(
  area1=sig.CA, area2=sig.SE, area3=sig.CASE, 
  n12= sig.CA.SE, n13=sig.CA.CASE, 
  n23=sig.SE.CASE,
  n123=sig.all, cex=5,
  category = c("CA", "SE", "CASE"),
  fill = cbPaletteSmall3,cat.cex = rep(5, 3),
  cat.col = cbPaletteSmall3, label.col = rep("white", 7))
dev.off()

```

### B11
```{r}
library(VennDiagram)
alpha = 0.05
alpha2 = 0.1

Sig.loci.B11.CA.LOC <- read.table("Sig.loci.B11.CA.LOC", header =FALSE)
Sig.loci.B11.SE.LOC <- read.table("Sig.loci.B11.SE.LOC", header =FALSE)
Sig.loci.B11.CASE.LOC <- read.table("Sig.loci.B11.CASE.LOC", header =FALSE)

sig.CA <- nrow(unique(Sig.loci.B11.CA.LOC))
sig.SE <- nrow(unique(Sig.loci.B11.SE.LOC))
sig.CASE <- nrow(unique(Sig.loci.B11.CASE.LOC))

sig.CA.SE <- nrow(unique(read.table("Sig.loci.B11.CA.SE.LOC", header =FALSE)))
sig.CA.CASE <- nrow(unique(read.table("Sig.loci.B11.CA.CASE.LOC", header =FALSE)))
sig.SE.CASE <- nrow(unique(read.table("Sig.loci.B11.SE.CASE.LOC", header =FALSE)))

sig.all <- nrow(unique(read.table("Sig.loci.B11.SE.CASE.CA.LOC", header =FALSE)))


png(filename="VenB11LOC.png", type="cairo",units="px", width=3000, height=3000, res=200, bg="transparent")
venn.plot <- draw.triple.venn(
  area1=sig.CA, area2=sig.SE, area3=sig.CASE, 
  n12= sig.CA.SE, n13=sig.CA.CASE, 
  n23=sig.SE.CASE,
  n123=sig.all, cex=5,
  category = c("CA", "SE", "CASE"),
  fill = cbPaletteSmall3,cat.cex = rep(5, 3),
  cat.col = cbPaletteSmall3, label.col = rep("white", 7))
dev.off()

```

### B12
```{r}
library(VennDiagram)
alpha = 0.05
alpha2 = 0.1

Sig.loci.B12.CA.LOC <- read.table("Sig.loci.B12.CA.LOC", header =FALSE)
Sig.loci.B12.SE.LOC <- read.table("Sig.loci.B12.SE.LOC", header =FALSE)
Sig.loci.B12.CASE.LOC <- read.table("Sig.loci.B12.CASE.LOC", header =FALSE)

sig.CA <- nrow(unique(Sig.loci.B12.CA.LOC))
sig.SE <- nrow(unique(Sig.loci.B12.SE.LOC))
sig.CASE <- nrow(unique(Sig.loci.B12.CASE.LOC))

sig.CA.SE <- nrow(unique(read.table("Sig.loci.B12.CA.SE.LOC", header =FALSE)))
sig.CA.CASE <- nrow(unique(read.table("Sig.loci.B12.CA.CASE.LOC", header =FALSE)))
sig.SE.CASE <- nrow(unique(read.table("Sig.loci.B12.SE.CASE.LOC", header =FALSE)))

sig.all <- nrow(unique(read.table("Sig.loci.B12.SE.CASE.CA.LOC", header =FALSE)))


png(filename="VenB12LOC.png", type="cairo",units="px", width=3000, height=3000, res=200, bg="transparent")
venn.plot <- draw.triple.venn(
  area1=sig.CA, area2=sig.SE, area3=sig.CASE,
  n12= sig.CA.SE, n13=sig.CA.CASE,
  n23=sig.SE.CASE,
  n123=sig.all, cex=5,
  category = c("CA", "SE", "CASE"),
  fill = cbPaletteSmall3,cat.cex = rep(5, 3),
  cat.col = cbPaletteSmall3, label.col = rep("white", 7))
dev.off()

```

### Tier-based Venn Diagrams

Helper to compute the six areas needed for `draw.triple.venn()` from a
grouped loci data frame (output of `group_and_average()`).

```{r}
# draw_tier_venn(): compute overlaps and render a CA/SE/CASE triple Venn
# for a given grouped-loci data frame.
#
# Arguments:
#   gdf       — grouped loci data frame (must have Sig.CA, Sig.SE, Sig.CASE columns)
#   png_file  — output PNG path
#   title     — printed to console for traceability
draw_tier_venn <- function(gdf, png_file, title = "") {
  cat(paste0("\n-- Venn: ", title, " --\n"))

  n_CA   <- nrow(unique(subset(gdf, Sig.CA   == TRUE, c(SNP))))
  n_SE   <- nrow(unique(subset(gdf, Sig.SE   == TRUE, c(SNP))))
  n_CASE <- nrow(unique(subset(gdf, Sig.CASE == TRUE, c(SNP))))

  n_CA_SE   <- nrow(unique(subset(gdf, Sig.CA == TRUE & Sig.SE   == TRUE, c(SNP))))
  n_CA_CASE <- nrow(unique(subset(gdf, Sig.CA == TRUE & Sig.CASE == TRUE, c(SNP))))
  n_SE_CASE <- nrow(unique(subset(gdf, Sig.SE == TRUE & Sig.CASE == TRUE, c(SNP))))
  n_all     <- nrow(unique(subset(gdf, Sig.CA == TRUE & Sig.SE   == TRUE & Sig.CASE == TRUE, c(SNP))))

  cat(sprintf("  CA=%d  SE=%d  CASE=%d  CA∩SE=%d  CA∩CASE=%d  SE∩CASE=%d  all=%d\n",
              n_CA, n_SE, n_CASE, n_CA_SE, n_CA_CASE, n_SE_CASE, n_all))

  png(filename = png_file, type = "cairo", units = "px",
      width = 3000, height = 3000, res = 200, bg = "transparent")
  vp <- draw.triple.venn(
    area1 = n_CA, area2 = n_SE, area3 = n_CASE,
    n12   = n_CA_SE, n13 = n_CA_CASE, n23 = n_SE_CASE, n123 = n_all,
    cex = 5, category = c("CA", "SE", "CASE"),
    fill = cbPaletteSmall3, cat.cex = rep(5, 3),
    cat.col = cbPaletteSmall3, label.col = rep("white", 7))
  dev.off()
  invisible(vp)
}

# --- Core loci (multi-block, highest confidence) ---
draw_tier_venn(grouped_core.sig, "VenCore.png", "Core")

# --- Aggregate loci (per-block + all-blocks cross-validated) ---
draw_tier_venn(grouped_aggregate.sig, "VenAgg.png", "Aggregate")

# --- Block-Specific loci (single-block outliers; bs_source tracks origin) ---
# May produce zero-area circles for some stressors in sparse treatment categories
draw_tier_venn(grouped_block.specific, "VenBS.png", "Block-Specific")
```

# PCA
## All sample PCA of allele frequencies
```{bash, eval = FALSE}
source activate CASE

mawk '!/CHR/' Total.Significant.Loci | cut -f2,3 | sort | uniq > TSL.pca.filter

mawk 'NR==FNR{a[$1,$2]; next} ($1,$2) in a' TSL.pca.filter CASE.All.Blocks.cov.sync | cut --complement -f60- > outlier.pca.sync
```

```{r}
input.all.outlier <- read.sync(file="outlier.pca.sync", gen=seq(1,56), repl=seq(1,56), polarization="rising")


input.all.outlier.af <- af(input.all.outlier,gen=seq(1,56), repl=seq(1,56))
treatment.labels <- c(rep("CA", 11),rep("CASE", 11),rep("CON", 11),rep("IS", 12),rep("SE", 11))
spawn.names <- c("B12","B11","B12","B10","B11","B10","B11","B12","B10","B12","B11","B10","B11","B12","B12","B10","B12","B11","B10","B11","B11","B12","B10","B11","B12","B11","B10","B12","B10","B11","B12","B11","B12","B10","B11","B10","B11","B10","B11","B10","B11","B12","B12","B12","B12","B11","B12","B10","B10","B11","B11","B10","B12","B12","B11","B12")

colnames(input.all.outlier.af) <- paste(treatment.labels,spawn.names,sep="_")


# Perform PCA
af_t <- t(input.all.outlier.af)

pca_res <- prcomp(af_t, center = TRUE, scale. = TRUE)

# Get scores for plotting
pca_df <- as.data.frame(pca_res$x)
#pca_df$locus <- rownames(input.all.outlier.af)  # keep locus IDs if you have them

var_explained <- pca_res$sdev^2 / sum(pca_res$sdev^2) * 100

# Example: if you have a vector "pop_group" the same length as rows

treatment.labels <- c(rep("CA", 11),rep("CASE", 11),rep("CON", 11),rep("IS", 12),rep("SE", 11))
spawn.names <- c("B12","B11","B12","B10","B11","B10","B11","B12","B10","B12","B11","B10","B11","B12","B12","B10","B12","B11","B10","B11","B11","B12","B10","B11","B12","B11","B10","B12","B10","B11","B12","B11","B12","B10","B11","B10","B11","B10","B11","B10","B11","B12","B12","B12","B12","B11","B12","B10","B10","B11","B11","B10","B12","B12","B11","B12")

pca_df$Population <- spawn.names
pca_df$Treatments <- treatment.labels

ggplot(pca_df, aes(x = PC1, y = PC2, color = Population, fill=Population)) +
  geom_point(aes(alpha=0.2), size =10,shape=21, col="black")+  scale_fill_manual(values=cbPaletteSmall,name="Treatment")+ 
guides(alpha=FALSE) +theme(axis.title.x = element_text(size = 24),axis.title.y = element_text(size = 24)) +
  theme_minimal() +
  labs(
    x = paste0("PC1 (", round(var_explained[1], 1), "%)"),
    y = paste0("PC2 (", round(var_explained[2], 1), "%)"),
    title = "PCA of Allele Frequencies"
  )

```
```{r}
png(filename="PC1.png", type="cairo",units="px", width=5400, height=3000, res=300, bg="transparent")
ggplot(pca_df, aes(x=PC1, y= PC2, color = Treatments, fill=Treatments)) + geom_point(aes(alpha=0.2), size =10,shape=21, col="black")+ theme_classic() + scale_fill_manual(values=cbPaletteSmall,name="Treatment")+ 
guides(alpha=FALSE) +theme(axis.title.x = element_text(size = 24),axis.title.y = element_text(size = 24))+
  labs(
    x = paste0("PC1 (", round(var_explained[1], 1), "%)"),
    y = paste0("PC2 (", round(var_explained[2], 1), "%)"),
    title = "PCA of Allele Frequencies"
  )
dev.off()
png(filename="PC1b.png", type="cairo",units="px", width=5400, height=3000, res=300, bg="transparent")
ggplot(pca_df, aes(x=PC1, y= PC2, color = Population, fill=Population)) + geom_point(aes(alpha=0.2), size =10,shape=21, col="black")+ theme_classic() + scale_fill_manual(values=cbPaletteSmall,name="Spawn")+ 
guides(alpha=FALSE) +theme(axis.title.x = element_text(size = 24),axis.title.y = element_text(size = 24))+
  labs(
    x = paste0("PC1 (", round(var_explained[1], 1), "%)"),
    y = paste0("PC2 (", round(var_explained[2], 1), "%)"),
    title = "PCA of Allele Frequencies"
  )
dev.off()
```
## Outlier loci for each individual blocks
```{bash, eval = FALSE}
source activate CASE


mawk 'NR==FNR{a[$1,$2]; next} ($1,$2) in a' TSL.pca.filter CASE.All.Blocks.sync | cut --complement -f60- > outlier.pca.block.sync
```


```{r}
b10.pos <- read.table("B10.pos")
b11.pos <- read.table("B11.pos")
b12.pos <- read.table("B12.pos")

input.all.outlier.block <- read.sync(file="outlier.pca.block.sync", gen=seq(1,56), repl=seq(1,56), polarization="rising")

treatment.labels <- c(rep("CA", 11),rep("CASE", 11),rep("CON", 11),rep("IS", 12),rep("SE", 11))
spawn.names <- c("B12","B11","B12","B10","B11","B10","B11","B12","B10","B12","B11","B10","B11","B12","B12","B10","B12","B11","B10","B11","B11","B12","B10","B11","B12","B11","B10","B12","B10","B11","B12","B11","B12","B10","B11","B10","B11","B10","B11","B10","B11","B12","B12","B12","B12","B11","B12","B10","B10","B11","B11","B10","B12","B12","B11","B12")
input.all.outlier.block.af <- af(input.all.outlier.block,gen=seq(1,56), repl=seq(1,56))
colnames(input.all.outlier.block.af) <- paste(treatment.labels,spawn.names,sep="_")

```


```{r}

colnames(input.all.outlier.block.af) <- trimws(colnames(input.all.outlier.block.af))

stages <- c("B10","B11","B12")

for(stage in stages){
  # Get the position data for this stage
  pos_data <- get(paste0(tolower(stage), ".pos"))
  
  # Use the chromosome identifiers directly from .pos file (no mapping needed)
  stage_loci <- paste(pos_data[,1], pos_data[,2], sep = ".")
  
  # Filter rows based on the constructed loci identifiers
  row_idx <- rownames(input.all.outlier.block.af) %in% stage_loci
  
  # Match columns that end with "_B10" / "_B11" / "_B12"
  cols_idx <- grep(paste0("_", stage, "$"), colnames(input.all.outlier.block.af))
  
  cat(sprintf("\n== Stage %s ==\n", stage))
  cat("  Found loci in .pos file:", length(stage_loci), "\n")
  cat("  Matching loci in data:", sum(row_idx), "\n")
  cat("  Found sample columns:", length(cols_idx), "\n")
  
  if(length(cols_idx) < 2){
    warning(sprintf("Stage %s: less than 2 samples found - skipping PCA.", stage))
    next
  }
  
  if(sum(row_idx) < 2){
    warning(sprintf("Stage %s: less than 2 matching loci found - skipping PCA.", stage))
    next
  }
  
  # Apply both row and column filtering
  sub_mat <- input.all.outlier.block.af[row_idx, cols_idx, drop = FALSE]
  cat("  dim(sub_mat) (loci x samples):", dim(sub_mat), "\n")
  
  # Transpose so rows = samples, cols = loci (variables)
  mat_t <- t(sub_mat)
  
  # Remove loci (columns) with zero variance across the samples in this stage
  var_cols <- apply(mat_t, 2, var, na.rm = TRUE)
  keep <- which(var_cols > 0)
  removed_n <- sum(var_cols == 0)
  cat("  loci removed (zero variance):", removed_n, "\n")
  
  if(length(keep) < 2){
    warning(sprintf("Stage %s: fewer than 2 variable loci after filtering - skipping PCA.", stage))
    next
  }
  
  mat_t2 <- mat_t[, keep, drop = FALSE]
  cat("  dim(mat_t2) (samples x retained loci):", dim(mat_t2), "\n")
  
  # Run PCA (now safe to scale)
  pca_res <- prcomp(mat_t2, center = TRUE, scale. = FALSE)
  
  # PCA dataframe
  pca_df <- as.data.frame(pca_res$x)
  
  # Extract Treatments and Spawn from sample names (rownames of mat_t2)
  sample_names <- rownames(mat_t2)
  pca_df$Treatment <- sub("_.*", "", sample_names)   # text before first "_"
  pca_df$Spawn     <- sub(".*_", "", sample_names)   # text after last "_"
  
  # Variance explained
  var_explained <- (pca_res$sdev^2) / sum(pca_res$sdev^2) * 100
  
  # Choose palette fallback if cbPaletteSmall not defined
  if(exists("cbPaletteSmall")){
    fill_scale <- scale_fill_manual(values = cbPaletteSmall, name = "Treatment")
  } else {
    fill_scale <- scale_fill_brewer(palette = "Set1", name = "Treatment")
  }
  
  # Plot
  p <- ggplot(pca_df, aes(x = PC1, y = PC2, fill = Treatment)) +
    geom_point(aes(alpha = 0.2), size = 6, shape = 21, color = "black") +
    fill_scale +
    guides(alpha = FALSE) +
    theme_classic() +
    theme(axis.title.x = element_text(size = 14),
          axis.title.y = element_text(size = 14),
          plot.title = element_text(hjust = 0.5)) +
    labs(
      title = paste0("PCA - ", stage),
      x = paste0("PC1 (", round(var_explained[1], 1), "%)"),
      y = paste0("PC2 (", round(var_explained[2], 1), "%)")
    )
  
  # Save (adjust size/resolution or use png(...) if you prefer)
  outfile <- paste0("PC_", stage, ".png")
  ggsave(outfile, plot = p, width = 12, height = 7, dpi = 300)
  cat("  saved:", outfile, "\n")
}
```
## PCA of allele frequency difference from intitial for all samples
```{r}

# Base R approach for matrix named input.all.outlier.af
# Get column indices for each group
is_b10_cols <- grep("^IS_B10", colnames(input.all.outlier.af))
is_b11_cols <- grep("^IS_B11", colnames(input.all.outlier.af))
is_b12_cols <- grep("^IS_B12", colnames(input.all.outlier.af))

# Calculate row means and add as new columns
input.all.outlier.af <- cbind(input.all.outlier.af, 
                              ISM_B10 = rowMeans(input.all.outlier.af[, is_b10_cols], na.rm = TRUE),
                              ISM_B11 = rowMeans(input.all.outlier.af[, is_b11_cols], na.rm = TRUE),
                              ISM_B12 = rowMeans(input.all.outlier.af[, is_b12_cols], na.rm = TRUE))
```

```{r}
# Create new matrix with only delta columns (ISM values subtracted from corresponding B10/B11/B12 columns)
# (excluding IS columns from the subtraction)

# Get column indices for each group (excluding IS columns)
b10_cols <- grep("B10$", colnames(input.all.outlier.af))
b10_cols <- b10_cols[!grepl("^IS", colnames(input.all.outlier.af)[b10_cols])]

b11_cols <- grep("B11$", colnames(input.all.outlier.af))
b11_cols <- b11_cols[!grepl("^IS", colnames(input.all.outlier.af)[b11_cols])]

b12_cols <- grep("B12$", colnames(input.all.outlier.af))
b12_cols <- b12_cols[!grepl("^IS", colnames(input.all.outlier.af)[b12_cols])]

# Combine all target columns
all_target_cols <- c(b10_cols, b11_cols, b12_cols)

# Create vectors to store results and column names
delta_values <- list()
delta_names <- character()

# Process B10 columns
for(col in b10_cols) {
  delta_values[[length(delta_values) + 1]] <- input.all.outlier.af[, "ISM_B10"] - input.all.outlier.af[, col]
  delta_names <- c(delta_names, paste0(colnames(input.all.outlier.af)[col], "_delta"))
}

# Process B11 columns
for(col in b11_cols) {
  delta_values[[length(delta_values) + 1]] <- input.all.outlier.af[, "ISM_B11"] - input.all.outlier.af[, col]
  delta_names <- c(delta_names, paste0(colnames(input.all.outlier.af)[col], "_delta"))
}

# Process B12 columns
for(col in b12_cols) {
  delta_values[[length(delta_values) + 1]] <- input.all.outlier.af[, "ISM_B12"] - input.all.outlier.af[, col]
  delta_names <- c(delta_names, paste0(colnames(input.all.outlier.af)[col], "_delta"))
}

# Create the final matrix
new_matrix <- do.call(cbind, delta_values)
rownames(new_matrix) <- rownames(input.all.outlier.af)
colnames(new_matrix) <- delta_names

```



```{r}
# Perform PCA
af_t <- t(new_matrix)

pca_res <- prcomp(af_t, center = TRUE, scale. = FALSE)

# Get scores for plotting
pca_df <- as.data.frame(pca_res$x)
#pca_df$locus <- rownames(input.all.outlier.af)  # keep locus IDs if you have them

var_explained <- pca_res$sdev^2 / sum(pca_res$sdev^2) * 100

# Example: if you have a vector "pop_group" the same length as rows

treatment.labels <- c(rep("CA", 3),rep("CASE", 3),rep("CON", 3),rep("SE", 3),rep("CA", 4),rep("CASE", 4),rep("CON", 4),rep("SE", 4),rep("CA", 4),rep("CASE", 4),rep("CON", 4),rep("SE", 4))
spawn.names <- c(rep("B10",12),rep("B11",16),rep("B12",16))

pca_df$Population <- spawn.names
pca_df$Treatments <- treatment.labels

ggplot(pca_df, aes(x = PC1, y = PC2, fill = Treatments, shape = as.factor(Population))) +
  geom_point(size = 8, color = "black", alpha = 0.5) + 
  scale_fill_manual(values = cbPaletteSmall[-4], name = "Treatment") + 
  scale_shape_manual(values = c(21, 22, 23), name = "Spawn") +
  guides(fill = guide_legend(override.aes = list(shape = 21)), shape= guide_legend(override.aes= list(fill=cbPaletteSmall[4]))) +
  theme_minimal() +
  theme(axis.title.x = element_text(size = 24), axis.title.y = element_text(size = 24)) +
  labs(
    x = paste0("PC1 (", round(var_explained[1], 1), "%)"),
    y = paste0("PC2 (", round(var_explained[2], 1), "%)"),
    title = "PCA of Allele Frequencies"
  )

```


## Tier-specific PCA

### Extract tier-specific sync files

```{bash, eval=FALSE}
source activate CASE

# Build per-tier position filters from the Significant.Loci files created in the
# CON-filtering section. Each filter is a CHR/BP table used to subset the
# full sync file.

# --- Core loci ---
mawk '!/CHR/' Core.Significant.Loci | cut -f2,3 | sort | uniq > Core.pca.filter
# All-blocks sync (cov-filtered, columns 1–56 only)
mawk 'NR==FNR{a[$1,$2]; next} ($1,$2) in a' Core.pca.filter CASE.All.Blocks.cov.sync \
  | cut --complement -f60- > Core.outlier.pca.sync
# Raw sync (for per-block PCA loop below)
mawk 'NR==FNR{a[$1,$2]; next} ($1,$2) in a' Core.pca.filter CASE.All.Blocks.sync \
  | cut --complement -f60- > Core.outlier.pca.block.sync

# --- Block-Specific loci ---
mawk '!/CHR/' BS.Significant.Loci | cut -f2,3 | sort | uniq > BS.pca.filter
mawk 'NR==FNR{a[$1,$2]; next} ($1,$2) in a' BS.pca.filter CASE.All.Blocks.cov.sync \
  | cut --complement -f60- > BS.outlier.pca.sync
mawk 'NR==FNR{a[$1,$2]; next} ($1,$2) in a' BS.pca.filter CASE.All.Blocks.sync \
  | cut --complement -f60- > BS.outlier.pca.block.sync

# --- Aggregate loci ---
mawk '!/CHR/' Agg.Significant.Loci | cut -f2,3 | sort | uniq > Agg.pca.filter
mawk 'NR==FNR{a[$1,$2]; next} ($1,$2) in a' Agg.pca.filter CASE.All.Blocks.cov.sync \
  | cut --complement -f60- > Agg.outlier.pca.sync
mawk 'NR==FNR{a[$1,$2]; next} ($1,$2) in a' Agg.pca.filter CASE.All.Blocks.sync \
  | cut --complement -f60- > Agg.outlier.pca.block.sync
```

### All-samples PCA helper function

```{r}
# run_tier_pca(): reads a sync file for one locus tier, computes allele
# frequencies, runs PCA (all 56 samples), and saves two PNGs — one colored
# by Treatment, one by Spawn (block).
#
# Arguments:
#   sync_file   — path to the tier-filtered .sync file (cov-filtered, 56 cols)
#   tier_label  — human-readable label used in plot titles
#   out_prefix  — file-name prefix for PNG output (e.g. "PC_Core")
#
# Returns invisibly: list(pca_df, var_explained, p_treat, p_spawn)
run_tier_pca <- function(sync_file, tier_label, out_prefix) {
  cat(paste0("\n=== PCA: ", tier_label, " ===\n"))

  # Sample metadata — same order as in all existing PCA blocks
  treatment.labels <- c(rep("CA", 11), rep("CASE", 11), rep("CON", 11),
                        rep("IS", 12), rep("SE", 11))
  spawn.names <- c("B12","B11","B12","B10","B11","B10","B11","B12","B10","B12",
                   "B11","B10","B11","B12","B12","B10","B12","B11","B10","B11",
                   "B11","B12","B10","B11","B12","B11","B10","B12","B10","B11",
                   "B12","B11","B12","B10","B11","B10","B11","B10","B11","B10",
                   "B11","B12","B12","B12","B12","B11","B12","B10","B10","B11",
                   "B11","B10","B12","B12","B11","B12")

  inp    <- read.sync(file = sync_file, gen = seq(1, 56), repl = seq(1, 56),
                      polarization = "rising")
  inp.af <- af(inp, gen = seq(1, 56), repl = seq(1, 56))
  colnames(inp.af) <- paste(treatment.labels, spawn.names, sep = "_")

  af_t    <- t(inp.af)
  pca_res <- prcomp(af_t, center = TRUE, scale. = TRUE)
  pca_df  <- as.data.frame(pca_res$x)
  var_exp <- pca_res$sdev^2 / sum(pca_res$sdev^2) * 100

  pca_df$Population <- spawn.names
  pca_df$Treatments <- treatment.labels

  cat(sprintf("  Loci: %d   PC1: %.1f%%   PC2: %.1f%%\n",
              nrow(inp.af), var_exp[1], var_exp[2]))

  base_theme <- list(
    theme_classic(),
    guides(alpha = "none"),
    theme(axis.title.x = element_text(size = 24),
          axis.title.y = element_text(size = 24)),
    labs(x = paste0("PC1 (", round(var_exp[1], 1), "%)"),
         y = paste0("PC2 (", round(var_exp[2], 1), "%)"),
         title = paste0("PCA — ", tier_label))
  )

  p_treat <- ggplot(pca_df, aes(x = PC1, y = PC2,
                                fill = Treatments, shape = as.factor(Population))) +
    geom_point(size = 8, color = "black", alpha = 0.5) +
    scale_fill_manual(values = cbPaletteSmall[-4], name = "Treatment") +
    scale_shape_manual(values = c(21, 22, 23), name = "Spawn") +
    guides(fill  = guide_legend(override.aes = list(shape = 21)),
           shape = guide_legend(override.aes = list(fill  = cbPaletteSmall[4]))) +
    theme_minimal() +
    theme(axis.title.x = element_text(size = 24),
          axis.title.y = element_text(size = 24)) +
    labs(x     = paste0("PC1 (", round(var_exp[1], 1), "%)"),
         y     = paste0("PC2 (", round(var_exp[2], 1), "%)"),
         title = paste0("PCA — ", tier_label))

  p_spawn <- ggplot(pca_df, aes(x = PC1, y = PC2,
                                fill = as.factor(Population), shape = as.factor(Population))) +
    geom_point(size = 8, color = "black", alpha = 0.5) +
    scale_fill_manual(values = cbPaletteSmall[-4], name = "Spawn") +
    scale_shape_manual(values = c(21, 22, 23), name = "Spawn") +
    guides(fill  = guide_legend(override.aes = list(shape = 21)),
           shape = guide_legend(override.aes = list(fill  = cbPaletteSmall[4]))) +
    theme_minimal() +
    theme(axis.title.x = element_text(size = 24),
          axis.title.y = element_text(size = 24)) +
    labs(x     = paste0("PC1 (", round(var_exp[1], 1), "%)"),
         y     = paste0("PC2 (", round(var_exp[2], 1), "%)"),
         title = paste0("PCA — ", tier_label))

  png(paste0(out_prefix, "_treat.png"), type = "cairo", units = "px",
      width = 5400, height = 3000, res = 300, bg = "transparent")
  print(p_treat); dev.off()

  png(paste0(out_prefix, "_spawn.png"), type = "cairo", units = "px",
      width = 5400, height = 3000, res = 300, bg = "transparent")
  print(p_spawn); dev.off()

  invisible(list(pca_df = pca_df, var_explained = var_exp,
                 p_treat = p_treat, p_spawn = p_spawn))
}
```

### Run all-samples PCA for each tier

```{r}
# All three tiers run across all 56 samples; block-restrict Agg/BS later
# if the all-block PCA is uninformative.
pca.core <- run_tier_pca("Core.outlier.pca.sync",  "Core Loci",           "PC_Core")
pca.agg  <- run_tier_pca("Agg.outlier.pca.sync",   "Aggregate Loci",      "PC_Agg")
pca.bs   <- run_tier_pca("BS.outlier.pca.sync",    "Block-Specific Loci", "PC_BS")

# Print in-line
print(pca.core$p_treat)
print(pca.agg$p_treat)
print(pca.bs$p_treat)
```

### Per-block PCA helper function

```{r}
# run_block_pca_tier(): for a given tier's block-sync file, run the same
# per-block (B10 / B11 / B12) PCA loop used for total.sig above.
# Each block uses only its own samples and loci from the .pos file.
#
# Arguments:
#   sync_file   — path to the tier-filtered block-level .sync file
#   tier_label  — human-readable label used in plot titles and file names
#
# Note: Agg and BS may have very few loci in a given block; the function
# will warn and skip rather than error if < 2 variable loci remain.
run_block_pca_tier <- function(sync_file, tier_label) {
  cat(paste0("\n=== Per-block PCA: ", tier_label, " ===\n"))

  treatment.labels <- c(rep("CA", 11), rep("CASE", 11), rep("CON", 11),
                        rep("IS", 12), rep("SE", 11))
  spawn.names <- c("B12","B11","B12","B10","B11","B10","B11","B12","B10","B12",
                   "B11","B10","B11","B12","B12","B10","B12","B11","B10","B11",
                   "B11","B12","B10","B11","B12","B11","B10","B12","B10","B11",
                   "B12","B11","B12","B10","B11","B10","B11","B10","B11","B10",
                   "B11","B12","B12","B12","B12","B11","B12","B10","B10","B11",
                   "B11","B10","B12","B12","B11","B12")

  inp    <- read.sync(file = sync_file, gen = seq(1, 56), repl = seq(1, 56),
                      polarization = "rising")
  inp.af <- af(inp, gen = seq(1, 56), repl = seq(1, 56))
  colnames(inp.af) <- paste(treatment.labels, spawn.names, sep = "_")
  colnames(inp.af) <- trimws(colnames(inp.af))

  stages <- c("B10", "B11", "B12")
  for (stage in stages) {
    pos_data   <- get(paste0(tolower(stage), ".pos"))
    stage_loci <- paste(pos_data[, 1], pos_data[, 2], sep = ".")
    row_idx    <- rownames(inp.af) %in% stage_loci
    cols_idx   <- grep(paste0("_", stage, "$"), colnames(inp.af))

    cat(sprintf("  %s  loci_in_pos=%d  matched=%d  samples=%d\n",
                stage, length(stage_loci), sum(row_idx), length(cols_idx)))

    if (length(cols_idx) < 2 || sum(row_idx) < 2) {
      warning(sprintf("Tier %s / Block %s: insufficient data — skipping.",
                      tier_label, stage))
      next
    }

    sub_mat <- inp.af[row_idx, cols_idx, drop = FALSE]
    mat_t   <- t(sub_mat)
    var_cols <- apply(mat_t, 2, var, na.rm = TRUE)
    keep     <- which(var_cols > 0)
    cat(sprintf("    zero-var loci removed: %d\n", sum(var_cols == 0)))

    if (length(keep) < 2) {
      warning(sprintf("Tier %s / Block %s: < 2 variable loci after filtering — skipping.",
                      tier_label, stage))
      next
    }

    mat_t2  <- mat_t[, keep, drop = FALSE]
    pca_res <- prcomp(mat_t2, center = TRUE, scale. = FALSE)
    pca_df  <- as.data.frame(pca_res$x)
    var_exp <- (pca_res$sdev^2 / sum(pca_res$sdev^2)) * 100

    samp_names    <- rownames(mat_t2)
    pca_df$Treatment <- sub("_.*", "", samp_names)
    pca_df$Spawn     <- sub(".*_", "", samp_names)

    p <- ggplot(pca_df, aes(x = PC1, y = PC2, fill = Treatment)) +
      geom_point(aes(alpha = 0.2), size = 6, shape = 21, color = "black") +
      scale_fill_manual(values = cbPaletteSmall, name = "Treatment") +
      guides(alpha = "none") +
      theme_classic() +
      theme(axis.title.x = element_text(size = 14),
            axis.title.y = element_text(size = 14),
            plot.title   = element_text(hjust = 0.5)) +
      labs(
        title = paste0("PCA — ", tier_label, " / ", stage),
        x = paste0("PC1 (", round(var_exp[1], 1), "%)"),
        y = paste0("PC2 (", round(var_exp[2], 1), "%)")
      )

    outfile <- paste0("PC_", gsub(" ", "_", tier_label), "_", stage, ".png")
    ggsave(outfile, plot = p, width = 12, height = 7, dpi = 300)
    cat(sprintf("    saved: %s\n", outfile))
  }
}
```

### Run per-block PCA for each tier

```{r}
run_block_pca_tier("Core.outlier.pca.block.sync", "Core")
run_block_pca_tier("Agg.outlier.pca.block.sync",  "Aggregate")
run_block_pca_tier("BS.outlier.pca.block.sync",   "Block-Specific")
```

